---
title: "Sample Descriptive Statistics"
format: html
---

In this file, we'll import all of the Dallas County files provided and create preliminary cross-tabulations and merges to explore basic counts, trends, and double check primary keys and joins across the data files. 

See `Codebooks` and `Data Diagram` tabs for more information on each individual data file. 

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())
```

```{r include=FALSE}
### pull in dallas data from raw data folder

### set sharepoint path using file.path function (path has different structure than usual so not using csg_sp_path from csgjcr package)
sharepoint_jj_av_dallas_raw_data <- file.path("C:/Users/abyrum/The Council of State Governments/JC Research - JJ_AV - JJ_AV/Dallas/Data/raw")

### using purrr::map, import list of tabs from excel worksheet
dallas_raw_tab_list <- purrr::map(purrr::set_names(excel_sheets(file.path(sharepoint_jj_av_dallas_raw_data,
                                                              "Dallas County (10.1.2017 - 9.30.2022).xlsx"))),
                      read_excel, 
                      path = file.path(sharepoint_jj_av_dallas_raw_data,"Dallas County (10.1.2017 - 9.30.2022).xlsx")) %>% 
  purrr::map(janitor::clean_names)

### clean names of all imported tabs before converting to dataframes
names(dallas_raw_tab_list) <- janitor::make_clean_names(names(dallas_raw_tab_list))

### then convert list of tabs to distinct dataframes with names from tabs
purrr::map(names(dallas_raw_tab_list),
           ~assign(.x, 
                   dallas_raw_tab_list[[.x]], 
        envir = .GlobalEnv)) 
```

```{r include=FALSE}
#############################################
### clean and de-dup child dataframe
### this is our base demo file for the sample
#############################################
child_clean <- child %>% 
  distinct(unique_id,
           .keep_all=TRUE) %>% ### no records dropped
  ### clean race/ethnicity and gender
  mutate(race_clean = case_when(
    race=="Asian or Pacific Islander" & ethnicity!="Hispanic" ~ 1,
    race=="Black" & ethnicity!="Hispanic" ~ 2,
    ethnicity=="Hispanic" ~ 3,
    race=="White" & ethnicity!="Hispanic" ~ 4,
    race %in% c("Unknown","American Indian or Alaskan Native") & ethnicity!="Hispanic" ~ 5,
    TRUE ~ as.numeric(NA)),
    race_clean = factor(race_clean,
         levels = c(1,2,3,4,5),
         labels = c("Asian", "Black", "Hispanic", "White", "Other"))) %>% 
  mutate(gender_clean = case_when(
    gender=="Female" ~ 1,
    gender=="Male" ~ 2,
    TRUE ~ as.numeric(NA)),
    gender_clean = factor(gender_clean,
         levels = c(1,2),
         labels = c("Female", "Male"))) ### use factor function to assign labels to values

########################################
### clean and de-dup offenses dataframe
########################################
offenses_clean <- offenses %>% 
  distinct(unique_id,
           referral_number,
           offense_id,
           .keep_all=TRUE) %>% ### no records dropped
  ### clean dates and create years for potential grouping in future trend analysis
  mutate(offense_date = ymd(as_date(offense_date)),
         referral_date = ymd(as_date(referral_date)),
         disposition_date = ymd(as_date(excel_numeric_to_date(as.numeric(as.character(disposition_date)), 
                                                  date_system = "modern"))),         
         offense_year = year(offense_date),
         referral_year = year(referral_date),
         disposition_year = year(disposition_date)) %>% 
  ### create unique referral ID and unique offense ID for possible filtering or counting
  mutate(unique_referral_id = paste0(unique_id,
                                     referral_number),
         unique_offense_id = paste0(unique_id,
                                    referral_number,
                                    offense_id)) %>% 
  ### calculate number of offenses per referral by grouping by unique_referral_id
  group_by(unique_referral_id) %>% 
  mutate(unique_offenses_per_referral_count = n_distinct(unique_offense_id,
                                                         na.rm = TRUE)) %>% 
  ungroup()

########################################
### clean and de-dup supervision dataframe
########################################
supervision_clean <- supervision %>% 
  distinct(unique_id,
           referral_number,
           supervision_begin_date,
           .keep_all=TRUE) %>% ### 1 record dropped (note: 170 recods have duplicated IDs but different begin dates)
  ### clean dates and create years for potential grouping in future trend analysis
  mutate(supervision_begin_date = ymd(as_date(supervision_begin_date)),
         supervision_end_date = ymd(as_date(supervision_end_date)),
         supervision_begin_year = year(supervision_begin_date),
         supervision_end_year = year(supervision_end_date)) %>% 
  ### create unique referral ID possible filtering, joining, or counting
  mutate(unique_referral_id = paste0(unique_id,
                                     referral_number)) 

#############################################
### clean and de-dup supervision_level dataframe
#############################################

### by unique_id, referral_number, phase_begin_date, phase_end_date
supervision_level_clean <- supervision_level %>% 
  distinct(unique_id,
           referral_number,
           phase,
           phase_begin_date,
           phase_end_date,
           .keep_all=TRUE) ### 1 record dropped 
```

<br>

# Sample Descriptives

**Data Sample:** Supervision records of DCJD juveniles on either Court-Ordered Probation/Permanent Probation/Deferred Prosecution at any point from 10/1/2017 through 9/30/2022



## Table 1. Unique Youth and Referrals by Year (Year of Referral)

```{r echo=FALSE,message=FALSE,warning=FALSE}
### create denominator -- unique referrals for entire sample
unique_referrals_sample_denom <- n_distinct(offenses_clean$unique_id,
                                            offenses_clean$referral_number)

### create denominator -- unique youth for entire sample
unique_youth_sample_denom <- n_distinct(offenses_clean$unique_id)

### unique youth and referrals per year
df_referrals_youth_per_year <- offenses_clean %>% 
  dplyr::group_by(referral_year) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Referrals, Percent of Sample (%)` = scales::percent(`Unique Referrals (N)`/unique_referrals_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Year of Referral` = referral_year) %>% 
  mutate(`Year of Referral` = as.character(`Year of Referral`))

### overall
df_referrals_youth_overall <- offenses_clean %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Referrals, Percent of Sample (%)` = scales::percent(`Unique Referrals (N)`/unique_referrals_sample_denom,
                                                                       accuracy = .1)) %>% 
  mutate(`Year of Referral` = "Overall")

### combine tables for kable
df_referrals_youth_per_year_table <- rbind(df_referrals_youth_per_year,df_referrals_youth_overall)

### print table via kableextra
kable(df_referrals_youth_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(14, bold = TRUE)
```


```{r include=FALSE,message=FALSE,warning=FALSE}
## Join 1. Join of `Child` and `Offenses`

### left join of child file to offenses file in order to see if there is much missingness
### i.e. are there offenses without demo records? 
offenses_child_demo_join <- 
  left_join(offenses_clean,
            child_clean,
            by = "unique_id") ### join looks good; all records join
```

<br>

## Table 2: Unique Youth and Referrals by Race/Ethnicity

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and referrals per year
df_referrals_youth_race <- offenses_child_demo_join %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Youth, Percent of Sample (%)` = scales::percent(`Unique Youth (N)`/unique_youth_sample_denom,
                                                                       accuracy = .1),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Referrals, Percent of Sample (%)` = scales::percent(`Unique Referrals (N)`/unique_referrals_sample_denom,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) %>% 
  mutate(`Race/Ethnicity` = as.character(`Race/Ethnicity`))

### overall
df_referrals_youth_overall_race <- offenses_child_demo_join %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Youth, Percent of Sample (%)` = scales::percent(`Unique Youth (N)`/unique_youth_sample_denom,
                                                                       accuracy = .1),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Referrals, Percent of Sample (%)` = scales::percent(`Unique Referrals (N)`/unique_referrals_sample_denom,
                                                                       accuracy = .1)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_referrals_youth_race_table <- rbind(df_referrals_youth_race,df_referrals_youth_overall_race)

### print table via kableextra
kable(df_referrals_youth_race_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 3: Average Offenses per Referral over Time

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique offenses per referral by year of referral
### since we are taking mean and median, we need to de-dup by referral 
### 'unique_offenses_per_referral_count' was calculated at referral-level
df_offenses_per_referral_by_year <- offenses_clean %>% 
  distinct(unique_referral_id,
           .keep_all = TRUE) %>% 
  dplyr::group_by(referral_year) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Mean Offenses per Referral` = format(round(mean(unique_offenses_per_referral_count,
                                                    na.rm=TRUE), 
                                                 digits = 2),
                                                 nsmall = 2),
            `Median Offenses per Referral` = median(unique_offenses_per_referral_count)) %>% 
  ungroup() %>% 
  dplyr::rename(`Year of Referral` = referral_year) %>% 
  mutate(`Year of Referral` = as.character(`Year of Referral`))

### overall
df_offenses_per_referral_overall <- offenses_clean %>% 
  distinct(unique_referral_id,
           .keep_all = TRUE) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Mean Offenses per Referral` = format(round(mean(unique_offenses_per_referral_count,
                                                    na.rm=TRUE),
                                                 digits = 2),
                                                 nsmall = 2),
            `Median Offenses per Referral` = median(unique_offenses_per_referral_count)) %>% 
  mutate(`Year of Referral` = "Overall")

### combine tables for kable
df_offenses_per_referral_by_year_table <- rbind(df_offenses_per_referral_by_year,df_offenses_per_referral_overall)

### print table via kableextra
kable(df_offenses_per_referral_by_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(14, bold = TRUE)
```

<br>

## Table 4: Referral Type Options

```{r echo=FALSE,message=FALSE,warning=FALSE}
### disposition options
df_offenses_referral_type <- offenses_clean %>% 
  dplyr::group_by(referral_type) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id)) %>% 
  ungroup() %>% 
  dplyr::rename(`Referral Type` = referral_type) 

### print table via kableextra
kable(df_offenses_referral_type, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 5: Disposition Options

```{r echo=FALSE,message=FALSE,warning=FALSE}
### disposition options
df_offenses_dispositions <- offenses_clean %>% 
  dplyr::group_by(disposition) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id)) %>% 
  ungroup() %>% 
  dplyr::rename(`Disposition` = disposition) 

### print table via kableextra
kable(df_offenses_dispositions, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 6: Supervision Type

```{r echo=FALSE,message=FALSE,warning=FALSE}
### overall supervision type
df_supervision_type_table <- supervision_clean %>% 
  dplyr::group_by(supervision_type) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id)) %>% 
  ungroup() %>% 
  dplyr::rename(`Supervision Type` = supervision_type) 

### print table via kableextra
kable(df_supervision_type_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```


<br>

## Table 7: Supervision Level

```{r echo=FALSE,message=FALSE,warning=FALSE}
### overall supervision type
df_supervision_level_table <- supervision_level_clean %>% 
  dplyr::group_by(phase) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_id,
                                                referral_number)) %>% 
  ungroup() %>% 
  dplyr::rename(`Supervision Level` = phase) 

### print table via kableextra
kable(df_supervision_level_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 8: Supervision Outcomes

Note: It seems like supervision outcomes of "NA" indicate supervision active at time of data pull. Will confirm with Dallas County. 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### supervision outcomes
df_supervision_outcome_table <- supervision_clean %>% 
  dplyr::group_by(outcome) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id)) %>% 
  ungroup() %>% 
  dplyr::rename(`Supervision Outcome` = outcome) 

### print table via kableextra
kable(df_supervision_outcome_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 9: Overall Violation Type 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### overall violation type
df_overall_violation_type_table <- violations %>% 
  dplyr::group_by(offense_description) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_id,violation_referral_number)) %>% 
  ungroup() %>% 
  dplyr::rename(`Violation Type` = offense_description) 

### print table via kableextra
kable(df_overall_violation_type_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```


<br>

## Table 10: Technical Violation Type 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### technical violation information
df_technical_violation_type_table <- violations %>% 
  filter(offense_description%in%c("VIOL OF COURT ORDER  - TECHNICAL","VIOL OF COURT ORDER (DET SENT PROB) -TECHNICAL")) %>%
  dplyr::group_by(violation) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_id,violation_referral_number)) %>% 
  ungroup() %>% 
  dplyr::rename(`Technical Violation Type` = violation) 

### print table via kableextra
kable(df_technical_violation_type_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 11: Placement Type 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### placement types
df_placement_type_table <- placements %>% 
  dplyr::group_by(placement_type) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_id,placement_referral_number)) %>% 
  ungroup() %>% 
  dplyr::rename(`Placement Type` = placement_type) 

### print table via kableextra
kable(df_placement_type_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br>

## Table 12: Offense Level and Type


*Proposed hierarchy (most to least serious) for keeping most serious disposed offense per referral:*


*Are these correct? Do we want to rank within violent, property? How do we want to rank CINS?*


**1. Felony:**

* Violent (Homicide, Sexual Assault, Assaultive, Weapons Offenses, Robbery, Other Violent)

* Property (Burglary, Theft, Other Property)

* Non-Person Drug (Drug Offenses)

* Other Felony (Other Felony)


**2. Misdemeanor:**

* Violent (Assaultive, Weapons Offenses)

* Property (Theft, Other Property)

* Drug (Drug Offenses)

* Other Misdemeanor (Other Misdemeanor)


**3. CINS (Conduct indicating a need for supervision)/status??:**

* Alternative Education Expulsion

* Disorderly Conduct

* Drugs

* Liquor Laws

* Other CINS

* Runaway

* Property (was theft)

* Truancy

* Sex Offenses


**4. Violation of Court Order:**

* VOP 


**5. Contempt:**

* Contempt 


**6. Other:**

* Other Administrative 

```{r echo=FALSE,message=FALSE,warning=FALSE}
### offense types
table(offenses$offense_level,
      offenses$offense_type,
      useNA = 'always')
```

<br>
