---
title: "Building the Analytic Files"
format: html
---

In this syntax, we'll import all of the Dallas County files provided and create two analytic files based on the templates in the second and third tabs here: https://csgorg.sharepoint.com/:x:/s/Team-JC-Research-JJ_AV/EZ-RDTetlZVCoiQxlasiboEBhsT7WNlx5v0qR7sDBji1-A?e=eggzRJ

See `Codebooks` and `Data Diagram` tabs for more information on each individual data file. 

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### pull in dallas data from raw data folder

### data path
sp_data_path <- csg_get_project_path("jj-av-dallas")

### set sharepoint path using file.path function (path has different structure than usual so not using csg_sp_path from csgjcr package)
sharepoint_jj_av_dallas_raw_data <- file.path(sp_data_path,"Data/raw")

### using purrr::map, import list of tabs from excel worksheet
dallas_raw_tab_list <- purrr::map(purrr::set_names(excel_sheets(file.path(sharepoint_jj_av_dallas_raw_data,
                                                              "Dallas County (10.1.2017 - 9.30.2022).xlsx"))),
                      read_excel, 
                      path = file.path(sharepoint_jj_av_dallas_raw_data,"Dallas County (10.1.2017 - 9.30.2022).xlsx")) %>% 
  purrr::map(janitor::clean_names)

### clean names of all imported tabs before converting to dataframes
names(dallas_raw_tab_list) <- janitor::make_clean_names(names(dallas_raw_tab_list))

### then convert list of tabs to distinct dataframes with names from tabs
purrr::map(names(dallas_raw_tab_list),
           ~assign(.x, 
                   dallas_raw_tab_list[[.x]], 
        envir = .GlobalEnv)) 
```

```{r warning=FALSE}
#############################################
### clean and de-dup child dataframe
### this is our base demo file for the sample
#############################################
child_clean <- child %>% 
  distinct(unique_id,
           .keep_all=TRUE) %>% ### no records dropped
  ### clean race/ethnicity and gender
  ### use factor function to assign labels to values
  mutate(race_clean = case_when(
    race=="Asian or Pacific Islander" & ethnicity!="Hispanic" ~ 1,
    race=="Black" & ethnicity!="Hispanic" ~ 2,
    ethnicity=="Hispanic" ~ 3,
    race=="White" & ethnicity!="Hispanic" ~ 4,
    race %in% c("Unknown","American Indian or Alaskan Native") & ethnicity!="Hispanic" ~ 5,
    TRUE ~ as.numeric(NA)),
    race_clean = factor(race_clean,
         levels = c(1,2,3,4,5),
         labels = c("Asian", "Black", "Hispanic", "White", "Other"))) %>% 
  mutate(gender_clean = case_when(
    gender=="Female" ~ 1,
    gender=="Male" ~ 2,
    TRUE ~ as.numeric(NA)),
    gender_clean = factor(gender_clean,
         levels = c(1,2),
         labels = c("Female", "Male"))) %>% 
  ### clean dates
  mutate(birth_date = ymd(as_date(birth_date))) 

#############################################
### clean and de-dup supervision dataframe
#############################################
supervision_clean <- supervision %>% 
  distinct(unique_id,
           referral_number,
           supervision_begin_date,
           .keep_all=TRUE) %>% ### 1 record dropped (note: 170 records have duplicated IDs but different begin dates)
  ### clean dates and create years for potential grouping in future trend analysis
  mutate(supervision_begin_date = ymd(as_date(supervision_begin_date)),
         supervision_end_date = ymd(as_date(supervision_end_date)),
         supervision_begin_year = year(supervision_begin_date),
         supervision_end_year = year(supervision_end_date),
         overall_supervision_los_days = as.numeric(difftime(supervision_end_date,
                                                            supervision_begin_date,
                                                                    units="days"))) %>% 
  ### create unique referral ID possible filtering, joining, or counting
  mutate(unique_referral_id = paste0(unique_id,
                                     referral_number),
         unique_supervision_id = paste0(unique_id,
                                        referral_number,
                                        supervision_begin_date)) %>% 
  ### rename columns with duplicate names across files to indicate where data initially came from 
  dplyr::rename(supervision_disposition = disposition,
                supervision_outcome = outcome)

### test for duplicate types 
### flag records with multiple supervision records per referral number (N=170 referrals)
### 1,100 youth have multiple supervision records (largely linked to different referrals)
### keep duplicates in for now -- but make note for Emily and Becky 
supervision_test_de_dup <- supervision %>% 
  janitor::get_dupes(c(unique_id,
                       referral_number))


#############################################
### clean and de-dup supervision_extension dataframe
#############################################

### by unique_id and referral_number -- take first and last extension date 
### and count number of unique extension records per unique_id and referral_number
supervision_extension_clean <- supervision_extension %>% 
  distinct(unique_id,
           referral_number,
           extension_begin_date,
           extension_end_date,
           .keep_all=TRUE) %>% ### 0 records dropped 
  ### clean dates and create years for potential grouping in future trend analysis
  mutate(supervision_begin_date = ymd(as_date(supervision_begin_date)),
         supervision_end_date = ymd(as_date(supervision_end_date)),
         extension_begin_date = ymd(as_date(extension_begin_date)),
         extension_end_date = ymd(as_date(extension_end_date)),
         supervision_extension_los_days = as.numeric(difftime(extension_end_date,
                                                            extension_begin_date,
                                                                    units="days")),
         unique_supervision_id = paste0(unique_id,
                                        referral_number,
                                        supervision_begin_date)) %>% 
  ### create a count variable as well as a min and max extension date to obtain full LOS
  group_by(unique_supervision_id) %>% 
  mutate(unique_supervision_extensions_per_supervision_count = n_distinct(unique_id,
                                                           referral_number,
                                                           extension_begin_date,
                                                           extension_end_date),
         min_supervision_extension_begin_date =  min(extension_begin_date,
                                         na.rm = TRUE),
         max_supervision_extension_end_date =  max(extension_end_date,
                                         na.rm = TRUE),
         total_los_supervision_extension_days = sum(supervision_extension_los_days,
                                                    na.rm = TRUE)) %>% 
  ungroup() %>% 
  ### rename columns with duplicate names across files to indicate where data initially came from 
  dplyr::rename(supervision_extension_supervision_type = supervision_type,
                supervision_extension_begin_date = extension_begin_date,
                supervision_extension_phase_end_date = extension_end_date) %>% 
  ### dropping these dates as they appear in other files and will just be duplicated after we merge
  dplyr::select(unique_supervision_id,
                unique_supervision_extensions_per_supervision_count,
                min_supervision_extension_begin_date,
                max_supervision_extension_end_date,
                total_los_supervision_extension_days) %>% 
  distinct(unique_supervision_id,
           .keep_all = TRUE)


#############################################
### clean and de-dup supervision_level dataframe
#############################################

### by unique_id, referral_number, phase_begin_date, phase_end_date
supervision_level_clean <- supervision_level %>% 
  distinct(unique_id,
           referral_number,
           phase,
           phase_begin_date,
           phase_end_date,
           .keep_all=TRUE) %>%  ### 1 record dropped 
  ### clean dates and create years for potential grouping in future trend analysis
  mutate(phase_begin_date = ymd(as_date(phase_begin_date)),
         phase_end_date = ymd(as_date(phase_end_date)),
         unique_supervision_id = paste0(unique_id,
                                        referral_number,
                                        supervision_begin_date)) %>% 
  ### rename columns with duplicate names across files to indicate where data initially came from 
  dplyr::rename(supervision_level_phase = phase,
                supervision_level_supervision_type = supervision_type,
                supervision_level_phase_begin_date = phase_begin_date,
                supervision_level_phase_end_date = phase_end_date) %>% 
  ### create hierarchy of supervision levels
  ### when we measure changes/modifications to supervision levels,
  ### we are most interested in changes to more intensive levels of supervision 
  ### (as opposed to planned decreases in intensity over time)
    mutate(supervision_level_phase_severity = 
           case_when(
             supervision_level_phase=="PLACEMENT" ~ 1,
             supervision_level_phase=="DETENTION/SHELTER" ~ 2,
             supervision_level_phase=="ISP LEVEL 1" ~ 3,             
             supervision_level_phase=="ISP LEVEL 2" ~ 4,
             supervision_level_phase=="ISP LEVEL 3" ~ 5,
             supervision_level_phase=="PROB LEVEL R1" ~ 6,
             supervision_level_phase=="PROB LEVEL R2" ~ 7,             
             supervision_level_phase=="PROB LEVEL R3" ~ 8,
             supervision_level_phase=="PROB LEVEL R4" ~ 9,
             supervision_level_phase%in%c("None","WARRANT") ~ 11, 
             TRUE ~ as.numeric(NA))) %>% 
  ### now arrange and group by youth to take the next supervision level, if present
  ### using dplyr::lead to take the next supervision_level_phase_severity value
  ### using https://dplyr.tidyverse.org/reference/lead-lag.html
  ### this will allow us to calculate the number of instances where youth 
  ### experienced an increase in supervision intensiveness 
  ### logic: using supervision_level_phase_severity, next value is less than current value
  ### indicates an increase in intensity of supervision
  arrange(unique_id,
          referral_number,
          supervision_level_phase_begin_date) %>%
  group_by(unique_id) %>%
  mutate(next_supervision_level = dplyr::lead(supervision_level_phase_severity,
                                                   1,
                                                   default=NA)) %>%
  ungroup() %>%
  mutate(next_supervision_level_is_increase_flag = ifelse(supervision_level_phase_severity>next_supervision_level,
                                                          1,0)) %>% 
  ### calculate los by supervision level type (probation, detention, placement, none, and warrant)
  mutate(overall_supervision_los_days = as.numeric(difftime(supervision_end_date,
                                                            supervision_begin_date,
                                                                    units="days")),
         temp_supervision_level_los_days = as.numeric(difftime(supervision_level_phase_end_date,
                                                            supervision_level_phase_begin_date,
                                                                    units="days"))) %>% 
  group_by(unique_supervision_id) %>% 
  mutate(probation_supervision_los_days = sum(temp_supervision_level_los_days[supervision_level_phase%in%c("ISP LEVEL 1",
                                                                                                        "ISP LEVEL 2",
                                                                                                        "ISP LEVEL 3",
                                                                                                        "PROB LEVEL R1",
                                                                                                        "PROB LEVEL R2",
                                                                                                        "PROB LEVEL R3",
                                                                                                        "PROB LEVEL R4")],
                                              na.rm = TRUE),
         detention_supervision_los_days = sum(temp_supervision_level_los_days[supervision_level_phase=="DETENTION/SHELTER"],
                                              na.rm = TRUE),
         placement_supervision_los_days = sum(temp_supervision_level_los_days[supervision_level_phase=="PLACEMENT"],
                                              na.rm = TRUE),
         none_supervision_los_days = sum(temp_supervision_level_los_days[supervision_level_phase=="NONE"],
                                              na.rm = TRUE),
         warrant_supervision_los_days = sum(temp_supervision_level_los_days[supervision_level_phase=="WARRANT"],
                                              na.rm = TRUE)) %>% 
  ### create a count variable in case it's handy for later analysis
  ### sum los by supervision phase/level type at supervision record-level 
  mutate(overall_unique_supervision_levels_per_supervision_episode_count = n_distinct(unique_id,
                                                           referral_number,
                                                           supervision_level_phase_begin_date,
                                                           supervision_level_phase_end_date),
         supervision_level_increases_per_supervision_episode_count = sum(next_supervision_level_is_increase_flag,
                                              na.rm = TRUE),
         probation_supervision_los_days = sum(probation_supervision_los_days,
                                              na.rm = TRUE),
         detention_supervision_los_days = sum(detention_supervision_los_days,
                                              na.rm = TRUE),
         placement_supervision_los_days = sum(placement_supervision_los_days,
                                              na.rm = TRUE),
         none_supervision_los_days = sum(none_supervision_los_days,
                                              na.rm = TRUE),
         warrant_supervision_los_days = sum(warrant_supervision_los_days,
                                              na.rm = TRUE)) %>% 
  ungroup() %>% 
  ### de-dup, keeping first record to preserve initial level for supervision period
  arrange(unique_supervision_id,
          supervision_level_phase_begin_date) %>% 
  distinct(unique_supervision_id,
           .keep_all = TRUE) %>% 
  ### only keeping variables created at supervision record-level
  dplyr::select(unique_supervision_id,
                initial_supervision_level = supervision_level_phase,
                overall_supervision_los_days,
                overall_unique_supervision_levels_per_supervision_episode_count,
                supervision_level_increases_per_supervision_episode_count,
                probation_supervision_los_days:warrant_supervision_los_days)
 

#############################################
### clean and de-dup offenses dataframe
#############################################
offenses_clean <- offenses %>% 
  distinct(unique_id,
           referral_number,
           offense_id,
           .keep_all=TRUE) %>% ### no records dropped
  ### clean dates and create years for potential grouping in future trend analysis
  mutate(offense_date = ymd(as_date(offense_date)),
         referral_date = ymd(as_date(referral_date)),
         disposition_date = ymd(as_date(excel_numeric_to_date(as.numeric(as.character(disposition_date)), 
                                                  date_system = "modern"))),
         offense_year = year(offense_date),
         referral_year = year(referral_date),
         offense_disposition_year = year(disposition_date)) %>% 
  ### create unique referral ID and unique offense ID for possible filtering or counting
  mutate(unique_referral_id = paste0(unique_id,
                                     referral_number),
         unique_offense_id = paste0(unique_id,
                                    referral_number,
                                    offense_id)) %>% 
  ### calculate number of offenses per referral by grouping by unique_referral_id
  group_by(unique_referral_id) %>% 
  mutate(unique_offenses_per_referral_count = n_distinct(unique_offense_id,
                                                         na.rm = TRUE),
         unique_felony_offenses_per_referral_count = n_distinct(unique_offense_id[offense_level=="Felony"],
                                                         na.rm = TRUE),
         unique_misdemeanor_offenses_per_referral_count = n_distinct(unique_offense_id[offense_level=="Misdemeanor"],
                                                         na.rm = TRUE),
         unique_cins_offenses_per_referral_count = n_distinct(unique_offense_id[offense_level=="CINS"],
                                                         na.rm = TRUE)) %>% 
  ungroup() %>% 
  ### create factor variable for offense severity based on hierarchy outlined in table 11 on descriptives page
  ### need to confirm order with team
  mutate(offense_level_type_combined_grouped = 
           case_when(
             offense_level=="Felony" & offense_type%in%c("Homicide",
                                                         "Sexual Assault", 
                                                         "Assaultive",
                                                         "Weapons Offenses", 
                                                         "Robbery",
                                                         "Other Violent") ~ 1,
             offense_level=="Felony" & offense_type%in%c("Burglary", 
                                                         "Theft", 
                                                         "Other Property") ~ 2,
             offense_level=="Felony" & offense_type%in%c("Drug Offenses") ~ 3,             
             offense_level=="Felony" & offense_type%in%c("Other Felony") ~ 4,
             
             
             offense_level=="Misdemeanor" & offense_type%in%c("Assaultive",
                                                              "Weapons Offenses") ~ 5,
             offense_level=="Misdemeanor" & offense_type%in%c("Theft",
                                                              "Other Property") ~ 6,
             offense_level=="Misdemeanor" & offense_type%in%c("Drug Offenses") ~ 7,             
             offense_level=="Misdemeanor" & offense_type%in%c("Other Misdemeanor") ~ 8,
             offense_level=="CINS" ~ 9,
             offense_level=="Violation of Court Order" ~ 10, 
             offense_level=="Contempt" ~ 11, 
             offense_level=="Other" ~ 12, 
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_level_type_combined_grouped = factor(offense_level_type_combined_grouped,
         levels = c(1,2,3,4,5,6,7,8,9,10,11,12),
         labels = c("Felony, Violent",
                    "Felony, Property",
                    "Felony, Drug",
                    "Felony, Other",
                    "Misdemeanor, Violent",
                    "Misdemeanor, Property",
                    "Misdemeanor, Drug",
                    "Misdemeanor, Other",
                    "CINS",
                    "VOP",
                    "Contempt",
                    "Other")),
         ### now create variable for offense type only 
         offense_type_grouped = 
           case_when(
             offense_type%in%c("Homicide",
                               "Sexual Assault", 
                               "Assaultive",
                               "Weapons Offenses", 
                               "Robbery",
                               "Other Violent") ~ 1,
             offense_type%in%c("Burglary", 
                               "Theft", 
                               "Other Property") ~ 2,
             offense_type%in%c("Drug Offenses") ~ 3,             
             offense_type%in%c("Other Felony","Other Misdemeanor") ~ 4,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_type_grouped = factor(offense_type_grouped,
         levels = c(1,2,3,4),
         labels = c("Violent",
                    "Property",
                    "Drug",
                    "Other"))) %>% 
  mutate(risk_level = 
           case_when(
             risk_level=="Low Risk" ~ 1,
             risk_level%in%c("Medium-Low Risk",
                             "Medium-High Risk",
                             "Moderate Risk") ~ 2,
             risk_level=="High Risk" ~ 3,             
             risk_level=="Unknown" ~ 4,
             risk_level=="Not Administered" ~ 5,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         risk_level = factor(risk_level,
         levels = c(1,2,3,4,5),
         labels =  c("Low Risk", 
                     "Moderate Risk", 
                     "High Risk",
                     "Unknown",
                     "Not Administered")),
         needs_level = 
           case_when(
             needs_level=="Low Needs" ~ 1,
             needs_level=="Moderate Needs" ~ 2,
             needs_level=="High Needs" ~ 3,             
             needs_level=="Unknown" ~ 4,
             needs_level=="Not Administered" ~ 5,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         needs_level = factor(needs_level,
         levels = c(1,2,3,4,5),
         labels = c("Low Needs", 
                    "Moderate Needs", 
                    "High Needs",
                    "Unknown",
                    "Not Administered")))
    
### de-duplicate in two steps here:
### first use doi=="primary" (this is the primary offense at disposition)
### then de-dup by offense severity if there are still more than one offense per referral
### we ultimately want a de-duplicated dataframe with only the most serious offense kept per referral
offenses_clean_de_dup <- offenses_clean %>% 
  filter(doi=="Primary") %>% 
  arrange(unique_referral_id,
          offense_level_type_combined_grouped) %>% 
  distinct(unique_referral_id,
           .keep_all = TRUE) %>% 
  ### rename columns with duplicate names across files to indicate where data initially came from 
  dplyr::rename(offense_citation_number = citation_number,
                offense_disposition = disposition,
                offense_disposition_date = disposition_date,
                offense_referral_risk_level = risk_level,
                offense_referral_needs_level =  needs_level)

### now create additional dataframe with offense data for referral history 
### add "prior_" as prefix to all columns to clarify this for eventual join (where we will already have offense data linked to supervision)
prior_offenses_clean_de_dup <- offenses_clean_de_dup %>% 
  rename_with(~ paste0("prior_", .),
              -unique_id)

#############################################
### clean and de-dup violations dataframe
#############################################

### business rule: need to de-dup violations file -- keeping one unique_id and referral_id -- with most serious violation kept (new offense over technical over other) per referral id

### ask Dallas County if duplicates indicate multiple violations or not

violations_clean_de_dup <- violations %>% 
  filter(!is.na(violation_date)) %>% ### just double checking since we'll need violation_date for later joins; no records dropped
  mutate(disposition_date_no_missing_values = ifelse(!is.na(disposition_date)==TRUE,
                                                     disposition_date,
                                                     filed_date)) %>%
  ### clean dates and create years for potential grouping in future trend analysis
  mutate(unique_violation_referral_id = paste0(unique_id,violation_referral_number),
         unique_violation_disposition_id = paste0(unique_id,disposition_date_no_missing_values),
         violation_date = ymd(as_date(violation_date)),
         filed_date = ymd(as_date(filed_date)),
         prosecutor_action_date = ymd(as_date(prosecutor_action_date)),
         disposition_date = ymd(as_date(disposition_date)),
         violation_date_year = year(violation_date)) %>% 
  ### rename columns with duplicate names across files to indicate where data initially came from 
  dplyr::rename(violation_filed_date = filed_date,
                violation_prosecutor_action_date = prosecutor_action_date,
                violation_disposition_date = disposition_date,
                violation_disposition = disposition,
                violation_offense_description = offense_description,
                violation_prosectur_action = prosecutor_action) %>% 
  ### create factor variable for violation type based
  ### need to confirm hierarchy with team
  mutate(violation_severity = case_when(
    violation_offense_description%in%c("VIOL OF COURT ORDER  - NEW OFFENSE",
                   "VIOL OF COURT ORDER (DET SENT PROB) -NEW OFF") ~ 1,
    violation_offense_description%in%c("VIOL OF COURT ORDER  - TECHNICAL",
                   "VIOL OF COURT ORDER (DET SENT PROB) -TECHNICAL") ~ 2,
    violation_offense_description%in%c("ADMINISTRATIVE HOLD",
                   "MODIFY DISPOSITION - NO VIOLATION",
                   "REOPEN DISPOSITION",
                   "VIOLATIONS OF CONDITIONS OF RELEASE (VCR)") ~ 3,
    TRUE ~ as.numeric(NA)),
    ### use factor function to assign labels to values
    violation_severity_factor = factor(violation_severity,
                                       levels = c(1,2,3),
                                       labels = c("New Offense",
                                                  "Technical Violation",
                                                  "Other"))) %>%
  mutate(violation_technical_flag = ifelse(violation_severity==2,
                                           1,0),
         violation_new_offense_flag = ifelse(violation_severity==1,
                                           1,0),
         violation_other_flag = ifelse(violation_severity==3,
                                           1,0)) %>% 

  group_by(unique_violation_referral_id) %>% 
  mutate(new_offense_violation_count = sum(violation_new_offense_flag,
                                           na.rm = TRUE),
         technical_violation_count = sum(violation_technical_flag,
                                           na.rm = TRUE),
         other_violation_count = sum(violation_other_flag,
                                           na.rm = TRUE)) %>% 
  ungroup() %>% 
  ### keep most serious violation as coded by Dallas County
  filter(primary_offense_at_disposition=="Yes") %>% 
  
  ### need clarity on missing disposition information/missing primary_offense_at_disposition values
  ### are these just recent cases w/o disposition at time of data pull and should be dropped?
  
  ## now de-dup by violation referral ID -- keeping most serious violation according
  ## to our coding
  ## this only affects violations with missing 'primary_offense_at_disposition' or instances
  ## where one violation referral has multiple violations as primary offense
  arrange(unique_violation_referral_id,
          violation_severity) %>%
  ### some violation referrals have multiple individual violations considered primary_offense_at_disposition -- we've already created the important referral-flag/columns so it's okay to de-dup here (if we end up exploring specific types of technicals, we will need to revisit this as we're just randomly keeping one of potentially several technical violations here)
  distinct(unique_violation_referral_id,
           .keep_all = TRUE)
```

<br>

# Supervision File  

**Data Elements:** 

* Unique ID

* Complaint Number

* Charge Disposed to Supervision

* Supervision Type

* Supervision Risk Level

* Mental Health Need

* Substance Use Need

* Prior Referrals

* Supervision Start Date

* Supervision End Date

* TV

* Number of TV During Supervision

* Number of New Referrals

* New Referral

* Supervision Outcome

* Supervision Length of Stay

* Probation Extended Due to TV

* Sent to Residential Placement Due to TV

* Committed Due to TV

* Age at Start of Supervision

* Sex

* Race / Ethnicity

<br><br>

## Join 1. Join of `supervision_clean` and `child_clean`

Create file that is unique by referral and supervision period

```{r warning=FALSE}
### left join of child file to supervision file in order to see if there is much missingness
### i.e. are there supervision records without demo records? 
supervision_child_join_1 <- 
  left_join(supervision_clean,
            child_clean,
            by = "unique_id") %>% ### join looks good; all records join
  ### calculate age at start of supervision
  ### divide by 365 to convert days to years (there is no year option for difftime)
  mutate(age_at_start_of_supervision = as.numeric(difftime(supervision_begin_date,
                                                                    birth_date,
                                                                    units="days"))/365)

```

<br><br>

## Join 2. Join of `supervision_child_join_1` and `supervision_extension_clean`

File will now be unique by referral, supervision period, and supervision extension

```{r warning=FALSE}
### left join of base file and supervision extension file in order to see if there is much missingness
### nothing is likely to look off here as we don't expect to have supervision extension information for everyone
### there are no supervision extension records without base supervision records which is a good sign 
supervision_child_join_2 <- 
  left_join(supervision_child_join_1,
            supervision_extension_clean,
            by = "unique_supervision_id")  

```

<br><br>

## Join 3. Join of `supervision_child_join_2` and `supervision_level_clean`

File will now be unique by referral, supervision period, supervision extension, and supervision level 

```{r warning=FALSE}
### left join of base file and supervision level file in order to see if there is much missingness
supervision_child_join_3 <- 
  left_join(supervision_child_join_2,
            supervision_level_clean,
            by = "unique_supervision_id")  ### join looks good; all records join (which makes sense as all supervision records should have at least one supervision level record)
```

<br><br>

## Join 4. Join of `supervision_child_join_3` and `offenses_clean_de_dup`

Using a left join only joins offense records that led to supervision/disposition to supervision. Later, should I also join just by unique_id to capture offense records which occurred during supervision? The offense file is already de-duped by referral -- keeping the most serious offense -- so the file will still be unique by referral, supervision period, supervision extension, and supervision level 

```{r warning=FALSE}
### create offense file specific to this join -- only capturing offenses with dispositions of supervision 
offenses_clean_de_dup_initial_join <- offenses_clean_de_dup %>% 
  dplyr::select(unique_id,
                referral_number,
                offense_date,
                referral_date,
                referral_type,
                offense_citation_number,
                offense_level_type_combined_grouped,
                offense_level,
                offense_type,
                offense_type_grouped,
                offense_description,
                offense_disposition,
                offense_disposition_date:offense_disposition_year,
                unique_offense_id,
                unique_offenses_per_referral_count:unique_cins_offenses_per_referral_count)

### left join of offenses_clean_de_dup_initial_join file to supervision_child_join_3 file 
supervision_child_join_offenses_4 <- 
  left_join(supervision_child_join_3,
            offenses_clean_de_dup_initial_join,
            by = c("unique_id",
                   "referral_number")) %>%  ### only offense records with supervision dispositions will join (the supervisions file is our base cohort); this explains the records in offenses_clean_de_dup_initial_join that did not join to supervision_child_join_3
  ### now calculate age at time of referrals
  ### divide by 365 to convert days to years (there is no year option for difftime)
  mutate(age_at_referral = as.numeric(difftime(referral_date,
                                               birth_date,
                                               units="days"))/365)
```

<br><br>

## Join 5. Join of `supervision_child_join_3` and `prior_offenses_clean_de_dup` (for historic offense data this time)

Join just by unique_id to capture offense records which occurred before supervision (using dates to filter on this criteria). The offense file is already de-duped by referral -- keeping the most serious offense -- so the file will still be unique by referral, supervision period, supervision extension, and supervision level 

**Logic for filter:** `prior_offenses_clean_de_dup$prior_referral_date` < `supervision_child_join_offenses_4$referral_date`

```{r warning=FALSE}
### create offense file specific to this join -- only capturing referrals that occurred prior to supervision periods
### we need to do this in two steps to ensure we don't accidentally drop individuals without prior referrals from our sample when filtering 
prior_offenses_clean_de_dup_to_join <- prior_offenses_clean_de_dup %>% 
  dplyr::select(unique_id,
                prior_referral_number,
                prior_unique_referral_id,
                prior_referral_date,
                prior_referral_type,
                prior_offense_level_type_combined_grouped,
                prior_offense_level,
                prior_offense_type,
                prior_offense_description,
                prior_offense_disposition,
                prior_offense_disposition_date:prior_offense_disposition_year,
                prior_unique_offenses_per_referral_count:prior_unique_cins_offenses_per_referral_count) %>% 
  ### right join of prior_offenses_clean_de_dup_to_join file to supervision_child_join_offenses_4 file 
  right_join(supervision_child_join_offenses_4,
             by = "unique_id") %>% 
  ### only keep records which are truly prior to supervision period (prior to the referral date of the supervision record)
  filter(prior_referral_date < referral_date) %>%  
  ### calculate number of prior referrals by grouping by unique_id
  group_by(unique_id) %>% 
  mutate(prior_overall_referral_count = n_distinct(prior_unique_referral_id,
                                                         na.rm = TRUE),
         prior_felony_referral_count = n_distinct(prior_unique_referral_id[prior_offense_level=="Felony"],
                                                         na.rm = TRUE),
         prior_misd_referral_count = n_distinct(prior_unique_referral_id[prior_offense_level=="Misdemeanor"],
                                                         na.rm = TRUE),
         prior_cins_referral_count = n_distinct(prior_unique_referral_id[prior_offense_level=="CINS"],
                                                         na.rm = TRUE)) %>% 
  ungroup() %>% 
  ### only keep individual level variables on prior referrals
  dplyr::select(unique_id,
                prior_overall_referral_count:prior_cins_referral_count) %>% 
  ### no de-dup by individual
  distinct(unique_id,
           .keep_all=TRUE)

### left join of prior_offenses_clean_de_dup_to_join file to supervision_child_join_offenses_4 file 
supervision_child_join_offenses_5 <- 
  left_join(supervision_child_join_offenses_4,
            prior_offenses_clean_de_dup_to_join,
            by = c("unique_id")) 
```


<br><br>

## Join 5. Join of `supervision_child_join_offenses_5` and `violations_clean_de_dup`

Using a left join only joins offense records that led to supervision/disposition to supervision. Later, should I also join just by unique_id to capture offense records which occurred during supervision? The offense file is already de-duped by referral -- keeping the most serious offense -- so the file will still be unique by referral, supervision period, supervision extension, and supervision level 

**Logic to double check:** only keeping violation records where the violation_date>=supervision_begin_date & violation_date<=supervision_end_date

```{r warning=FALSE}
### left join of violations_clean file to supervision_child_join_offenses_5 file 
supervision_child_join_offenses_violatons_6 <- 
  left_join(supervision_child_join_offenses_5,
            violations_clean_de_dup,
            by = c("unique_id")) %>% ### this is a many to many join so there are now lots of records (all violations joining to all supervisions/supervision extensions/supervision levels)
  ### now we need to filter on date -- only keeping violation records where the violation_date>=supervision_begin_date & violation_date<=supervision_end_date
  ### first create fake end date for records where the end date is blank; since this indicates that supervision was ongoing at time of data pull, we still want to include violations that occurred so changing NA to '2030-01-01' in new variable for the following filter
  mutate(supervision_end_date_missing_include = ifelse(is.na(supervision_end_date)==TRUE,
                                       ymd(as_date("2030-01-01")),
                                       ymd(as_date(supervision_end_date))),
         supervision_end_date_missing_include = ymd(as_date(supervision_end_date_missing_include)),
         ### flag records with no joining violation information using violation_referral_number
         no_violation_records_joined = ifelse(is.na(violation_referral_number==TRUE),
                                       1,0)) %>% 
  ### we only want to keep either (1) supervision records with no violations or (2) supervision records with violation records when those violations occurred during the period of supervision  
  filter(no_violation_records_joined==1 | (violation_date>=supervision_begin_date & violation_date<=supervision_end_date_missing_include)) %>% 
  group_by(unique_supervision_id) %>% 
  ### count of referrals linked to any violation (using no_violation_records_joined), technical violations, and new offense violations
  mutate(overall_violation_referral_count = n_distinct(violation_referral_number[no_violation_records_joined==0],
                                                         na.rm = TRUE),
         technical_violation_referral_count = n_distinct(violation_referral_number[no_violation_records_joined==0 & violation_severity=="Technical Violation"],
                                                         na.rm = TRUE),
         new_offense_violation_referral_count = n_distinct(violation_referral_number[no_violation_records_joined==0 & violation_severity=="New Offense"],
                                                           na.rm = TRUE)
         # technical_violation_referral_count_in_2017 = n_distinct(violation_referral_number[no_violation_records_joined==0 & violation_severity=="Technical Violation" & violation_date_year==2017],
         #                                                 na.rm = TRUE),
         # technical_violation_referral_count_in_2018 = n_distinct(violation_referral_number[no_violation_records_joined==0 & violation_severity=="Technical Violation" & violation_date_year==2018],
         #                                                 na.rm = TRUE),
         # technical_violation_referral_count_in_2019 = n_distinct(violation_referral_number[no_violation_records_joined==0 & violation_severity=="Technical Violation" & violation_date_year==2019],
         #                                                 na.rm = TRUE),
         # technical_violation_referral_count_in_2020 = n_distinct(violation_referral_number[no_violation_records_joined==0 & violation_severity=="Technical Violation" & violation_date_year==2020],
         #                                                 na.rm = TRUE),
         # technical_violation_referral_count_in_2021 = n_distinct(violation_referral_number[no_violation_records_joined==0 & violation_severity=="Technical Violation" & violation_date_year==2021],
         #                                                 na.rm = TRUE)
         ) %>% 
  ungroup() %>% 
  ### now de-dup by supervision record to keep same row count as before join 
  distinct(unique_supervision_id,
           .keep_all=TRUE) %>% 
  mutate(technical_violation_flag = ifelse(technical_violation_referral_count>0 & !is.na(overall_violation_referral_count)==TRUE,
                                           1,0),
         overall_violation_referral_flag = ifelse(overall_violation_referral_count>0 & !is.na(overall_violation_referral_count)==TRUE,
                                                  1,0))
  
```

<br><br>

```{r warning=FALSE}
### select final variables we want for supervision analytic file
prelim_dallas_county_av_supervision_analytic_file <- supervision_child_join_offenses_violatons_6 

# %>%
#   dplyr::select(unique_supervision_id,
#                 referral_number,
#                 unique_youth_id = unique_id, 
#                 offense_citation_number,
#                 offense_description,
#                 offense_level,
#                 offense_type_grouped,
#                 offense_level_type_combined_grouped,
#                 supervision_type,
#                 referral_type,
#                 offense_referral_risk_level,
#                 offense_referral_needs_level,
#                 mental_health_needs,
#                 mental_health_needs_indicator,
#                 substance_use_need,
#                 prior_overall_referral_count,
#                 prior_felony_referral_count,
#                 prior_misd_referral_count,
#                 prior_cins_referral_count,
#                 supervision_begin_date,
#                 supervision_end_date,
#                 technical_violation_flag,
#                 technical_violation_referral_count,
#                 new_offense_violation_referral_count,
#                 overall_violation_referral_count,
#                 overall_violation_referral_flag,
#                 supervision_outcome,
#                 overall_supervision_los_days,
#                 probation_supervision_los_days,
#                 detention_supervision_los_days,
#                 placement_supervision_los_days,
#                 none_supervision_los_days,
#                 warrant_supervision_los_days,
#                 age_at_start_of_supervision,
#                 gender_clean,
#                 race_clean)


###############
### export file
###############

### set sharepoint path using sp_data_path and file.path function 
sharepoint_jj_av_dallas_analytic_data <- file.path(sp_data_path,"Data/analysis")

write_delim(prelim_dallas_county_av_supervision_analytic_file,
            file.path(sharepoint_jj_av_dallas_analytic_data,
                      "prelim_dallas_county_av_supervision_analytic_file.txt"),
                      delim = "|")

```

