---
title: "Building the Analytic Files"
format: html
---

In this syntax, we'll import all of the Dallas County files provided and create two analytic files based on the templates in the second and third tabs here: https://csgorg.sharepoint.com/:x:/s/Team-JC-Research-JJ_AV/EZ-RDTetlZVCoiQxlasiboEBhsT7WNlx5v0qR7sDBji1-A?e=eggzRJ

See `Codebooks` and `Data Diagram` tabs for more information on each individual data file. 

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### pull in dallas data from raw data folder

### set sharepoint path using file.path function (path has different structure than usual so not using csg_sp_path from csgjcr package)
sharepoint_jj_av_dallas_raw_data <- file.path("C:/Users/abyrum/The Council of State Governments/JC Research - JJ_AV - JJ_AV/Dallas/Data/raw")

### using purrr::map, import list of tabs from excel worksheet
dallas_raw_tab_list <- purrr::map(purrr::set_names(excel_sheets(file.path(sharepoint_jj_av_dallas_raw_data,
                                                              "Dallas County (10.1.2017 - 9.30.2022).xlsx"))),
                      read_excel, 
                      path = file.path(sharepoint_jj_av_dallas_raw_data,"Dallas County (10.1.2017 - 9.30.2022).xlsx")) %>% 
  purrr::map(janitor::clean_names)

### clean names of all imported tabs before converting to dataframes
names(dallas_raw_tab_list) <- janitor::make_clean_names(names(dallas_raw_tab_list))

### then convert list of tabs to distinct dataframes with names from tabs
purrr::map(names(dallas_raw_tab_list),
           ~assign(.x, 
                   dallas_raw_tab_list[[.x]], 
        envir = .GlobalEnv)) 
```

```{r warning=FALSE}
#############################################
### clean and de-dup child dataframe
### this is our base demo file for the sample
#############################################
child_clean <- child %>% 
  distinct(unique_id,
           .keep_all=TRUE) %>% ### no records dropped
  ### clean race/ethnicity and gender
  ### use factor function to assign labels to values
  mutate(race_clean = case_when(
    race=="Asian or Pacific Islander" & ethnicity!="Hispanic" ~ 1,
    race=="Black" & ethnicity!="Hispanic" ~ 2,
    ethnicity=="Hispanic" ~ 3,
    race=="White" & ethnicity!="Hispanic" ~ 4,
    race %in% c("Unknown","American Indian or Alaskan Native") & ethnicity!="Hispanic" ~ 5,
    TRUE ~ as.numeric(NA)),
    race_clean = factor(race_clean,
         levels = c(1,2,3,4,5),
         labels = c("Asian", "Black", "Hispanic", "White", "Other"))) %>% 
  mutate(gender_clean = case_when(
    gender=="Female" ~ 1,
    gender=="Male" ~ 2,
    TRUE ~ as.numeric(NA)),
    gender_clean = factor(gender_clean,
         levels = c(1,2),
         labels = c("Female", "Male"))) %>% 
  ### clean dates
  mutate(birth_date = ymd(as_date(birth_date))) 

########################################
### clean and de-dup supervision dataframe
########################################
supervision_clean <- supervision %>% 
  distinct(unique_id,
           referral_number,
           supervision_begin_date,
           .keep_all=TRUE) %>% ### 1 record dropped (note: 170 recods have duplicated IDs but different begin dates)
  ### clean dates and create years for potential grouping in future trend analysis
  mutate(supervision_begin_date = ymd(as_date(supervision_begin_date)),
         supervision_end_date = ymd(as_date(supervision_end_date)),
         supervision_begin_year = year(supervision_begin_date),
         supervision_end_year = year(supervision_end_date)) %>% 
  ### create unique referral ID possible filtering, joining, or counting
  mutate(unique_referral_id = paste0(unique_id,
                                     referral_number)) 

########################################
### clean and de-dup offenses dataframe
########################################
offenses_clean <- offenses %>% 
  distinct(unique_id,
           referral_number,
           offense_id,
           .keep_all=TRUE) %>% ### no records dropped
  ### clean dates and create years for potential grouping in future trend analysis
  mutate(offense_date = ymd(as_date(offense_date)),
         referral_date = ymd(as_date(referral_date)),
         disposition_date = ymd(as_date(excel_numeric_to_date(as.numeric(as.character(disposition_date)), 
                                                  date_system = "modern"))),
         offense_year = year(offense_date),
         referral_year = year(referral_date),
         disposition_year = year(disposition_date)) %>% 
  ### create unique referral ID and unique offense ID for possible filtering or counting
  mutate(unique_referral_id = paste0(unique_id,
                                     referral_number),
         unique_offense_id = paste0(unique_id,
                                    referral_number,
                                    offense_id)) %>% 
  ### calculate number of offenses per referral by grouping by unique_referral_id
  group_by(unique_referral_id) %>% 
  mutate(unique_offenses_per_referral_count = n_distinct(unique_offense_id,
                                                         na.rm = TRUE),
         unique_felony_offenses_per_referral_count = n_distinct(unique_offense_id[offense_level=="Felony"],
                                                         na.rm = TRUE),
         unique_misdemeanor_offenses_per_referral_count = n_distinct(unique_offense_id[offense_level=="Misdemeanor"],
                                                         na.rm = TRUE),
         unique_cins_offenses_per_referral_count = n_distinct(unique_offense_id[offense_level=="CINS"],
                                                         na.rm = TRUE)) %>% 
  ungroup() %>% 
  ### create factor variable for offense severity based on hierarchy outlined in table 11 on descriptives page
  ### need to confirm order with team
  mutate(offense_level_type_severity = 
           case_when(
             offense_level=="Felony" & offense_type%in%c("Homicide",
                                                         "Sexual Assault", 
                                                         "Assaultive",
                                                         "Weapons Offenses", 
                                                         "Robbery",
                                                         "Other Violent") ~ 1,
             offense_level=="Felony" & offense_type%in%c("Burglary", 
                                                         "Theft", 
                                                         "Other Property") ~ 2,
             offense_level=="Felony" & offense_type%in%c("Drug Offenses") ~ 3,             
             offense_level=="Felony" & offense_type%in%c("Other Felony") ~ 4,
             
             
             offense_level=="Misdemeanor" & offense_type%in%c("Assaultive",
                                                              "Weapons Offenses") ~ 5,
             offense_level=="Misdemeanor" & offense_type%in%c("Theft",
                                                              "Other Property") ~ 6,
             offense_level=="Misdemeanor" & offense_type%in%c("Drug Offenses") ~ 7,             
             offense_level=="Misdemeanor" & offense_type%in%c("Other Misdemeanor") ~ 8,
             offense_level=="CINS" ~ 9,
             offense_level=="Violation of Court Order" ~ 10, 
             offense_level=="Contempt" ~ 11, 
             offense_level=="Other" ~ 12, 
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_level_type_severity = factor(offense_level_type_severity,
         levels = c(1,2,3,4,5,6,7,8,9,10,11,12),
         labels = c("Felony, Violent",
                    "Felony, Property",
                    "Felony, Drug",
                    "Felony, Other",
                    "Misdemeanor, Violent",
                    "Misdemeanor, Property",
                    "Misdemeanor, Drug",
                    "Misdemeanor, Other",
                    "CINS",
                    "VOP",
                    "Contempt",
                    "Other"))) 

### now create a de-duplicated dataframe with most serious offense kept per referral
offenses_clean_de_dup <- offenses_clean %>% 
  arrange(unique_referral_id,
          offense_level_type_severity) %>% 
  distinct(unique_referral_id,
           .keep_all = TRUE)
  
```

<br>

# Supervision File  

**Data Elements:** 

* Unique ID

* Complaint Number

* Charge Disposed to Supervision

* Supervision Type

* Supervision Risk Level

* Mental Health Need

* Substance Use Need

* Prior Referrals

* Supervision Start Date

* Supervision End Date

* TV

* Number of TV During Supervision

* Number of TV 2017

* Number of TV 2018

* Number of TV 2019

* Number of TV 2020

* Number of TV 2021

* Number of New Referrals

* New Referral

* Supervision Outcome

* Supervision Length of Stay

* LOS 2017

* LOS 2018

* LOS 2019

* LOS 2020

* LOS 2021

* Probation Extended Due to TV

* Sent to Residential Placement Due to TV

* Committed Due to TV

* Age at Start of Supervision

* Sex

* Race / Ethnicity

<br><br>

## Join 1. Join of `supervision_clean` and `child_clean`

Create file that is unique by referral

```{r warning=FALSE}
### left join of child file to supervision file in order to see if there is much missingness
### i.e. are there supervision records without demo records? 
supervision_child_join_1 <- 
  left_join(supervision_clean,
            child_clean,
            by = "unique_id") %>% ### join looks good; all records join
  ### calculate age at start of supervision
  ### divide by 365 to convert days to years (there is no year option for difftime)
  mutate(age_at_start_of_supervision = as.numeric(difftime(supervision_begin_date,
                                                                    birth_date,
                                                                    units="days"))/365)

```

<br><br>

## Join 2. Join of `supervision_child_join_1` and `offenses_clean_de_dup`

Only joins offense records that led to supervision. Later, should I also join just by unique_id to capture offense records which occurred during supervision?

```{r eval=FALSE,warning=FALSE}
### create offense file specific to this join -- only capturing offenses with dispositions of supervision 
offenses_clean_de_dup_initial_join <- offenses_clean_de_dup %>% 
  dplyr::select(unique_id,
                referral_number,
                offense_date,
                referral_date,
                referral_type,
                offense_level_type_severity,
                offense_level,
                offense_type,
                offense_description,
                disposition_offense_file = disposition,
                disposition_date:disposition_year,
                unique_offense_id,
                unique_offenses_per_referral_count:unique_cins_offenses_per_referral_count)

### left join of supervision_child_join_1 file to offenses_clean_de_dup file in order to see if there is much missingness
### i.e. are there offenses without demo records? 
supervision_child_join_offenses_2 <- 
  left_join(supervision_child_join_1,
            offenses_clean_de_dup_initial_join,
            by = c("unique_id",
                   "referral_number")) ### only offense records with supervision dispositions will join (the supervisions file is our base cohort)
```

<br><br>

