---
title: "Who Receives Technical Violations?"
format: html
---

**Who receives technical violations?**

1. What proportion of youth on probation supervision receive a technical violation during a probation term? How does this vary across race/ethnicity, sex, age, and risk level? 

2. What proportion of violations filed by a PO are rejected by supervisor or prosecutor?


```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog","ggtext","ggpattern")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### set project path with csg_get_project_path (just once)
# csg_set_project_path(project = "jj-av-dallas",
# sp_folder = "C:/Users/abyrum/The Council of State Governments/JC Research - JJ_AV - JJ_AV/Dallas", force = TRUE)

### data path
sp_data_path <- csg_get_project_path("jj-av-dallas")

## viz output path
sp_viz_output_path <- paste0(sp_data_path,"/output/r_output_presentation")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
###############################
### import dallas analytic file
###############################

### set sharepoint path using sp_data_path and file.path function 
sharepoint_jj_av_dallas_analytic_data <- file.path(sp_data_path,"Data/analysis")

df_dallas_county_av_supervision_analytic_file <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "df_dallas_county_av_supervision_analytic_file.txt"),
                      delim = "|") %>% 
  mutate(offense_referral_risk_level = 
           case_when(
             offense_referral_risk_level=="Low Risk" ~ 1,
             offense_referral_risk_level%in%c("Medium-Low Risk",
                             "Medium-High Risk",
                             "Moderate Risk") ~ 2,
             offense_referral_risk_level=="High Risk" ~ 3,             
             offense_referral_risk_level%in%c("Unknown/Not Administered") ~ 4,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_risk_level = factor(offense_referral_risk_level,
         levels = c(1,2,3,4),
         labels =  c("Low Risk", 
                     "Moderate Risk", 
                     "High Risk",
                     "Unknown/Not Administered")),
         offense_referral_needs_level = 
           case_when(
             offense_referral_needs_level=="Low Needs" ~ 1,
             offense_referral_needs_level=="Moderate Needs" ~ 2,
             offense_referral_needs_level=="High Needs" ~ 3,             
             offense_referral_needs_level%in%c("Unknown/Not Administered") ~ 4,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_needs_level = factor(offense_referral_needs_level,
         levels = c(1,2,3,4),
         labels = c("Low Needs", 
                    "Moderate Needs", 
                    "High Needs",
                    "Unknown/Not Administered"))) |> 
  ### remove FY 2023 Completion (year is incomplete based on timing of data pull) 
  filter(supervision_end_fy!=2023)

```

<br>

# 1. Technical Violations Overview

**NOTE:** All analysis of technical violations in this section (e.g., supervision episodes with at least one technical violation) refers to the filing of any technical violations regardless of outcome/disposition. 

<br>

## Table 1. By FY: Percentage of Supervision Episodes/Referrals with a Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
### create denominator -- unique referrals for entire sample
unique_referrals_sample_denom <- n_distinct(df_dallas_county_av_supervision_analytic_file$unique_id,
                                            df_dallas_county_av_supervision_analytic_file$referral_number)

### create denominator -- unique supervision episodes
unique_supervision_episode_denom <- n_distinct(df_dallas_county_av_supervision_analytic_file$unique_referral_id)

### create denominator -- unique youth for entire sample
unique_youth_sample_denom <- n_distinct(df_dallas_county_av_supervision_analytic_file$unique_id)

### unique youth and referrals per FY
df_technical_violations_per_year <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(supervision_end_fy) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (row %)` = scales::percent(n_distinct(unique_referral_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (row %)` = scales::percent(n_distinct(unique_referral_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Completion` = supervision_end_fy) %>% 
  mutate(`FY of Completion` = as.character(`FY of Completion`))

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (row %)` = scales::percent(n_distinct(unique_referral_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (row %)` = scales::percent(n_distinct(unique_referral_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`FY of Completion` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

## slide 28
```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and referrals per FY of exit
df_modifications_extensions_per_year_viz <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(supervision_end_fy) %>% 
  dplyr::summarise(percent = n_distinct(unique_referral_id[technical_violation_flag==1])/n_distinct(unique_referral_id)) %>% 
  ungroup() |> 
  mutate(group = "dallas")

###geom_line 
ggplot(data = df_modifications_extensions_per_year_viz, aes(x = supervision_end_fy, y = percent
                                                            ,
                                                            color = group,
                                                            group = group
                                                            )) +
  geom_line(color = "black", size = 2.75) +
  geom_line(size = 2.2) +
  geom_point(color = "black", size = 4) +
  geom_point(size = 3.5) +
  labs(x = "Fiscal Year", y = "Supervision Episodes with\nTechnical Violation (%)", color=NULL, title = NULL, caption = NULL) +
  scale_y_continuous(label=scales::percent_format(accuracy=1),
                     limits = c(min(0), 
                                max(.32))) +
  theme(legend.position = "none",
        legend.title = element_text(hjust = 0.5,size = 13),
        legend.text = element_text(size = 13),
        panel.grid.major.x = element_blank(),      
        plot.title = element_text( hjust = 0.5),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.title.x = element_text(size = 16,margin = margin(t = 15)),
        axis.title.y = element_text(size = 16,margin = margin(r = 15)),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5)) +  
  scale_color_manual(values = c("#1F4A58")) +
  scale_fill_manual(values = c("#1F4A58")) +
  geom_label_repel(aes(label = scales::percent(as.numeric(percent),
                                               accuracy = 0.1),
                    fill = group
                    ),
                   hjust = .1,
                   label.padding = 0.2,
                   box.padding = 0.2,
                   color = "white",
                   size = 5,
                   segment.color = NA,
                   fontface = "bold",
                   na.rm = TRUE,
                   show.legend = FALSE)

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_28_episodes_with_technical_violations.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>

## Table 2. By Race/Ethnicity: Percentage of Supervision Episodes/Referrals with a Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_technical_violations_race <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (row %)` = scales::percent(n_distinct(unique_referral_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (RRI to White youth)` = round((n_distinct(unique_referral_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`)/0.1184573, digits = 1),
            `Supervision Episodes, with at least one new offense violation (row %)` = scales::percent(n_distinct(unique_referral_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (RRI to White youth)` = round((n_distinct(unique_referral_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`)/0.0261708,digits = 1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean)

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (row %)` = scales::percent(n_distinct(unique_referral_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (RRI to White youth)` = NA,
            `Supervision Episodes, with at least one new offense violation (row %)` = scales::percent(n_distinct(unique_referral_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (RRI to White youth)` = NA) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_technical_violations_race_table <- rbind(df_technical_violations_race,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_race_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

```{r }
### unique youth, referrals, and supervision episodes
df_technical_violations_race <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (row %)` = scales::percent(n_distinct(unique_referral_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (RRI to White youth)` = round((n_distinct(unique_referral_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`)/0.1184573, digits = 1),
            `Supervision Episodes, with at least one new offense violation (row %)` = scales::percent(n_distinct(unique_referral_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (RRI to White youth)` = round((n_distinct(unique_referral_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`)/0.0261708,digits = 1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean)

### remove groups analysis with small sample size
### pull out RRIs for plot
### use gather to shift data from wide to long
df_modifications_extensions_race_rri_viz <- df_technical_violations_race %>% 
  filter(`Race/Ethnicity`%in%c("Black",
                               "Hispanic",
                               "White")) %>% 
  dplyr::select(`Race/Ethnicity`,rri=`Supervision Episodes, with at least one technical violations (RRI to White youth)`) %>% 
  dplyr::filter(`Race/Ethnicity`!="White") %>% 
  mutate(reference = 1)

### plot
ggplot(data = df_modifications_extensions_race_rri_viz, 
       aes(y = rri, 
           x = `Race/Ethnicity`, 
           fill = forcats::fct_rev(`Race/Ethnicity`))) + 
  geom_bar(stat = "identity", 
           position = "dodge"
           # ,color = "gray80"
             ) +
    # geom_bar(aes(y=reference),
    #          stat = "identity", 
    #        position = "dodge", 
    #        fill = "gray80") +
    geom_col_pattern(aes(y=reference),
                   pattern_color = NA,
                   pattern_fill = "gray80",
                   pattern = "stripe"
                   # ,color = "gray80"
                     ) +
  geom_abline(slope=0, 
              intercept=1,  
              col = "#000000", 
              size = 1.5, 
              linetype="dashed") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(limits=c(min(0), 
                                           max(2.05))) +
  scale_fill_manual(values = c("#1F4A58","#87C2D4")) +
  scale_color_manual(values = rev(c("#1F4A58","#87C2D4"))) +
  theme(legend.position = "top",
        legend.title.align=0.5,
        # axis.text.y = element_text(face = "bold", hjust = 1, size = 14),
        # strip.text.x = element_text(face = "bold", vjust = 1.5, size = 14, 
        #                             hjust = 0.5),
          axis.text.y = element_text(face = "bold",size = 14),
        axis.text.x = element_text(face = "bold", hjust = 1, size = 14),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        axis.title.x = element_text(size = 15, margin = margin(t = 15)),
        axis.title.y = element_text(size =15, margin = margin(r = 15))) +
    labs(y = "Relative Rate Index (RRI)", 
         x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  # facet_grid(~ rri_measure) +
 # guides(fill = guide_legend(reverse = TRUE,
 #                             title.position = "top",
 #                             label.position = "bottom",
 #                             keywidth = 3,
 #                             nrow = 1)) +
   guides(fill = FALSE) +
  # geom_label_repel(aes(label = format(round(as.numeric(rri), 
  #                                           digits = 1), 
  #                                     nsmall=1), 
  #                      group = forcats::fct_rev(`Race/Ethnicity`),
  #                      color = `Race/Ethnicity`),
  #                 position = position_dodge(.9),
  #                 direction = 'x',
  #                 hjust = 0.75,
  #                 label.padding = 0.3,
  #                 box.padding = 0.15,
  #                 size = 5,
  #                 fill = "white",
  #                 fontface = "bold",
  #                 na.rm = TRUE,
  #                 show.legend = FALSE) +
  annotate("text", 
           x = 2.53, 
           y = 1.46, 
           label = "This line represents White youth (reference group)", 
           colour = "#000000", 
           size = 3.75, 
           fontface = 2)


### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_30_technical_violation_rate_race_eth_rri.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

```{r }
### unique youth, referrals, and supervision episodes
df_technical_violations_risk_viz <- df_dallas_county_av_supervision_analytic_file |> 
  filter(race_clean%in%c("Black","White","Hispanic")) |> 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(percent = n_distinct(unique_referral_id[technical_violation_flag==1])/n_distinct(unique_referral_id)) %>% 
  ungroup() |> 
  pivot_longer(!race_clean, names_to = "complaint_type", values_to = "percent") 

### plot
### bar plot
ggplot(data = df_technical_violations_risk_viz,
       aes(x = race_clean,
           y = percent,
           fill = race_clean)) + 
  geom_bar(stat = "identity",  
           color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(min(0), 
                                max(.22))) +
  geom_label(
    aes(
      y = percent,
      label = scales::percent(percent,
                              accuracy = 1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 6,
    colour = "white",
    show.legend = FALSE
  ) +
  scale_fill_manual(values = c("#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084")) +
  guides(fill = FALSE) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme_minimal() +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        # axis.text.x = element_markdown(),
        axis.text.y = element_markdown(size = 16),
        axis.text.x = element_text(face = "bold", hjust = 1, size = 16),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_29_technical_violation_race_eth.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>

## Table 3. By Gender: Percentage of Supervision Episodes/Referrals with a Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_technical_violations_risk <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(gender_clean) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (row %)` = scales::percent(n_distinct(unique_referral_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (row %)` = scales::percent(n_distinct(unique_referral_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean)

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
   dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (row %)` = scales::percent(n_distinct(unique_referral_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (row %)` = scales::percent(n_distinct(unique_referral_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Gender` = "Overall")

### combine tables for kable
df_technical_violations_risk_table <- rbind(df_technical_violations_risk,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_risk_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

```{r }
### unique youth, referrals, and supervision episodes
df_technical_violations_risk_viz <- df_dallas_county_av_supervision_analytic_file |> 
  dplyr::group_by(gender_clean) %>% 
  dplyr::summarise(percent = n_distinct(unique_referral_id[technical_violation_flag==1])/n_distinct(unique_referral_id)) %>% 
  ungroup() |> 
  pivot_longer(!gender_clean, names_to = "complaint_type", values_to = "percent") 

### plot
### bar plot
ggplot(data = df_technical_violations_risk_viz,
       aes(x = gender_clean,
           y = percent,
           fill = gender_clean)) + 
  geom_bar(stat = "identity",  
           color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(min(0), 
                                max(.22))) +
  geom_label(
    aes(
      y = percent,
      label = scales::percent(percent,
                              accuracy = 1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 6,
    colour = "white",
    show.legend = FALSE
  ) +
  scale_fill_manual(values = c("#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084")) +
  guides(fill = FALSE) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme_minimal() +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        # axis.text.x = element_markdown(),
        axis.text.y = element_markdown(size = 16),
        axis.text.x = element_text(face = "bold", hjust = 1, size = 16),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_29_technical_violation_gender.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>


## Table 4. By Age: Percentage of Supervision Episodes/Referrals with a Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
### turn age into a factor
df_dallas_county_av_supervision_analytic_file %<>%
 mutate(age_at_referral_clean = factor(age_at_referral_clean,
         levels = c("Less than 12", 
                    "12 to 13",
                    "14 to 16",
                    "17+")))

### unique youth, referrals, and supervision episodes
df_technical_violations_risk <- df_dallas_county_av_supervision_analytic_file %>% 
  filter(!is.na(age_at_referral_clean)) |> 
  dplyr::group_by(age_at_referral_clean) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (row %)` = scales::percent(n_distinct(unique_referral_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (row %)` = scales::percent(n_distinct(unique_referral_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age` = age_at_referral_clean)

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
    filter(!is.na(age_at_referral_clean)) |> 
   dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (row %)` = scales::percent(n_distinct(unique_referral_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (row %)` = scales::percent(n_distinct(unique_referral_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Age` = "Overall")

### combine tables for kable
df_technical_violations_risk_table <- rbind(df_technical_violations_risk,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_risk_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br>

## Table 5. By Risk Level: Percentage of Supervision Episodes/Referrals with a Technical Violation

**Note:** This is the "listed risk level at the time of referral disposition"

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_technical_violations_risk <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (row %)` = scales::percent(n_distinct(unique_referral_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (row %)` = scales::percent(n_distinct(unique_referral_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level)

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
   dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (row %)` = scales::percent(n_distinct(unique_referral_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (row %)` = scales::percent(n_distinct(unique_referral_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_technical_violations_risk_table <- rbind(df_technical_violations_risk,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_risk_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

```{r }
### unique youth, referrals, and supervision episodes
df_technical_violations_risk_viz <- df_dallas_county_av_supervision_analytic_file |> 
    filter(offense_referral_risk_level!="Unknown/Not Administered") |> 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(percent = n_distinct(unique_referral_id[technical_violation_flag==1])/n_distinct(unique_referral_id)) %>% 
  ungroup() |> 
  pivot_longer(!offense_referral_risk_level, names_to = "complaint_type", values_to = "percent") 

### plot
### bar plot
ggplot(data = df_technical_violations_risk_viz,
       aes(x = offense_referral_risk_level,
           y = percent,
           fill = offense_referral_risk_level)) + 
  geom_bar(stat = "identity",  
           color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(min(0), 
                                max(.5))) +
  geom_label(
    aes(
      y = percent,
      label = scales::percent(percent,
                              accuracy = 1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 6,
    colour = "white",
    show.legend = FALSE
  ) +
  scale_fill_manual(values = c("#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084")) +
  guides(fill = FALSE) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme_minimal() +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        # axis.text.x = element_markdown(),
        axis.text.y = element_markdown(size = 16),
        axis.text.x = element_text(face = "bold", hjust = 1, size = 16),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_29_technical_violation_risk.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>

## Slide 12: 

**Note:** This is the "listed risk level at the time of referral disposition"

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_technical_violations_risk_viz <- df_dallas_county_av_supervision_analytic_file %>% 
  ###hereherehere
  filter(offense_referral_risk_level!="Unknown/Not Administered") |> 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`Supervision Episodes` = n_distinct(unique_referral_id)/unique_supervision_episode_denom) %>% 
  ungroup() |> 
  pivot_longer(!offense_referral_risk_level, names_to = "complaint_type", values_to = "percent") 

### plot
### bar plot
ggplot(data = df_technical_violations_risk_viz,
       aes(x = offense_referral_risk_level,
           y = percent,
           fill = offense_referral_risk_level)) + 
  geom_bar(stat = "identity",  
           color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(min(0), 
                                max(.6))) +
  geom_label(
    aes(
      y = percent,
      label = scales::percent(percent,
                              accuracy = 1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 6,
    colour = "white",
    show.legend = FALSE
  ) +
  scale_fill_manual(values = c("#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084")) +
  guides(fill = FALSE) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme_minimal() +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        # axis.text.x = element_markdown(),
        axis.text.y = element_markdown(size = 16),
        axis.text.x = element_text(face = "bold", hjust = 1, size = 16),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_12_all_episodes_risk.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>

## Table 6. By Needs Level: Percentage of Supervision Episodes/Referrals with a Technical Violation

**Note:** This is the "listed needs level at the time of referral disposition"

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_technical_violations_needs <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (row %)` = scales::percent(n_distinct(unique_referral_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (row %)` = scales::percent(n_distinct(unique_referral_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level)

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
   dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (row %)` = scales::percent(n_distinct(unique_referral_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (row %)` = scales::percent(n_distinct(unique_referral_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_technical_violations_needs_table <- rbind(df_technical_violations_needs,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_needs_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br><br>

# 3. Supervisor/Prosecutor Rejections 

**Business Rule:** According to Dallas County, all of the technical violation records without a referral number indicate that a PO filed the violation, but that it was rejected by a supervisor.

**NOTE:** Only about 2% of all violations fit this criteria -- not sure if it warrants analysis (especially anything disaggregated). The Dallas team mentioned several factors to consider regarding rejections in general as well as the small percentage of violations that appear in our sample. A fair amount of informal rejection is possible (possible violations are rejected/not approved before any data would be entered or a violation would actually be filed). PO has to get permission from supervisor before filing a violation so there should be very few rejected violations (i.e., PO's will likely only formally file a violation if they feel confident it will be approved by a supervisor).Thus, 2% really only reflects what is in the data system but likely does not speak to the real trend.

<br><br>
