---
title: "Who Receives Technical Violations?"
format: html
---

**Who receives technical violations?**

1. What proportion of youth on probation supervision receive a technical violation during a probation term? How does this vary across race/ethnicity, sex, and risk level? 

2. Descriptive overview of the population of youth who receive a technical violation during the study period (when technical violation was the primary offense) by race/ethnicity, age category, sex, and risk level  

3. What proportion of violations filed by a PO are rejected by supervisor or prosecutor?


```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### set project path with csg_get_project_path (just once)
# csg_set_project_path(project = "jj-av-dallas",
# sp_folder = "C:/Users/abyrum/The Council of State Governments/JC Research - JJ_AV - JJ_AV/Dallas", force = TRUE)

### data path
sp_data_path <- csg_get_project_path("jj-av-dallas")

### viz output path
# sp_viz_output_path <- paste(sp_data_path, "/Output/r_output_presentation")

```

```{r include=FALSE,message=FALSE,warning=FALSE}
###############################
### import dallas analytic file
###############################

### set sharepoint path using sp_data_path and file.path function 
sharepoint_jj_av_dallas_analytic_data <- file.path(sp_data_path,"Data/analysis")

df_dallas_county_av_supervision_analytic_file <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "df_dallas_county_av_supervision_analytic_file.txt"),
                      delim = "|") %>% 
  mutate(offense_referral_risk_level = 
           case_when(
             offense_referral_risk_level=="Low Risk" ~ 1,
             offense_referral_risk_level%in%c("Medium-Low Risk",
                             "Medium-High Risk",
                             "Moderate Risk") ~ 2,
             offense_referral_risk_level=="High Risk" ~ 3,             
             offense_referral_risk_level=="Unknown" ~ 4,
             offense_referral_risk_level=="Not Administered" ~ 5,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_risk_level = factor(offense_referral_risk_level,
         levels = c(1,2,3,4,5),
         labels =  c("Low Risk", 
                     "Moderate Risk", 
                     "High Risk",
                     "Unknown",
                     "Not Administered")),
         offense_referral_needs_level = 
           case_when(
             offense_referral_needs_level=="Low Needs" ~ 1,
             offense_referral_needs_level=="Moderate Needs" ~ 2,
             offense_referral_needs_level=="High Needs" ~ 3,             
             offense_referral_needs_level=="Unknown" ~ 4,
             offense_referral_needs_level=="Not Administered" ~ 5,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_needs_level = factor(offense_referral_needs_level,
         levels = c(1,2,3,4,5),
         labels = c("Low Needs", 
                    "Moderate Needs", 
                    "High Needs",
                    "Unknown",
                    "Not Administered")))

```

<br>

# 1. Technical Violations Overview

**NOTE:** All analysis of technical violations in this section (e.g., supervision episodes with at least one technical violation) refers to the filing of any technical violations regardless of outcome/disposition. 

<br>

## Table 1. By year: Percentage of Supervision Episodes/Referrals with a Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
### create denominator -- unique referrals for entire sample
unique_referrals_sample_denom <- n_distinct(df_dallas_county_av_supervision_analytic_file$unique_id,
                                            df_dallas_county_av_supervision_analytic_file$referral_number)

### create denominator -- unique supervision episodes
unique_supervision_episode_denom <- n_distinct(df_dallas_county_av_supervision_analytic_file$unique_supervision_id)

### create denominator -- unique youth for entire sample
unique_youth_sample_denom <- n_distinct(df_dallas_county_av_supervision_analytic_file$unique_id)

### unique youth and referrals per year
df_technical_violations_per_year <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(referral_year) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (%)` = scales::percent(n_distinct(unique_supervision_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (%)` = scales::percent(n_distinct(unique_supervision_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Year of Referral` = referral_year) %>% 
  mutate(`Year of Referral` = as.character(`Year of Referral`))

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (%)` = scales::percent(n_distinct(unique_supervision_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (%)` = scales::percent(n_distinct(unique_supervision_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Year of Referral` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(11, bold = TRUE)
```

<br>

## Table 2. By Race/Ethnicity: Percentage of Supervision Episodes/Referrals with a Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_technical_violations_race <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (%)` = scales::percent(n_distinct(unique_supervision_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (%)` = scales::percent(n_distinct(unique_supervision_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean)

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
   dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (%)` = scales::percent(n_distinct(unique_supervision_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (%)` = scales::percent(n_distinct(unique_supervision_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_technical_violations_race_table <- rbind(df_technical_violations_race,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_race_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```


<br>

## Table 3. By Risk Level: Percentage of Supervision Episodes/Referrals with a Technical Violation

**Note:** This is the "listed risk level at the time of referral disposition"

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_technical_violations_risk <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (%)` = scales::percent(n_distinct(unique_supervision_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (%)` = scales::percent(n_distinct(unique_supervision_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level)

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
   dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (%)` = scales::percent(n_distinct(unique_supervision_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (%)` = scales::percent(n_distinct(unique_supervision_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_technical_violations_risk_table <- rbind(df_technical_violations_risk,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_risk_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 4. By Needs Level: Percentage of Supervision Episodes/Referrals with a Technical Violation

**Note:** This is the "listed needs level at the time of referral disposition"

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_technical_violations_needs <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (%)` = scales::percent(n_distinct(unique_supervision_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (%)` = scales::percent(n_distinct(unique_supervision_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level)

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
   dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one technical violations (%)` = scales::percent(n_distinct(unique_supervision_id[technical_violation_flag==1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one new offense violation (%)` = scales::percent(n_distinct(unique_supervision_id[new_offense_violation_count>0 & !is.na(new_offense_violation_count)])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_technical_violations_needs_table <- rbind(df_technical_violations_needs,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_needs_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

# 2. Technical Violations Descriptives

**NOTE:** All analysis of technical violations in this section (e.g., supervision episodes with at least one technical violation) refers to the filing of any technical violation regardless of outcome/disposition -- but where the technical violation was the primary offense/violation. 

**TBD**

<br><br>

# 3. Supervisor/Prosecutor Rejections

**TBD**

<br><br>
