---
title: "What happens to youth as the result of a technical violation?"
format: html
---

**What happens to youth as the result of a technical violation?** 

**1.** 

* Of youth who receive a technical violation as a primary offense, what proportion are placed in a residential facility; detention; committed to state custody? How does this vary across race/ethnicity, sex, and risk level? 

* Of youth who receive a technical violation as a primary offense, what proportion receive an extended supervision episode? 


**2.**

* What is the average length of time a supervision episode is extended as the result of a technical violation? How does this vary across race/ethnicity, sex, and risk level? 



**3.** 

* In Dallas, probation can file a violation to get a kid into a 30 day residential program. The violation does not go to the prosecutor. If the kid is successful in the placement, then the department dismisses the violation. How often does this happen? 



**Double check following coding/grouping of violation dispositions with team:**

* "No Disposition" = "ADJUDICATED - NO DISPOSITION"

* "Probation" = "ADJUDICATED PLACED ON PROBATION", "CONSOLIDATED MULTIPLE CHARGES - ONE DISPOSITION (PROBATION)") 

* "30 Day Residential Program" = "DISMISSED OR WITHDRAWN BY DEPARTMENT"

* "Dismissed/Withdrawn" = "COMPLAINT DISMISSED BY COURT", "DISMISSED WITHOUT PROSECUTION","DISMISSED WITHOUT PROSECUTION - PA", "NO CASE FILED BY DA NO JD ACTION", "NO INTAKE, NO PROBABLE CAUSE - DECLINED BY PROSECUTOR", "NO INTAKE, NO PROBABLE CAUSE - PROBATION DEPARTMENT", "NO INTAKE, PROBABLE CAUSE - PROSECUTOR", "NONSUIT", "NONSUIT (PA)","NO INTAKE, DISPOSED BY INTAKE"
                            
* "Other" = "CONSOLIDATED IN ANOTHER CASE/REFERRAL", "CONSOLIDATED BY DEPARTMENT", "FILED AS A MOTION TO MODIFY","FILED AS MOTION TO MODIFY", "MOD/VOP Disposed by Intake (PA)","TAKEN INTO CONSIDERATION","SUPERVISORY CAUTION BY DEPARTMENT", "TAKEN INTO CONSIDERATION (PA Complaint)", "TRANSFER OF DISPOSITION BY COURT"
                            
* "Placement" = "CONSOLIDATED MULTIPLE CHARGES - ONE DISPOSITION (PLACEMENT)", "MODIFICATION PLACEMENT","MODIFIED TO PLACEMENT-DETERMINATE SENTENCE PROB", "PROBATION/PLACEMENT"
                            
* "Commitment" = "PROB REVOKED-DETERMINATE COMMITMENT","PROB REVOKED-INDETERMINATE COMMITMENT","TJJD DETERMINATE COMMITMENT","TJJD INDETERMINATE COMMITMENT"  
                            
* "Probation Extension" = "PROBATION EXTENDED" 

* "Probation Modified" = "PROBATION MODIFIED"  

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### data path
sp_data_path <- csg_get_project_path("jj-av-dallas")

### viz output path
# sp_viz_output_path <- paste(sp_data_path, "/Output/r_output_presentation")

```

```{r include=FALSE,message=FALSE,warning=FALSE}
###############################
### import dallas analytic file
###############################

### set sharepoint path using sp_data_path and file.path function 
sharepoint_jj_av_dallas_analytic_data <- file.path(sp_data_path,"Data/analysis")

df_dallas_county_av_supervision_analytic_file <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "df_dallas_county_av_supervision_analytic_file.txt"),
                      delim = "|") %>% 
  mutate(offense_referral_risk_level = 
           case_when(
             offense_referral_risk_level=="Low Risk" ~ 1,
             offense_referral_risk_level%in%c("Medium-Low Risk",
                             "Medium-High Risk",
                             "Moderate Risk") ~ 2,
             offense_referral_risk_level=="High Risk" ~ 3,             
             offense_referral_risk_level=="Unknown" ~ 4,
             offense_referral_risk_level=="Not Administered" ~ 5,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_risk_level = factor(offense_referral_risk_level,
         levels = c(1,2,3,4,5),
         labels =  c("Low Risk", 
                     "Moderate Risk", 
                     "High Risk",
                     "Unknown",
                     "Not Administered")),
         offense_referral_needs_level = 
           case_when(
             offense_referral_needs_level=="Low Needs" ~ 1,
             offense_referral_needs_level=="Moderate Needs" ~ 2,
             offense_referral_needs_level=="High Needs" ~ 3,             
             offense_referral_needs_level=="Unknown" ~ 4,
             offense_referral_needs_level=="Not Administered" ~ 5,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_needs_level = factor(offense_referral_needs_level,
         levels = c(1,2,3,4,5),
         labels = c("Low Needs", 
                    "Moderate Needs", 
                    "High Needs",
                    "Unknown",
                    "Not Administered"))) |> 
  ### de-dup by unique_supervision_id for mean calculations
  distinct(unique_supervision_id,
           .keep_all = TRUE)

```

```{r include=FALSE,message=FALSE,warning=FALSE}
### import violations file so that denominator is all violations (grouped)
### and not just all referrals with a violation

### read in violations file
df_technical_violations_dispo_clean_demo <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "df_violations_clean_demo.txt"),
                      delim = "|") |> 
  filter(violation_severity_factor == "Technical Violation") |> 
  mutate(youth_violation_id = paste0(unique_id,
                                    violation_referral_number),
         violation_filed_date_fy = csgjcr::csg_fiscal_year(violation_filed_date,
                                                          fy_start="October")) |> 
  mutate(violation_type_cleaned = 
           case_when(
             violation=="100a  Violation Probation - General" ~ "General Violation",
             violation%in%c("5100c  Viol Prob - Discharge Unsatisfactorily From Placement (2)","5100j  Viol Prob - Violating Placement Rules (3)","5100b  Absenting Self From Court Order Placement (2,6)") ~ "Violation Related to Placement",
             violation=="5100d  Viol Prob - Runaway From Home/Placement" ~ "Runaway",
             violation=="5100e  Viol Prob - Failure to Report to Probation Officer (2)" ~ "Failure to Report to PO",
             violation=="5100i - Viol Prob - Violating School Rules" ~ "Violation of School Rules",
             violation=="5100f  Viol Prob - Curfew Violation (3)" ~ "Curfew Violation",
             violation=="5100l Viol Prob - Failure to Participate in Order Program (11)" ~ "Failure to Participate in Program",
             violation%in%c("5100h  Viol Prob - Truancy - Not attending each Class each Day (4)",
                            "5103c  Truancy 3 Days") ~ "Truancy",
             violation%in%c("5100g  Viol Prob - Failure to Notify PO Of change Of Home/School/Employment Address (5)",
                             "5100k  Viol Prob - Failure to Pay Probation Fees (9)",
                            "xxx - Converted Data") ~ "Other",
             violation=="No Violation/Modification Needed" ~ "No Violation",             
             TRUE ~ as.character(NA))) |> 
    filter(violation_type_cleaned!="No Violation") |> 
    mutate(violation_dispo_clean = 
           case_when(
             violation_disposition=="ADJUDICATED - NO DISPOSITION" ~ "No Disposition",
             violation_disposition%in%c("ADJUDICATED PLACED ON PROBATION",
                            "CONSOLIDATED MULTIPLE CHARGES - ONE DISPOSITION (PROBATION)") ~ "Probation",
             violation_disposition%in%c("DISMISSED OR WITHDRAWN BY DEPARTMENT") ~ "30 Day Residential Program",
             violation_disposition%in%c("COMPLAINT DISMISSED BY COURT",
                            "DISMISSED WITHOUT PROSECUTION",
                            "DISMISSED WITHOUT PROSECUTION - PA",
                            "NO CASE FILED BY DA NO JD ACTION",
                            "NO INTAKE, NO PROBABLE CAUSE - DECLINED BY PROSECUTOR",
                            "NO INTAKE, NO PROBABLE CAUSE - PROBATION DEPARTMENT",
                            "NO INTAKE, PROBABLE CAUSE - PROSECUTOR",
                            "NONSUIT",
                            "NONSUIT (PA)",
                            "NO INTAKE, DISPOSED BY INTAKE") ~ "Dismissed/Withdrawn",
             violation_disposition%in%c("CONSOLIDATED IN ANOTHER CASE/REFERRAL",
                            "CONSOLIDATED BY DEPARTMENT",
                            "FILED AS A MOTION TO MODIFY",
                            "FILED AS MOTION TO MODIFY",
                            "MOD/VOP Disposed by Intake (PA)",
                            "TAKEN INTO CONSIDERATION",
                            "SUPERVISORY CAUTION BY DEPARTMENT",
                            "TAKEN INTO CONSIDERATION (PA Complaint)",
                            "TRANSFER OF DISPOSITION BY COURT") ~ "Other",
             violation_disposition%in%c("CONSOLIDATED MULTIPLE CHARGES - ONE DISPOSITION (PLACEMENT)",
                            "MODIFICATION PLACEMENT",
                            "MODIFIED TO PLACEMENT-DETERMINATE SENTENCE PROB",
                            "PROBATION/PLACEMENT") ~ "Placement",
             violation_disposition%in%c("PROB REVOKED-DETERMINATE COMMITMENT",
                            "PROB REVOKED-INDETERMINATE COMMITMENT",
                            "TJJD DETERMINATE COMMITMENT",
                            "TJJD INDETERMINATE COMMITMENT") ~ "Commitment",  
             violation_disposition%in%c("PROBATION EXTENDED") ~ "Probation Extension",  
             violation_disposition%in%c("PROBATION MODIFIED") ~ "Probation Modified",   
             TRUE ~ as.character(NA))) 

```


# 1. Technical Violation Disposition Outcomes

<br>

## Table 1. By FY: Technical Violation Disposition Outcomes

**NOTE:** The base sample and denominator for this analysis is all filed violations where the most serious violation was a technical violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_dispo_clean_demo %>% 
  filter(violation_filed_date_fy>=2016) %>% 
  dplyr::group_by(violation_filed_date_fy) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                    `30 Day Residential Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="30 Day Residential Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Violation` = violation_filed_date_fy) %>% 
  mutate(`FY of Violation` = as.character(`FY of Violation`))

### overall
df_technical_violations_overall <- df_technical_violations_dispo_clean_demo %>% 
  filter(violation_filed_date_fy>=2016) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                    `30 Day Residential Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="30 Day Residential Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`FY of Violation` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(9, bold = TRUE)
```


<br>

## Table 2. By Race/Ethnicity: Technical Violation Disposition Outcomes

**NOTE:** The base sample and denominator for this analysis is all filed violations where the most serious violation was a technical violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                    `30 Day Residential Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="30 Day Residential Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean)

### overall
df_technical_violations_overall <- df_technical_violations_dispo_clean_demo %>% 
   dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                    `30 Day Residential Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="30 Day Residential Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 3. By Gender: Technical Violation Disposition Outcomes

**NOTE:** The base sample and denominator for this analysis is all filed violations where the most serious violation was a technical violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::group_by(gender_clean) %>% 
   dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                    `30 Day Residential Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="30 Day Residential Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>%  
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean)

### overall
df_technical_violations_overall <- df_technical_violations_dispo_clean_demo %>% 
   dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                    `30 Day Residential Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="30 Day Residential Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Gender` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br>

## Table 4. By Age: Technical Violation Disposition Outcomes

**TO DO:** Fix age variable -- by linking pertinent referral to each violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### turn age into a factor
df_technical_violations_dispo_clean_demo %<>%
 mutate(age_at_start_of_supervision_clean = factor(age_at_start_of_supervision_clean,
         levels = c("Less than 12", 
                    "12 to 13",
                    "14 to 15",
                    "16 to 20")))

### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::group_by(age_at_start_of_supervision_clean) %>% 
   dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                    `30 Day Residential Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="30 Day Residential Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age` = age_at_start_of_supervision_clean)

### overall
df_technical_violations_overall <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                    `30 Day Residential Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="30 Day Residential Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Age` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br>

## Table 5. By Risk Level: Technical Violation Disposition Outcomes

**Note:** This is the "listed risk level at the time of referral disposition"

**TO DO:** Double check risk level -- by linking pertinent referral to each violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                    `30 Day Residential Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="30 Day Residential Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level)

### overall
df_technical_violations_overall <- df_technical_violations_dispo_clean_demo %>% 
   dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                    `30 Day Residential Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="30 Day Residential Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 6. By Needs Level: Technical Violation Disposition Outcomes

**Note:** This is the "listed needs level at the time of referral disposition"

**TO DO:** Double check needs level -- by linking pertinent referral to each violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
   dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                    `30 Day Residential Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="30 Day Residential Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level)

### overall
df_technical_violations_overall <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                    `30 Day Residential Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="30 Day Residential Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

# 2. Average Length of Supervision Extension

What is the average length of time a supervision episode is extended as the result of a technical violation? How does this vary across race/ethnicity, sex, and risk level? 

**Note:** This analysis only uses the supervision extension -- so we are unable to speak to the exact reason (technical violation, new offense, etc.) for a given extension. We are following up with Dallas on this approach (and how much we can assume extensions and modifications are tied to violations).

**Business Rule:** We are only looking at violations filed in fiscal years 2016-2020 (to align with our sample window on the front end and ensure there is sufficient time at the end of sample for extension to actually occur).

**Looks like we have duplicates based on the demo merge (multiple age groups, multiple risk/needs scores)...is this true for other joins, as well?**

**TO DO: CLEAN UP DEMO JOIN + DECIDE WHICH VALUES TO KEEP (PERHAPS BY CLOSEST DATE AND/OR NON-MISSINGNESS?)**

```{r include=FALSE,message=FALSE,warning=FALSE}
### read in supervision extensions file that we want to merge to violations file for this section
### i created this file specifically for this purpose in the analytic file prep file
supervision_extension_demo_analysis_clean <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "supervision_extension_demo_analysis_clean.txt"),
                      delim = "|") |> 
  distinct() |> 
  mutate(supervision_extension_begin_fy = csgjcr::csg_fiscal_year(supervision_extension_begin_date,
                                                          fy_start="October")) |> 
  filter(supervision_extension_begin_fy>=2016,
         supervision_extension_begin_fy<=2020)

# ### join two files to explore supervision extensions that occur within 
# ### we can only join on youth ID
# ### referral IDs in these two files refer to different referrals (one a violation referral and one the original referral)
# df_technical_violations_supervision_extension <- left_join(df_technical_violations_dispo_clean_demo,
#                                                        supervision_extension_for_join_to_violations_clean,
#                                                        by = c("unique_id")) |> 
#   mutate(youth_violation_id = paste0(unique_id,
#                                      violation_referral_number)) |> 
#   ### now calculate time from violation disposition date to supervision extension start date
#   ### with preliminary business rules: if extension occurs within 15 days of violation disposition date
#   ### we are considering the two to be linked and thus, I am keeping those records in this file
#   ### all other records will be dropped -- we only want to calculate length of extension for those
#   ### records that fit this criteria
#   mutate(violation_disposition_date = ymd(as_date(violation_disposition_date)),
#          supervision_extension_begin_date = ymd(as_date(supervision_extension_begin_date))) |> 
#   mutate(time_from_dispo_to_extension_start = as.numeric(difftime(supervision_extension_begin_date,
#                                                             violation_disposition_date,
#                                                                     units="days"))) |> 
#   filter(time_from_dispo_to_extension_start>-5,
#          time_from_dispo_to_extension_start<=15) |>
#   ### remove pure duplicates
#   distinct() 

```


## Table 7. By FY: Average Length of Supervision Extension

**NOTE:** The base sample and denominator for this analysis is all supervision extensions (one supervision episode could have more than one extension) regardless of associated violation type. FY represents fiscal year of supervision extension.


```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean, median, min, and max of supervision_extension_in_days
df_technical_violations_per_year <- supervision_extension_demo_analysis_clean %>% 
  dplyr::group_by(supervision_extension_begin_fy) %>% 
   dplyr::summarise(`All Supervision Episodes w/ at Least One Supervision Extension (N)` = n_distinct(unique_supervision_id),
                   `Median` = median(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Mean` = mean(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Min` = min(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Max` = max(supervision_extension_in_days,
                                     na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Extension` = supervision_extension_begin_fy) %>% 
  mutate(`FY of Extension` = as.character(`FY of Extension`))

### overall
df_technical_violations_overall <- supervision_extension_demo_analysis_clean %>% 
   dplyr::summarise(`All Supervision Episodes w/ at Least One Supervision Extension (N)` = n_distinct(unique_supervision_id),
                   `Median` = median(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Mean` = mean(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Min` = min(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Max` = max(supervision_extension_in_days,
                                     na.rm = TRUE)) %>% 
  mutate(`FY of Extension` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 8. By Race/Ethnicity: Average Length of Supervision Extension

**NOTE:** The base sample and denominator for this analysis is all supervision extensions (one supervision episode could have more than one extension) regardless of associated violation type. FY represents fiscal year of supervision extension.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean, median, min, and max of supervision_extension_in_days
df_technical_violations_per_year <- supervision_extension_demo_analysis_clean %>% 
  dplyr::group_by(race_clean) %>% 
   dplyr::summarise(`All Supervision Episodes w/ at Least One Supervision Extension (N)` = n_distinct(unique_supervision_id),
                   `Median` = median(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Mean` = mean(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Min` = min(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Max` = max(supervision_extension_in_days,
                                     na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### overall
df_technical_violations_overall <- supervision_extension_demo_analysis_clean %>% 
   dplyr::summarise(`All Supervision Episodes w/ at Least One Supervision Extension (N)` = n_distinct(unique_supervision_id),
                   `Median` = median(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Mean` = mean(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Min` = min(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Max` = max(supervision_extension_in_days,
                                     na.rm = TRUE)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(4, bold = TRUE)

```

<br>

## Table 9. By Gender: Average Length of Supervision Extension

**NOTE:** The base sample and denominator for this analysis is all supervision extensions (one supervision episode could have more than one extension) regardless of associated violation type. FY represents fiscal year of supervision extension.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean, median, min, and max of supervision_extension_in_days
df_technical_violations_per_year <- supervision_extension_demo_analysis_clean %>% 
  dplyr::group_by(gender_clean) %>% 
   dplyr::summarise(`All Supervision Episodes w/ at Least One Supervision Extension (N)` = n_distinct(unique_supervision_id),
                   `Median` = median(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Mean` = mean(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Min` = min(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Max` = max(supervision_extension_in_days,
                                     na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean) 

### overall
df_technical_violations_overall <- supervision_extension_demo_analysis_clean %>% 
   dplyr::summarise(`All Supervision Episodes w/ at Least One Supervision Extension (N)` = n_distinct(unique_supervision_id),
                   `Median` = median(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Mean` = mean(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Min` = min(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Max` = max(supervision_extension_in_days,
                                     na.rm = TRUE)) %>% 
  mutate(`Gender` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(2, bold = TRUE)

```

<br>

## Table 10. By Age: Average Length of Supervision Extension

**NOTE:** The base sample and denominator for this analysis is all supervision extensions (one supervision episode could have more than one extension) regardless of associated violation type. FY represents fiscal year of supervision extension.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### turn age into a factor
supervision_extension_demo_analysis_clean %<>%
 mutate(age_at_start_of_supervision_clean = factor(age_at_start_of_supervision_clean,
         levels = c("Less than 12", 
                    "12 to 13",
                    "14 to 15",
                    "16 to 20")))

### mean, median, min, and max of supervision_extension_in_days
df_technical_violations_per_year <- supervision_extension_demo_analysis_clean %>% 
  dplyr::group_by(age_at_start_of_supervision_clean) %>% 
   dplyr::summarise(`All Supervision Episodes w/ at Least One Supervision Extension (N)` = n_distinct(unique_supervision_id),
                   `Median` = median(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Mean` = mean(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Min` = min(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Max` = max(supervision_extension_in_days,
                                     na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age` = age_at_start_of_supervision_clean) 

### overall
df_technical_violations_overall <- supervision_extension_demo_analysis_clean %>% 
   dplyr::summarise(`All Supervision Episodes w/ at Least One Supervision Extension (N)` = n_distinct(unique_supervision_id),
                   `Median` = median(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Mean` = mean(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Min` = min(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Max` = max(supervision_extension_in_days,
                                     na.rm = TRUE)) %>% 
  mutate(`Age` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br>

## Table 11. By Risk Level: Average Length of Supervision Extension

**NOTE:** The base sample and denominator for this analysis is all supervision extensions (one supervision episode could have more than one extension) regardless of associated violation type. FY represents fiscal year of supervision extension.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean, median, min, and max of supervision_extension_in_days
df_technical_violations_per_year <- supervision_extension_demo_analysis_clean %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
   dplyr::summarise(`All Supervision Episodes w/ at Least One Supervision Extension (N)` = n_distinct(unique_supervision_id),
                   `Median` = median(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Mean` = mean(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Min` = min(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Max` = max(supervision_extension_in_days,
                                     na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level) 

### overall
df_technical_violations_overall <- supervision_extension_demo_analysis_clean %>% 
   dplyr::summarise(`All Supervision Episodes w/ at Least One Supervision Extension (N)` = n_distinct(unique_supervision_id),
                   `Median` = median(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Mean` = mean(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Min` = min(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Max` = max(supervision_extension_in_days,
                                     na.rm = TRUE)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 12. By Needs Level: Average Length of Supervision Extension

**NOTE:** The base sample and denominator for this analysis is all supervision extensions (one supervision episode could have more than one extension) regardless of associated violation type. FY represents fiscal year of supervision extension.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean, median, min, and max of supervision_extension_in_days
df_technical_violations_per_year <- supervision_extension_demo_analysis_clean %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
   dplyr::summarise(`All Supervision Episodes w/ at Least One Supervision Extension (N)` = n_distinct(unique_supervision_id),
                   `Median` = median(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Mean` = mean(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Min` = min(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Max` = max(supervision_extension_in_days,
                                     na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level) 

### overall
df_technical_violations_overall <- supervision_extension_demo_analysis_clean %>% 
   dplyr::summarise(`All Supervision Episodes w/ at Least One Supervision Extension (N)` = n_distinct(unique_supervision_id),
                   `Median` = median(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Mean` = mean(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Min` = min(supervision_extension_in_days,
                                     na.rm = TRUE),
                   `Max` = max(supervision_extension_in_days,
                                     na.rm = TRUE)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

# 3. Use of 30-day Residential Program 

In Dallas, probation can file a violation to get a kid into a 30 day residential program. The violation does not go to the prosecutor. If the kid is successful in the placement, then the department dismisses the violation. How often does this happen? 

**Business Rule:** I am exploring violations with dispositions of "DISMISSED OR WITHDRAWN BY DEPARTMENT" -- which indicates a sanction to the 30 day residential program (where if a kid is successful, the violation is dismissed). We should (1) confirm this interpretation with Dallas and (2) ask whether this disposition is only for youth who are successful in the program and if so, if there is a way to flag youth who are not successful. In addition, we are only looking at violations filed in fiscal years 2016 and on.

## Table 13. By FY: Percentage of Technical Violations Disposed to Residential Program

```{r echo=FALSE,message=FALSE,warning=FALSE}
### import violations file so that denominator is all violations (grouped)
### and not just all referrals with a violation

### read in violations file
df_violations_clean_demo <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "df_violations_clean_demo.txt"),
                      delim = "|") |> 
  mutate(youth_violation_id = paste0(unique_id,
                                    violation_referral_number),
         violation_filed_date_fy = csgjcr::csg_fiscal_year(violation_filed_date,
                                                          fy_start="October"),
         violation_dismissed_withdrawn_flag = ifelse(violation_disposition=="DISMISSED OR WITHDRAWN BY DEPARTMENT",
                                                     1,0))   |> 
  filter(violation_severity_factor == "Technical Violation",
         violation_filed_date_fy>=2016) |> 
  mutate(violation_type_cleaned = 
           case_when(
             violation=="100a  Violation Probation - General" ~ "General Violation",
             violation%in%c("5100c  Viol Prob - Discharge Unsatisfactorily From Placement (2)","5100j  Viol Prob - Violating Placement Rules (3)","5100b  Absenting Self From Court Order Placement (2,6)") ~ "Violation Related to Placement",
             violation=="5100d  Viol Prob - Runaway From Home/Placement" ~ "Runaway",
             violation=="5100e  Viol Prob - Failure to Report to Probation Officer (2)" ~ "Failure to Report to PO",
             violation=="5100i - Viol Prob - Violating School Rules" ~ "Violation of School Rules",
             violation=="5100f  Viol Prob - Curfew Violation (3)" ~ "Curfew Violation",
             violation=="5100l Viol Prob - Failure to Participate in Order Program (11)" ~ "Failure to Participate in Program",
             violation%in%c("5100h  Viol Prob - Truancy - Not attending each Class each Day (4)",
                            "5103c  Truancy 3 Days") ~ "Truancy",
             violation%in%c("5100g  Viol Prob - Failure to Notify PO Of change Of Home/School/Employment Address (5)",
                             "5100k  Viol Prob - Failure to Pay Probation Fees (9)",
                            "xxx - Converted Data") ~ "Other",
             violation=="No Violation/Modification Needed" ~ "No Violation",             
             TRUE ~ as.character(NA))) 

### create denominator -- unique referrals for entire sample
unique_violations_sample_denom <- n_distinct(df_violations_clean_demo$youth_violation_id)

### unique youth and referrals per FY
df_dismissed_violations_per_year <- df_violations_clean_demo %>% 
  dplyr::group_by(violation_filed_date_fy) %>% 
  dplyr::summarise(`Unique Youth w/ at least One Violation Disposed to 30 Day Program (N)` = n_distinct(unique_id[violation_dismissed_withdrawn_flag==1]),
            `All Technical Violations (N)` = n_distinct(youth_violation_id),
              `Technical Violations Disposed to 30 Day Program (N)` = n_distinct(youth_violation_id[violation_dismissed_withdrawn_flag==1]),
            `Technical Violations Disposed to 30 Day Program (%)` = scales::percent(`Technical Violations Disposed to 30 Day Program (N)`/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Filing` = violation_filed_date_fy) %>% 
  mutate(`FY of Filing` = as.character(`FY of Filing`)) 

### overall
df_violations_overall <- df_violations_clean_demo %>% 
  dplyr::summarise(`Unique Youth w/ at least One Violation Disposed to 30 Day Program (N)` = n_distinct(unique_id[violation_dismissed_withdrawn_flag==1]),
            `All Technical Violations (N)` = n_distinct(youth_violation_id),
              `Technical Violations Disposed to 30 Day Program (N)` = n_distinct(youth_violation_id[violation_dismissed_withdrawn_flag==1]),
            `Technical Violations Disposed to 30 Day Program (%)` = scales::percent(`Technical Violations Disposed to 30 Day Program (N)`/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`FY of Filing` = "Overall")

### combine tables for kable
df_dismissed_violations_per_year_table <- rbind(df_dismissed_violations_per_year,df_violations_overall)

### print table via kableextra
kable(df_dismissed_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(9, bold = TRUE)
```

<br>

## Table 14. By Race/Ethnicity: Percentage of Technical Violations Disposed to Residential Program

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and referrals per FY
df_dismissed_violations_per_year <- df_violations_clean_demo |> 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Unique Youth w/ at least One Violation Disposed to 30 Day Program (N)` = n_distinct(unique_id[violation_dismissed_withdrawn_flag==1]),
            `All Technical Violations (N)` = n_distinct(youth_violation_id),
              `Technical Violations Disposed to 30 Day Program (N)` = n_distinct(youth_violation_id[violation_dismissed_withdrawn_flag==1]),
            `Technical Violations Disposed to 30 Day Program (%)` = scales::percent(`Technical Violations Disposed to 30 Day Program (N)`/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### overall
df_violations_overall <- df_violations_clean_demo %>% 
  dplyr::summarise(`Unique Youth w/ at least One Violation Disposed to 30 Day Program (N)` = n_distinct(unique_id[violation_dismissed_withdrawn_flag==1]),
            `All Technical Violations (N)` = n_distinct(youth_violation_id),
              `Technical Violations Disposed to 30 Day Program (N)` = n_distinct(youth_violation_id[violation_dismissed_withdrawn_flag==1]),
            `Technical Violations Disposed to 30 Day Program (%)` = scales::percent(`Technical Violations Disposed to 30 Day Program (N)`/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_dismissed_violations_per_year_table <- rbind(df_dismissed_violations_per_year,df_violations_overall)

### print table via kableextra
kable(df_dismissed_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 15. By Gender: Percentage of Technical Violations Disposed to Residential Program

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and referrals per FY
df_dismissed_violations_per_year <- df_violations_clean_demo |> 
  dplyr::group_by(gender_clean) %>% 
  dplyr::summarise(`Unique Youth w/ at least One Violation Disposed to 30 Day Program (N)` = n_distinct(unique_id[violation_dismissed_withdrawn_flag==1]),
            `All Technical Violations (N)` = n_distinct(youth_violation_id),
              `Technical Violations Disposed to 30 Day Program (N)` = n_distinct(youth_violation_id[violation_dismissed_withdrawn_flag==1]),
            `Technical Violations Disposed to 30 Day Program (%)` = scales::percent(`Technical Violations Disposed to 30 Day Program (N)`/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean) 

### overall
df_violations_overall <- df_violations_clean_demo %>% 
  dplyr::summarise(`Unique Youth w/ at least One Violation Disposed to 30 Day Program (N)` = n_distinct(unique_id[violation_dismissed_withdrawn_flag==1]),
            `All Technical Violations (N)` = n_distinct(youth_violation_id),
              `Technical Violations Disposed to 30 Day Program (N)` = n_distinct(youth_violation_id[violation_dismissed_withdrawn_flag==1]),
            `Technical Violations Disposed to 30 Day Program (%)` = scales::percent(`Technical Violations Disposed to 30 Day Program (N)`/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Gender` = "Overall")

### combine tables for kable
df_dismissed_violations_per_year_table <- rbind(df_dismissed_violations_per_year,df_violations_overall)

### print table via kableextra
kable(df_dismissed_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(2, bold = TRUE)
```

<br>

## Table 16. By Age: Percentage of Technical Violations Disposed to Residential Program

```{r echo=FALSE,message=FALSE,warning=FALSE}
### turn age into a factor
df_violations_clean_demo %<>%
 mutate(age_at_start_of_supervision_clean = factor(age_at_start_of_supervision_clean,
         levels = c("Less than 12", 
                    "12 to 13",
                    "14 to 15",
                    "16 to 20")))

### unique youth and referrals per FY
df_dismissed_violations_per_year <- df_violations_clean_demo |> 
  dplyr::group_by(age_at_start_of_supervision_clean) %>% 
  dplyr::summarise(`Unique Youth w/ at least One Violation Disposed to 30 Day Program (N)` = n_distinct(unique_id[violation_dismissed_withdrawn_flag==1]),
            `All Technical Violations (N)` = n_distinct(youth_violation_id),
              `Technical Violations Disposed to 30 Day Program (N)` = n_distinct(youth_violation_id[violation_dismissed_withdrawn_flag==1]),
            `Technical Violations Disposed to 30 Day Program (%)` = scales::percent(`Technical Violations Disposed to 30 Day Program (N)`/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age` = age_at_start_of_supervision_clean) 

### overall
df_violations_overall <- df_violations_clean_demo %>% 
  dplyr::summarise(`Unique Youth w/ at least One Violation Disposed to 30 Day Program (N)` = n_distinct(unique_id[violation_dismissed_withdrawn_flag==1]),
            `All Technical Violations (N)` = n_distinct(youth_violation_id),
              `Technical Violations Disposed to 30 Day Program (N)` = n_distinct(youth_violation_id[violation_dismissed_withdrawn_flag==1]),
            `Technical Violations Disposed to 30 Day Program (%)` = scales::percent(`Technical Violations Disposed to 30 Day Program (N)`/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Age` = "Overall")

### combine tables for kable
df_dismissed_violations_per_year_table <- rbind(df_dismissed_violations_per_year,df_violations_overall)

### print table via kableextra
kable(df_dismissed_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br>

## Table 17. By Risk Level: Percentage of Technical Violations Disposed to Residential Program

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and referrals per FY
df_dismissed_violations_per_year <- df_violations_clean_demo |> 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`Unique Youth w/ at least One Violation Disposed to 30 Day Program (N)` = n_distinct(unique_id[violation_dismissed_withdrawn_flag==1]),
            `All Technical Violations (N)` = n_distinct(youth_violation_id),
              `Technical Violations Disposed to 30 Day Program (N)` = n_distinct(youth_violation_id[violation_dismissed_withdrawn_flag==1]),
            `Technical Violations Disposed to 30 Day Program (%)` = scales::percent(`Technical Violations Disposed to 30 Day Program (N)`/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level) 

### overall
df_violations_overall <- df_violations_clean_demo %>% 
  dplyr::summarise(`Unique Youth w/ at least One Violation Disposed to 30 Day Program (N)` = n_distinct(unique_id[violation_dismissed_withdrawn_flag==1]),
            `All Technical Violations (N)` = n_distinct(youth_violation_id),
              `Technical Violations Disposed to 30 Day Program (N)` = n_distinct(youth_violation_id[violation_dismissed_withdrawn_flag==1]),
            `Technical Violations Disposed to 30 Day Program (%)` = scales::percent(`Technical Violations Disposed to 30 Day Program (N)`/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_dismissed_violations_per_year_table <- rbind(df_dismissed_violations_per_year,df_violations_overall)

### print table via kableextra
kable(df_dismissed_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 18. By Risk Level: Percentage of Technical Violations Disposed to Residential Program

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and referrals per FY
df_dismissed_violations_per_year <- df_violations_clean_demo |> 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`Unique Youth w/ at least One Violation Disposed to 30 Day Program (N)` = n_distinct(unique_id[violation_dismissed_withdrawn_flag==1]),
            `All Technical Violations (N)` = n_distinct(youth_violation_id),
              `Technical Violations Disposed to 30 Day Program (N)` = n_distinct(youth_violation_id[violation_dismissed_withdrawn_flag==1]),
            `Technical Violations Disposed to 30 Day Program (%)` = scales::percent(`Technical Violations Disposed to 30 Day Program (N)`/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level) 

### overall
df_violations_overall <- df_violations_clean_demo %>% 
  dplyr::summarise(`Unique Youth w/ at least One Violation Disposed to 30 Day Program (N)` = n_distinct(unique_id[violation_dismissed_withdrawn_flag==1]),
            `All Technical Violations (N)` = n_distinct(youth_violation_id),
              `Technical Violations Disposed to 30 Day Program (N)` = n_distinct(youth_violation_id[violation_dismissed_withdrawn_flag==1]),
            `Technical Violations Disposed to 30 Day Program (%)` = scales::percent(`Technical Violations Disposed to 30 Day Program (N)`/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_dismissed_violations_per_year_table <- rbind(df_dismissed_violations_per_year,df_violations_overall)

### print table via kableextra
kable(df_dismissed_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 19. By Violation Type: Percentage of Technical Violations Disposed to Residential Program

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and referrals per FY
df_dismissed_violations_per_year <- df_violations_clean_demo |> 
  dplyr::group_by(violation_type_cleaned) %>% 
  dplyr::summarise(`Unique Youth w/ at least One Violation Disposed to 30 Day Program (N)` = n_distinct(unique_id[violation_dismissed_withdrawn_flag==1]),
            `All Technical Violations (N)` = n_distinct(youth_violation_id),
              `Technical Violations Disposed to 30 Day Program (N)` = n_distinct(youth_violation_id[violation_dismissed_withdrawn_flag==1]),
            `Technical Violations Disposed to 30 Day Program (%)` = scales::percent(`Technical Violations Disposed to 30 Day Program (N)`/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Violation Type` = violation_type_cleaned) 

### overall
df_violations_overall <- df_violations_clean_demo %>% 
  dplyr::summarise(`Unique Youth w/ at least One Violation Disposed to 30 Day Program (N)` = n_distinct(unique_id[violation_dismissed_withdrawn_flag==1]),
            `All Technical Violations (N)` = n_distinct(youth_violation_id),
              `Technical Violations Disposed to 30 Day Program (N)` = n_distinct(youth_violation_id[violation_dismissed_withdrawn_flag==1]),
            `Technical Violations Disposed to 30 Day Program (%)` = scales::percent(`Technical Violations Disposed to 30 Day Program (N)`/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Violation Type` = "Overall")

### combine tables for kable
df_dismissed_violations_per_year_table <- rbind(df_dismissed_violations_per_year,df_violations_overall)

### print table via kableextra
kable(df_dismissed_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(10, bold = TRUE)
```


<br><br>
