---
title: "When and how often do youth receive technical violations?"
format: html
---

**When and how often do youth receive technical violations?**  

* What is the average time to a first technical violation on a supervision episode? How does this vary across race/ethnicity, sex, and risk level? 

* What is the average number of technical violations that occur during a probation episode? How does this vary across race/ethnicity, sex, and risk level?  

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### data path
sp_data_path <- csg_get_project_path("jj-av-dallas")

### viz output path
# sp_viz_output_path <- paste(sp_data_path, "/Output/r_output_presentation")

```

```{r include=FALSE,message=FALSE,warning=FALSE}
###############################
### import dallas analytic file
###############################

### set sharepoint path using sp_data_path and file.path function 
sharepoint_jj_av_dallas_analytic_data <- file.path(sp_data_path,"Data/analysis")

df_dallas_county_av_supervision_analytic_file <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "df_dallas_county_av_supervision_analytic_file.txt"),
                      delim = "|") %>% 
  mutate(offense_referral_risk_level = 
           case_when(
             offense_referral_risk_level=="Low Risk" ~ 1,
             offense_referral_risk_level%in%c("Medium-Low Risk",
                             "Medium-High Risk",
                             "Moderate Risk") ~ 2,
             offense_referral_risk_level=="High Risk" ~ 3,             
             offense_referral_risk_level=="Unknown" ~ 4,
             offense_referral_risk_level=="Not Administered" ~ 5,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_risk_level = factor(offense_referral_risk_level,
         levels = c(1,2,3,4,5),
         labels =  c("Low Risk", 
                     "Moderate Risk", 
                     "High Risk",
                     "Unknown",
                     "Not Administered")),
         offense_referral_needs_level = 
           case_when(
             offense_referral_needs_level=="Low Needs" ~ 1,
             offense_referral_needs_level=="Moderate Needs" ~ 2,
             offense_referral_needs_level=="High Needs" ~ 3,             
             offense_referral_needs_level=="Unknown" ~ 4,
             offense_referral_needs_level=="Not Administered" ~ 5,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_needs_level = factor(offense_referral_needs_level,
         levels = c(1,2,3,4,5),
         labels = c("Low Needs", 
                    "Moderate Needs", 
                    "High Needs",
                    "Unknown",
                    "Not Administered"))) |> 
  ### de-dup by unique_supervision_id for mean calculations
  distinct(unique_supervision_id,
           .keep_all = TRUE) %>% 
  ### convert inf to NA
  mutate_all(.,.funs = function(x){ifelse(is.infinite(x),NA,x)})

```

<br>

# 1. Average Time to First Technical Violation

**NOTE:** There are two possibilities for exploring time to technical violation:

* **CURRENTLY** using `supervision_start_first_tech_violation_first_overall` (from `violation_filed_date`) if we are only looking at first technical violations that were also first overall violations (QUESTION: use with `violation_technical_flag` filter?) 

* we could also instead use `supervision_start_first_tech_violation_any` (from `min_technical_violation_date`) to explore first technical violations even if following new offense violation (i.e., the first technical violation for an episode even if it occurs after a separate new offense violation)

<br>

## Table 1. By FY: Time to First Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
### average time to first technical violation
df_time_to_technical_fy <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(supervision_end_fy) %>% 
  dplyr::summarise(`Average Time to First Technical Violation (Mean)` = mean(supervision_start_first_tech_violation_first_overall,
                                                                          na.rm = TRUE),
                   `Average Time to First Technical Violation (Median)` = median(supervision_start_first_tech_violation_first_overall,
                                                                          na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Completion` = supervision_end_fy) %>% 
  mutate(`FY of Completion` = as.character(`FY of Completion`))

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Average Time to First Technical Violation (Mean)` = mean(supervision_start_first_tech_violation_first_overall,
                                                                          na.rm = TRUE),
                   `Average Time to First Technical Violation (Median)` = median(supervision_start_first_tech_violation_first_overall,
                                                                          na.rm = TRUE)) %>% 
  mutate(`FY of Completion` = "Overall")

### combine tables for kable
df_time_to_technical_fy_table <- rbind(df_time_to_technical_fy,df_technical_violations_overall)

### print table via kableextra
kable(df_time_to_technical_fy_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7, bold = TRUE)
```

<br>

## Table 2. By Race/Ethnicity: Time to First Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
### average time to first technical violation
df_time_to_technical_fy <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Average Time to First Technical Violation (Mean)` = mean(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE),
                   `Average Time to First Technical Violation (Median)` = median(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Average Time to First Technical Violation (Mean)` = mean(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE),
                   `Average Time to First Technical Violation (Median)` = median(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_time_to_technical_fy_table <- rbind(df_time_to_technical_fy,df_technical_violations_overall)

### print table via kableextra
kable(df_time_to_technical_fy_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 3. By Gender: Time to First Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
### average time to first technical violation
df_time_to_technical_fy <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(gender_clean) %>% 
  dplyr::summarise(`Average Time to First Technical Violation (Mean)` = mean(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE),
                   `Average Time to First Technical Violation (Median)` = median(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean) 

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Average Time to First Technical Violation (Mean)` = mean(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE),
                   `Average Time to First Technical Violation (Median)` = median(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE)) %>% 
  mutate(`Gender` = "Overall")

### combine tables for kable
df_time_to_technical_fy_table <- rbind(df_time_to_technical_fy,df_technical_violations_overall)

### print table via kableextra
kable(df_time_to_technical_fy_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br>

## Table 4. By Age: Time to First Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
### turn age into a factor
df_dallas_county_av_supervision_analytic_file %<>%
 mutate(age_at_referral_clean = factor(age_at_referral_clean,
         levels = c("Less than 12", 
                    "12 to 13",
                    "14 to 15",
                    "16 to 20")))

### average time to first technical violation
df_time_to_technical_fy <- df_dallas_county_av_supervision_analytic_file %>% 
  filter(!is.na(age_at_referral_clean)) |> 
  dplyr::group_by(age_at_referral_clean) %>% 
  dplyr::summarise(`Average Time to First Technical Violation (Mean)` = mean(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE),
                   `Average Time to First Technical Violation (Median)` = median(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age at Referral` = age_at_referral_clean) 

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
    filter(!is.na(age_at_referral_clean)) |> 
  dplyr::summarise(`Average Time to First Technical Violation (Mean)` = mean(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE),
                   `Average Time to First Technical Violation (Median)` = median(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE)) %>% 
  mutate(`Age at Referral` = "Overall")

### combine tables for kable
df_time_to_technical_fy_table <- rbind(df_time_to_technical_fy,df_technical_violations_overall)

### print table via kableextra
kable(df_time_to_technical_fy_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br>

## Table 5. By Risk Level: Time to First Technical Violation

**Note:** This is the "listed risk level at the time of referral disposition"

```{r echo=FALSE,message=FALSE,warning=FALSE}
### average time to first technical violation
df_time_to_technical_fy <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`Average Time to First Technical Violation (Mean)` = mean(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE),
                   `Average Time to First Technical Violation (Median)` = median(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level) 

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Average Time to First Technical Violation (Mean)` = mean(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE),
                   `Average Time to First Technical Violation (Median)` = median(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_time_to_technical_fy_table <- rbind(df_time_to_technical_fy,df_technical_violations_overall)

### print table via kableextra
kable(df_time_to_technical_fy_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 6. By Needs Level: Time to First Technical Violation

**Note:** This is the "listed needs level at the time of referral disposition"

```{r echo=FALSE,message=FALSE,warning=FALSE}
### average time to first technical violation
df_time_to_technical_fy <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`Average Time to First Technical Violation (Mean)` = mean(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE),
                   `Average Time to First Technical Violation (Median)` = median(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level) 

### overall
df_technical_violations_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Average Time to First Technical Violation (Mean)` = mean(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE),
                   `Average Time to First Technical Violation (Median)` = median(supervision_start_first_tech_violation_any,
                                                                          na.rm = TRUE)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_time_to_technical_fy_table <- rbind(df_time_to_technical_fy,df_technical_violations_overall)

### print table via kableextra
kable(df_time_to_technical_fy_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

# 2. Average Number of Technical Violations per Episode

**TO DO**

<br><br>


