---
title: "Why do youth receive technical violations?"
format: html
---

**Why do youth receive technical violations?** 

* What are the most common reasons for technical violations when the violation was the primary offense? How do reasons vary across race/ethnicity, sex, and risk level? (Technical violation N: 2,333)

* What are the most common offenses when the technical violation was not the primary offense? There are two ways to run this analysis -- types of new offenses across all violations or only types of new offenses where there is a technical violation listed. Which do we want? (New offense N: 564)



**Double check following coding/grouping of technical violations with team:**

* "General Violation" = "100a  Violation Probation - General" 

* "Violation Related to Placement" = "5100c  Viol Prob - Discharge Unsatisfactorily From Placement (2)","5100j  Viol Prob - Violating Placement Rules (3)", "5100b  Absenting Self From Court Order Placement (2,6)"

* "Runaway" = "5100d  Viol Prob - Runaway From Home/Placement" 

* "Failure to Report to PO" = "5100e  Viol Prob - Failure to Report to Probation Officer (2)" 

* "Violation of School Rules" = "5100i - Viol Prob - Violating School Rules" 

* "Curfew Violation" = "5100f  Viol Prob - Curfew Violation (3)" 

* "Failure to Participate in Program" = "5100l Viol Prob - Failure to Participate in Order Program (11)" 

* "Truancy" = "5100h  Viol Prob - Truancy - Not attending each Class each Day (4)","5103c  Truancy 3 Days"

* "Other" = "5100g  Viol Prob - Failure to Notify PO Of change Of Home/School/Employment Address (5)","5100k  Viol Prob - Failure to Pay Probation Fees (9)","xxx - Converted Data")

* "No Violation" = "No Violation/Modification Needed" (*I have filtered these out from the first section*)

<br>

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### data path
sp_data_path <- csg_get_project_path("jj-av-dallas")

### viz output path
# sp_viz_output_path <- paste(sp_data_path, "/Output/r_output_presentation")

```

```{r include=FALSE,message=FALSE,warning=FALSE}
###############################
### import dallas analytic file
###############################

### set sharepoint path using sp_data_path and file.path function 
sharepoint_jj_av_dallas_analytic_data <- file.path(sp_data_path,"Data/analysis")

df_dallas_county_av_supervision_analytic_file <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "df_dallas_county_av_supervision_analytic_file.txt"),
                      delim = "|") %>% 
  mutate(offense_referral_risk_level = 
           case_when(
             offense_referral_risk_level=="Low Risk" ~ 1,
             offense_referral_risk_level%in%c("Medium-Low Risk",
                             "Medium-High Risk",
                             "Moderate Risk") ~ 2,
             offense_referral_risk_level=="High Risk" ~ 3,             
             offense_referral_risk_level=="Unknown" ~ 4,
             offense_referral_risk_level=="Not Administered" ~ 5,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_risk_level = factor(offense_referral_risk_level,
         levels = c(1,2,3,4,5),
         labels =  c("Low Risk", 
                     "Moderate Risk", 
                     "High Risk",
                     "Unknown",
                     "Not Administered")),
         offense_referral_needs_level = 
           case_when(
             offense_referral_needs_level=="Low Needs" ~ 1,
             offense_referral_needs_level=="Moderate Needs" ~ 2,
             offense_referral_needs_level=="High Needs" ~ 3,             
             offense_referral_needs_level=="Unknown" ~ 4,
             offense_referral_needs_level=="Not Administered" ~ 5,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_needs_level = factor(offense_referral_needs_level,
         levels = c(1,2,3,4,5),
         labels = c("Low Needs", 
                    "Moderate Needs", 
                    "High Needs",
                    "Unknown",
                    "Not Administered"))) |> 
  ### de-dup by unique_supervision_id for mean calculations
  distinct(unique_supervision_id,
           .keep_all = TRUE)

```

```{r include=FALSE,message=FALSE,warning=FALSE}
### import violations file so that denominator is all violations (grouped)
### and not just all referrals with a violation

### read in violations file
df_technical_violations_clean_demo <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "df_violations_clean_demo.txt"),
                      delim = "|") |> 
  filter(violation_severity_factor == "Technical Violation") |> 
  mutate(youth_violation_id = paste0(unique_id,
                                    violation_referral_number),
         violation_filed_date_fy = csgjcr::csg_fiscal_year(violation_filed_date,
                                                          fy_start="October")) |> 
  mutate(violation_type_cleaned = 
           case_when(
             violation=="100a  Violation Probation - General" ~ "General Violation",
             violation%in%c("5100c  Viol Prob - Discharge Unsatisfactorily From Placement (2)","5100j  Viol Prob - Violating Placement Rules (3)","5100b  Absenting Self From Court Order Placement (2,6)") ~ "Violation Related to Placement",
             violation=="5100d  Viol Prob - Runaway From Home/Placement" ~ "Runaway",
             violation=="5100e  Viol Prob - Failure to Report to Probation Officer (2)" ~ "Failure to Report to PO",
             violation=="5100i - Viol Prob - Violating School Rules" ~ "Violation of School Rules",
             violation=="5100f  Viol Prob - Curfew Violation (3)" ~ "Curfew Violation",
             violation=="5100l Viol Prob - Failure to Participate in Order Program (11)" ~ "Failure to Participate in Program",
             violation%in%c("5100h  Viol Prob - Truancy - Not attending each Class each Day (4)",
                            "5103c  Truancy 3 Days") ~ "Truancy",
             violation%in%c("5100g  Viol Prob - Failure to Notify PO Of change Of Home/School/Employment Address (5)",
                             "5100k  Viol Prob - Failure to Pay Probation Fees (9)",
                            "xxx - Converted Data") ~ "Other",
             violation=="No Violation/Modification Needed" ~ "No Violation",             
             TRUE ~ as.character(NA))) |> 
  filter(violation_type_cleaned!="No Violation")


```

# 1. Most Common Reasons for Technical Violations

<br>

## Table 1. By FY: Most Common Reasons for Technical Violations

**NOTE:** The base sample and denominator for this analysis is all filed violations where the most serious violation was a technical violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_clean_demo %>% 
  filter(violation_filed_date_fy>=2016) %>% 
  dplyr::group_by(violation_filed_date_fy) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Violation` = violation_filed_date_fy) %>% 
  mutate(`FY of Violation` = as.character(`FY of Violation`))

### overall
df_technical_violations_overall <- df_technical_violations_clean_demo %>% 
  filter(violation_filed_date_fy>=2016) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`FY of Violation` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(9, bold = TRUE)
```

<br>

## Table 2. By Race/Ethnicity: Most Common Reasons for Technical Violations

**NOTE:** The base sample and denominator for this analysis is all filed violations where the most serious violation was a technical violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_clean_demo %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### overall
df_technical_violations_overall <- df_technical_violations_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 3. By Gender: Most Common Reasons for Technical Violations

**NOTE:** The base sample and denominator for this analysis is all filed violations where the most serious violation was a technical violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_clean_demo %>% 
  dplyr::group_by(gender_clean) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean) 

### overall
df_technical_violations_overall <- df_technical_violations_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Gender` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br>

## Table 4. By Age (at start of supervision): Most Common Reasons for Technical Violations

**TO DO:** Fix age variable -- by linking pertinent referral to each violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### turn age into a factor
df_technical_violations_clean_demo %<>%
 mutate(age_at_start_of_supervision_clean = factor(age_at_start_of_supervision_clean,
         levels = c("Less than 12", 
                    "12 to 13",
                    "14 to 15",
                    "16 to 20")))
 
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_clean_demo %>% 
  dplyr::group_by(age_at_start_of_supervision_clean) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age` = age_at_start_of_supervision_clean) 

### overall
df_technical_violations_overall <- df_technical_violations_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Age` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br>

## Table 5. By Risk Level: Most Common Reasons for Technical Violations

**Note:** This is the "listed risk level at the time of referral disposition"

**TO DO:** Double check risk level -- by linking pertinent referral to each violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_clean_demo %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level) 

### overall
df_technical_violations_overall <- df_technical_violations_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 6. By Needs Level: Most Common Reasons for Technical Violations

**Note:** This is the "listed needs level at the time of referral disposition"

**TO DO:** Double check needs level -- by linking pertinent referral to each violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_clean_demo %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level) 

### overall
df_technical_violations_overall <- df_technical_violations_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (%)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

# 2. Most Common Offenses when Technical Violation isn't Primary Offense

**NOTE:** These are currently all new offense violations, regardless of whether a technical violation was present. I am using primary offense at intake as this appears to align with the new offense/technical flag in the violations file. 

**Question 1:** How should we interpret violations coded as new offenses in the violations file, but coded as VOP in the offenses file? Were these new offenses that were never formally referred/diverted and simply documented as VOPs?


```{r include=FALSE,message=FALSE,warning=FALSE}
### import violations file so that denominator is all violations (grouped)
### and not just all referrals with a violation

### read in violations file
df_new_offense_violations_clean_demo <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "df_violations_clean_demo.txt"),
                      delim = "|") |> 
  filter(violation_severity_factor == "New Offense") |> 
  mutate(violation_filed_date_fy = csgjcr::csg_fiscal_year(violation_filed_date,
                                                          fy_start="October")) |> 
  mutate(violation_type_cleaned = 
           case_when(
             violation=="100a  Violation Probation - General" ~ "General Violation",
             violation%in%c("5100c  Viol Prob - Discharge Unsatisfactorily From Placement (2)","5100j  Viol Prob - Violating Placement Rules (3)") ~ "Violation Related to Placement",
             violation=="5100d  Viol Prob - Runaway From Home/Placement" ~ "Runaway",
             violation=="5100e  Viol Prob - Failure to Report to Probation Officer (2)" ~ "Failure to Report to PO",
             violation=="5100i - Viol Prob - Violating School Rules" ~ "Violation of School Rules",
             violation=="5100f  Viol Prob - Curfew Violation (3)" ~ "Curfew Violation",
             violation=="5100l Viol Prob - Failure to Participate in Order Program (11)" ~ "Failure to Participate in Program",
             violation%in%c("5100h  Viol Prob - Truancy - Not attending each Class each Day (4)",
                            "5103c  Truancy 3 Days") ~ "Curfew Violation",
             violation%in%c("5100b  Absenting Self From Court Order Placement (2,6)",
                             "5100g  Viol Prob - Failure to Notify PO Of change Of Home/School/Employment Address (5)",
                             "5100k  Viol Prob - Failure to Pay Probation Fees (9)",
                            "xxx - Converted Data") ~ "Other",
             violation=="No Violation/Modification Needed" ~ "No Violation",             
             TRUE ~ as.character(NA))) |> 
  filter(violation_type_cleaned!="No Violation")

### read in offenses file
df_offenses_clean <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "offenses_clean.txt"),
                      delim = "|") |> 
  filter(ioi == "Primary") |> 
  dplyr::select(unique_id,offense_id,referral_number,offense_date,referral_date, offense_level, offense_description,offense_disposition=disposition,offense_risk_level=risk_level,offense_needs_level=needs_level,offense_year,offense_level_type_combined_grouped,offense_type_grouped)
  

### join two files to obtain offense information associated with new offense violation
df_new_offense_violations_clean_demo_full <- left_join(df_new_offense_violations_clean_demo,
                                                       df_offenses_clean,
                                                       by = c("unique_id","violation_referral_number"="referral_number")) |> 
  mutate(youth_violation_id = paste0(unique_id,
                                    violation_referral_number))

```

<br>

## Table 7. By FY: New Offense Violations

**NOTE:** The base sample and denominator for this analysis is all filed violations where the most serious violation was a new offense violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_new_offense_violations_per_year <- df_new_offense_violations_clean_demo_full %>% 
  filter(violation_filed_date_fy>=2016) %>% 
  dplyr::group_by(violation_filed_date_fy) %>% 
  dplyr::summarise(`All New Offense Violations (N)` = n_distinct(youth_violation_id),
                   `Felony, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `CINS (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="CINS"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `VOP (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="VOP"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Violation` = violation_filed_date_fy) %>% 
  mutate(`FY of Violation` = as.character(`FY of Violation`))

### overall
df_new_offense_violations_overall <- df_new_offense_violations_clean_demo_full %>% 
  filter(violation_filed_date_fy>=2016) %>% 
  dplyr::summarise(`All New Offense Violations (N)` = n_distinct(youth_violation_id),
                   `Felony, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `CINS (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="CINS"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `VOP (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="VOP"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`FY of Violation` = "Overall")

### combine tables for kable
df_new_offense_violations_per_year_table <- rbind(df_new_offense_violations_per_year,df_new_offense_violations_overall)

### print table via kableextra
kable(df_new_offense_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br>

## Table 8. By Race/Ethnicity: New Offense Violations

**NOTE:** The base sample and denominator for this analysis is all filed violations where the most serious violation was a new offense violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_new_offense_violations_clean_demo_full %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`All New Offense Violations (N)` = n_distinct(youth_violation_id),
                   `Felony, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `CINS (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="CINS"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `VOP (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="VOP"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### overall
df_technical_violations_overall <- df_new_offense_violations_clean_demo_full %>% 
   dplyr::summarise(`All New Offense Violations (N)` = n_distinct(youth_violation_id),
                   `Felony, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `CINS (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="CINS"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `VOP (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="VOP"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(4, bold = TRUE)
```

<br>

## Table 9. By Gender: New Offense Violations

**NOTE:** The base sample and denominator for this analysis is all filed violations where the most serious violation was a new offense violation.


```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_new_offense_violations_clean_demo_full %>% 
  dplyr::group_by(gender_clean) %>% 
   dplyr::summarise(`All New Offense Violations (N)` = n_distinct(youth_violation_id),
                   `Felony, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `CINS (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="CINS"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `VOP (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="VOP"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean) 

### overall
df_technical_violations_overall <- df_new_offense_violations_clean_demo_full %>% 
   dplyr::summarise(`All New Offense Violations (N)` = n_distinct(youth_violation_id),
                   `Felony, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `CINS (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="CINS"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `VOP (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="VOP"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Gender` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br>

## Table 10. By Age (at start of supervision): New Offense Violations

**TO DO:** Fix age variable -- by linking pertinent referral to each violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### turn age into a factor
df_new_offense_violations_clean_demo_full %<>%
 mutate(age_at_start_of_supervision_clean = factor(age_at_start_of_supervision_clean,
         levels = c("Less than 12", 
                    "12 to 13",
                    "14 to 15",
                    "16 to 20")))
 
### unique violation grouped
df_technical_violations_per_year <- df_new_offense_violations_clean_demo_full %>% 
  dplyr::group_by(age_at_start_of_supervision_clean) %>% 
  dplyr::summarise(`All New Offense Violations (N)` = n_distinct(youth_violation_id),
                   `Felony, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `CINS (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="CINS"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `VOP (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="VOP"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age` = age_at_start_of_supervision_clean) 

### overall
df_technical_violations_overall <- df_new_offense_violations_clean_demo_full %>% 
   dplyr::summarise(`All New Offense Violations (N)` = n_distinct(youth_violation_id),
                   `Felony, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `CINS (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="CINS"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `VOP (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="VOP"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1)) %>%  
  mutate(`Age` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br>

## Table 11. By Risk Level: New Offense Violations

**Note:** This is the "listed risk level at the time of referral disposition" for the new offense

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_new_offense_violations_clean_demo_full %>% 
  dplyr::group_by(offense_risk_level) %>% 
  dplyr::summarise(`All New Offense Violations (N)` = n_distinct(youth_violation_id),
                   `Felony, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `CINS (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="CINS"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `VOP (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="VOP"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1)) %>%  
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_risk_level) 

### overall
df_technical_violations_overall <- df_new_offense_violations_clean_demo_full %>% 
   dplyr::summarise(`All New Offense Violations (N)` = n_distinct(youth_violation_id),
                   `Felony, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `CINS (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="CINS"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `VOP (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="VOP"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1)) %>%  
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 12. By Needs Level: New Offense Violations

**Note:** This is the "listed needs level at the time of referral disposition" for the new offense

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_new_offense_violations_clean_demo_full %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`All New Offense Violations (N)` = n_distinct(youth_violation_id),
                   `Felony, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `CINS (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="CINS"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `VOP (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="VOP"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1)) %>%  
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level) 

### overall
df_technical_violations_overall <- df_new_offense_violations_clean_demo_full %>% 
   dplyr::summarise(`All New Offense Violations (N)` = n_distinct(youth_violation_id),
                   `Felony, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Felony, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Felony, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Violent (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Violent"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Property (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Property"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Drug (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Drug"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Misdemeanor, Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Misdemeanor, Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `CINS (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="CINS"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `VOP (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="VOP"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[offense_level_type_combined_grouped=="Other"])/`All New Offense Violations (N)`,
                                                                       accuracy = .1)) %>%  
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>
