---
title: "What happens to youth as the result of a technical violation?"
format: html
---

**What happens to youth as the result of a technical violation?** 

**1.** 

* Of youth who receive a technical violation as a primary offense, what proportion are placed in a residential facility; detention; committed to state custody? How does this vary across race/ethnicity, sex, and risk level? 

* Of youth who receive a technical violation as a primary offense, what proportion receive an extended supervision episode? 

**2.**

* What is the average length of time a supervision episode is extended as the result of a technical violation? How does this vary across race/ethnicity, sex, and risk level? 


**3.** 
* In Dallas, probation can file a violation to get a kid into a 30 day residential program. The violation does not go to the prosecutor. If the kid is successful in the placement, then the department dismisses the violation. How often does this happen? 



**Double check following coding/grouping of violation dispositions with team:**

* "No Disposition" = "ADJUDICATED - NO DISPOSITION"

* "Probation" = "ADJUDICATED PLACED ON PROBATION", "CONSOLIDATED MULTIPLE CHARGES - ONE DISPOSITION (PROBATION)") 

* "Dismissed/Withdrawn" = "COMPLAINT DISMISSED BY COURT", "DISMISSED OR WITHDRAWN BY DEPARTMENT", "DISMISSED WITHOUT PROSECUTION",
                            "DISMISSED WITHOUT PROSECUTION - PA", "NO CASE FILED BY DA NO JD ACTION", "NO INTAKE, NO PROBABLE CAUSE - * * "DECLINED BY PROSECUTOR", "NO INTAKE, NO PROBABLE CAUSE - PROBATION DEPARTMENT", "NO INTAKE, PROBABLE CAUSE - PROSECUTOR", "NONSUIT", "NONSUIT (PA)"
                            
* "Other" = "CONSOLIDATED IN ANOTHER CASE/REFERRAL", "CONSOLIDATED BY DEPARTMENT", "FILED AS A MOTION TO MODIFY","FILED AS MOTION TO MODIFY", "MOD/VOP Disposed by Intake (PA)","NO INTAKE, DISPOSED BY INTAKE","TAKEN INTO CONSIDERATION","SUPERVISORY CAUTION BY DEPARTMENT", "TAKEN INTO CONSIDERATION (PA Complaint)", "TRANSFER OF DISPOSITION BY COURT"
                            
* "Placement" = "CONSOLIDATED MULTIPLE CHARGES - ONE DISPOSITION (PLACEMENT)", "MODIFICATION PLACEMENT","MODIFIED TO PLACEMENT-DETERMINATE SENTENCE PROB", "PROBATION/PLACEMENT"
                            
* "Commitment" = "PROB REVOKED-DETERMINATE COMMITMENT","PROB REVOKED-INDETERMINATE COMMITMENT","TJJD DETERMINATE COMMITMENT","TJJD INDETERMINATE COMMITMENT"  
                            
* "Probation Extension" = "PROBATION EXTENDED" 

* "Probation Modified" = "PROBATION MODIFIED"  

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### data path
sp_data_path <- csg_get_project_path("jj-av-dallas")

### viz output path
# sp_viz_output_path <- paste(sp_data_path, "/Output/r_output_presentation")

```

```{r include=FALSE,message=FALSE,warning=FALSE}
###############################
### import dallas analytic file
###############################

### set sharepoint path using sp_data_path and file.path function 
sharepoint_jj_av_dallas_analytic_data <- file.path(sp_data_path,"Data/analysis")

df_dallas_county_av_supervision_analytic_file <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "df_dallas_county_av_supervision_analytic_file.txt"),
                      delim = "|") %>% 
  mutate(offense_referral_risk_level = 
           case_when(
             offense_referral_risk_level=="Low Risk" ~ 1,
             offense_referral_risk_level%in%c("Medium-Low Risk",
                             "Medium-High Risk",
                             "Moderate Risk") ~ 2,
             offense_referral_risk_level=="High Risk" ~ 3,             
             offense_referral_risk_level=="Unknown" ~ 4,
             offense_referral_risk_level=="Not Administered" ~ 5,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_risk_level = factor(offense_referral_risk_level,
         levels = c(1,2,3,4,5),
         labels =  c("Low Risk", 
                     "Moderate Risk", 
                     "High Risk",
                     "Unknown",
                     "Not Administered")),
         offense_referral_needs_level = 
           case_when(
             offense_referral_needs_level=="Low Needs" ~ 1,
             offense_referral_needs_level=="Moderate Needs" ~ 2,
             offense_referral_needs_level=="High Needs" ~ 3,             
             offense_referral_needs_level=="Unknown" ~ 4,
             offense_referral_needs_level=="Not Administered" ~ 5,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_needs_level = factor(offense_referral_needs_level,
         levels = c(1,2,3,4,5),
         labels = c("Low Needs", 
                    "Moderate Needs", 
                    "High Needs",
                    "Unknown",
                    "Not Administered"))) |> 
  ### de-dup by unique_supervision_id for mean calculations
  distinct(unique_supervision_id,
           .keep_all = TRUE)

```

```{r include=FALSE,message=FALSE,warning=FALSE}
### import violations file so that denominator is all violations (grouped)
### and not just all referrals with a violation

### read in violations file
df_technical_violations_dispo_clean_demo <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "df_violations_clean_demo.txt"),
                      delim = "|") |> 
  filter(violation_severity_factor == "Technical Violation") |> 
  mutate(youth_violation_id = paste0(unique_id,
                                    violation_referral_number),
         violation_filed_date_fy = csgjcr::csg_fiscal_year(violation_filed_date,
                                                          fy_start="October")) |> 
  mutate(violation_type_cleaned = 
           case_when(
             violation=="100a  Violation Probation - General" ~ "General Violation",
             violation%in%c("5100c  Viol Prob - Discharge Unsatisfactorily From Placement (2)","5100j  Viol Prob - Violating Placement Rules (3)") ~ "Violation Related to Placement",
             violation=="5100d  Viol Prob - Runaway From Home/Placement" ~ "Runaway",
             violation=="5100e  Viol Prob - Failure to Report to Probation Officer (2)" ~ "Failure to Report to PO",
             violation=="5100i - Viol Prob - Violating School Rules" ~ "Violation of School Rules",
             violation=="5100f  Viol Prob - Curfew Violation (3)" ~ "Curfew Violation",
             violation=="5100l Viol Prob - Failure to Participate in Order Program (11)" ~ "Failure to Participate in Program",
             violation%in%c("5100h  Viol Prob - Truancy - Not attending each Class each Day (4)",
                            "5103c  Truancy 3 Days") ~ "Curfew Violation",
             violation%in%c("5100b  Absenting Self From Court Order Placement (2,6)",
                             "5100g  Viol Prob - Failure to Notify PO Of change Of Home/School/Employment Address (5)",
                             "5100k  Viol Prob - Failure to Pay Probation Fees (9)",
                            "xxx - Converted Data") ~ "Other",
             violation=="No Violation/Modification Needed" ~ "No Violation",             
             TRUE ~ as.character(NA))) |> 
    mutate(violation_dispo_clean = 
           case_when(
             violation_disposition=="ADJUDICATED - NO DISPOSITION" ~ "No Disposition",
             violation_disposition%in%c("ADJUDICATED PLACED ON PROBATION",
                            "CONSOLIDATED MULTIPLE CHARGES - ONE DISPOSITION (PROBATION)") ~ "Probation",
             violation_disposition%in%c("COMPLAINT DISMISSED BY COURT",
                            "DISMISSED OR WITHDRAWN BY DEPARTMENT",
                            "DISMISSED WITHOUT PROSECUTION",
                            "DISMISSED WITHOUT PROSECUTION - PA",
                            "NO CASE FILED BY DA NO JD ACTION",
                            "NO INTAKE, NO PROBABLE CAUSE - DECLINED BY PROSECUTOR",
                            "NO INTAKE, NO PROBABLE CAUSE - PROBATION DEPARTMENT",
                            "NO INTAKE, PROBABLE CAUSE - PROSECUTOR",
                            "NONSUIT",
                            "NONSUIT (PA)") ~ "Dismissed/Withdrawn",
             violation_disposition%in%c("CONSOLIDATED IN ANOTHER CASE/REFERRAL",
                            "CONSOLIDATED BY DEPARTMENT",
                            "FILED AS A MOTION TO MODIFY",
                            "FILED AS MOTION TO MODIFY",
                            "MOD/VOP Disposed by Intake (PA)",
                            "NO INTAKE, DISPOSED BY INTAKE",
                            "TAKEN INTO CONSIDERATION",
                            "SUPERVISORY CAUTION BY DEPARTMENT",
                            "TAKEN INTO CONSIDERATION (PA Complaint)",
                            "TRANSFER OF DISPOSITION BY COURT") ~ "Other",
             violation_disposition%in%c("CONSOLIDATED MULTIPLE CHARGES - ONE DISPOSITION (PLACEMENT)",
                            "MODIFICATION PLACEMENT",
                            "MODIFIED TO PLACEMENT-DETERMINATE SENTENCE PROB",
                            "PROBATION/PLACEMENT") ~ "Placement",
             violation_disposition%in%c("PROB REVOKED-DETERMINATE COMMITMENT",
                            "PROB REVOKED-INDETERMINATE COMMITMENT",
                            "TJJD DETERMINATE COMMITMENT",
                            "TJJD INDETERMINATE COMMITMENT") ~ "Commitment",  
             violation_disposition%in%c("PROBATION EXTENDED") ~ "Probation Extension",  
             violation_disposition%in%c("PROBATION MODIFIED") ~ "Probation Modified",   
             TRUE ~ as.character(NA))) |> 
  filter(violation_type_cleaned!="No Violation")

```


# 1. Technical Violation Disposition Outcomes

<br>

## Table 1. By FY: Technical Violation Disposition Outcomes

**NOTE:** The base sample and denominator for this analysis is all filed violations where the most serious violation was a technical violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_dispo_clean_demo %>% 
  filter(violation_filed_date_fy>=2016) %>% 
  dplyr::group_by(violation_filed_date_fy) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Violation` = violation_filed_date_fy) %>% 
  mutate(`FY of Violation` = as.character(`FY of Violation`))

### overall
df_technical_violations_overall <- df_technical_violations_dispo_clean_demo %>% 
  filter(violation_filed_date_fy>=2016) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`FY of Violation` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(9, bold = TRUE)
```


<br>

## Table 2. By Race/Ethnicity: Technical Violation Disposition Outcomes

**NOTE:** The base sample and denominator for this analysis is all filed violations where the most serious violation was a technical violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean)

### overall
df_technical_violations_overall <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 3. By Gender: Technical Violation Disposition Outcomes

**NOTE:** The base sample and denominator for this analysis is all filed violations where the most serious violation was a technical violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::group_by(gender_clean) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean)

### overall
df_technical_violations_overall <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Gender` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br>

## Table 4. By Age: Technical Violation Disposition Outcomes

**TO DO:** Fix age variable -- by linking pertinent referral to each violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### turn age into a factor
df_technical_violations_dispo_clean_demo %<>%
 mutate(age_at_start_of_supervision_clean = factor(age_at_start_of_supervision_clean,
         levels = c("Less than 12", 
                    "12 to 13",
                    "14 to 15",
                    "16 to 20")))

### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::group_by(age_at_start_of_supervision_clean) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age` = age_at_start_of_supervision_clean)

### overall
df_technical_violations_overall <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Age` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br>

## Table 5. By Risk Level: Technical Violation Disposition Outcomes

**Note:** This is the "listed risk level at the time of referral disposition"

**TO DO:** Double check risk level -- by linking pertinent referral to each violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level)

### overall
df_technical_violations_overall <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 6. By Needs Level: Technical Violation Disposition Outcomes

**Note:** This is the "listed needs level at the time of referral disposition"

**TO DO:** Double check needs level -- by linking pertinent referral to each violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level)

### overall
df_technical_violations_overall <- df_technical_violations_dispo_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `Probation (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Extension (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Extension"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Probation Modified (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Probation Modified"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Placement (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Commitment (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Commitment"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Dismissed/Withdrawn (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="Dismissed/Withdrawn"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `No Disposition (%)` = scales::percent(n_distinct(youth_violation_id[violation_dispo_clean=="No Disposition"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Missing Disposition Data (%)` = scales::percent(n_distinct(youth_violation_id[is.na(violation_dispo_clean)==TRUE])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

# 2. Average Length of Supervision Extension

What is the average length of time a supervision episode is extended as the result of a technical violation? How does this vary across race/ethnicity, sex, and risk level? 

**Question:** Does this need to be linked to a technical violation by timing or by violation disposition? If by disposition, we'd need to clean dispositions differently (to look at all dispositions, not just most serious...)

<br><br>

