---
title: "Why do youth receive technical violations?"
format: html
---

**Why do youth receive technical violations?** 

* What are the most common reasons for technical violations when the violation was the primary offense? How do reasons vary across race/ethnicity, sex, and risk level? (Technical violation N: 2,333)

* What are the most common offenses when the technical violation was not the primary offense? There are two ways to run this analysis -- types of new offenses across all violations or only types of new offenses where there is a technical violation listed. Which do we want? (New offense N: 564)



**Double check following coding/grouping of technical violations with team:**

* "General Violation" = "100a  Violation Probation - General" 

* "Violation Related to Placement" = "5100c  Viol Prob - Discharge Unsatisfactorily From Placement (2)","5100j  Viol Prob - Violating Placement Rules (3)", "5100b  Absenting Self From Court Order Placement (2,6)"

* "Runaway" = "5100d  Viol Prob - Runaway From Home/Placement" 

* "Failure to Report to PO" = "5100e  Viol Prob - Failure to Report to Probation Officer (2)" 

* "Violation of School Rules" = "5100i - Viol Prob - Violating School Rules" 

* "Curfew Violation" = "5100f  Viol Prob - Curfew Violation (3)" 

* "Failure to Participate in Program" = "5100l Viol Prob - Failure to Participate in Order Program (11)" 

* "Truancy" = "5100h  Viol Prob - Truancy - Not attending each Class each Day (4)","5103c  Truancy 3 Days"

* "Other" = "5100g  Viol Prob - Failure to Notify PO Of change Of Home/School/Employment Address (5)","5100k  Viol Prob - Failure to Pay Probation Fees (9)","xxx - Converted Data")

* "No Violation" = "No Violation/Modification Needed" (*I have filtered these out from the first section*)

<br>

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog","ggtext","ggpattern")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### data path
sp_data_path <- csg_get_project_path("jj-av-dallas")

### set sharepoint path using sp_data_path and file.path function 
sharepoint_jj_av_dallas_analytic_data <- file.path(sp_data_path,"Data/analysis")

## viz output path
sp_viz_output_path <- paste0(sp_data_path,"/output/r_output_presentation")

```

```{r include=FALSE,message=FALSE,warning=FALSE}
### import violations file so that denominator is all violations (grouped)
### and not just all referrals with a violation

### read in violations file
df_technical_violations_clean_demo <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "df_violations_clean_demo.txt"),
                      delim = "|") |> 
  filter(violation_severity_factor == "Technical Violation") |> 
  mutate(youth_violation_id = paste0(unique_id,
                                    violation_referral_number),
         violation_filed_date_fy = csgjcr::csg_fiscal_year(violation_filed_date,
                                                          fy_start="October")) |> 
  mutate(violation_type_cleaned = 
           case_when(
             violation=="100a  Violation Probation - General" ~ "General Violation",
             violation%in%c("5100c  Viol Prob - Discharge Unsatisfactorily From Placement (2)","5100j  Viol Prob - Violating Placement Rules (3)","5100b  Absenting Self From Court Order Placement (2,6)") ~ "Violation Related to Placement",
             violation=="5100d  Viol Prob - Runaway From Home/Placement" ~ "Runaway",
             violation=="5100e  Viol Prob - Failure to Report to Probation Officer (2)" ~ "Failure to Report to PO",
             violation=="5100i - Viol Prob - Violating School Rules" ~ "Violation of School Rules",
             violation=="5100f  Viol Prob - Curfew Violation (3)" ~ "Curfew Violation",
             violation=="5100l Viol Prob - Failure to Participate in Order Program (11)" ~ "Failure to Participate in Program",
             violation%in%c("5100h  Viol Prob - Truancy - Not attending each Class each Day (4)",
                            "5103c  Truancy 3 Days") ~ "Truancy",
             violation%in%c("5100g  Viol Prob - Failure to Notify PO Of change Of Home/School/Employment Address (5)",
                             "5100k  Viol Prob - Failure to Pay Probation Fees (9)",
                            "xxx - Converted Data") ~ "Other",
             violation=="No Violation/Modification Needed" ~ "No Violation",             
             TRUE ~ as.character(NA))) |> 
  filter(violation_type_cleaned!="No Violation") %>% 
  mutate(offense_referral_risk_level = 
           case_when(
             offense_referral_risk_level=="Low Risk" ~ 1,
             offense_referral_risk_level%in%c("Medium-Low Risk",
                             "Medium-High Risk",
                             "Moderate Risk") ~ 2,
             offense_referral_risk_level=="High Risk" ~ 3,             
             offense_referral_risk_level%in%c("Unknown/Not Administered") ~ 4,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_risk_level = factor(offense_referral_risk_level,
         levels = c(1,2,3,4),
         labels =  c("Low Risk", 
                     "Moderate Risk", 
                     "High Risk",
                     "Unknown/Not Administered")),
         offense_referral_needs_level = 
           case_when(
             offense_referral_needs_level=="Low Needs" ~ 1,
             offense_referral_needs_level=="Moderate Needs" ~ 2,
             offense_referral_needs_level=="High Needs" ~ 3,             
             offense_referral_needs_level%in%c("Unknown/Not Administered") ~ 4,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_needs_level = factor(offense_referral_needs_level,
         levels = c(1,2,3,4),
         labels = c("Low Needs", 
                    "Moderate Needs", 
                    "High Needs",
                    "Unknown/Not Administered"))) |> 
  ### remove FY 2023 (year is incomplete based on timing of data pull) 
  filter(violation_filed_date_fy!=2023)


```

# 1. Most Common Reasons for Technical Violations

<br>

## Table 1. By FY: Most Common Reasons for Technical Violations

**NOTE:** The base sample and denominator for this analysis is all filed violations where the most serious violation was a technical violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_clean_demo %>% 
  filter(violation_filed_date_fy>=2016) %>% 
  dplyr::group_by(violation_filed_date_fy) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Violation` = violation_filed_date_fy) %>% 
  mutate(`FY of Violation` = as.character(`FY of Violation`))

### overall
df_technical_violations_overall <- df_technical_violations_clean_demo %>% 
  filter(violation_filed_date_fy>=2016) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`FY of Violation` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

```{r }
### unique youth, referrals, and supervision episodes
df_technical_violations_risk_viz <- df_technical_violations_clean_demo |> 
  filter(violation_filed_date_fy>=2016) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation` = n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                   `Curfew Violations` = n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                   `Failure to Participate in Program` = n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                   `Failure to Report to PO` = n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                   `Violation Related to Placement` = n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                   `Runaway` = n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                   `Violation of School Rules` = n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                   `Other Violations` = n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`) |>  
  ungroup() |> 
  pivot_longer(!`All Technical Violations (N)`, names_to = "complaint_type", values_to = "percent") |> 
  arrange(desc(percent))

### plot
### bar plot
ggplot(data = df_technical_violations_risk_viz,
       aes(x = reorder(complaint_type,-percent),
           y = percent,
           fill = complaint_type)) + 
  geom_bar(stat = "identity",  
           color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(min(0), 
                                max(.3))) +
  geom_label(
    aes(
      y = percent,
      label = scales::percent(percent,
                              accuracy = 1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 6,
    colour = "white",
    show.legend = FALSE
  ) +
  scale_fill_manual(values = c("#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084")) +
  guides(fill = FALSE) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme_minimal() +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        # axis.text.x = element_markdown(),
        axis.text.y = element_markdown(size = 16),
        axis.text.x = element_text(face = "bold", hjust = 1, size = 16),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_31_technical_violation_reasons.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>

## Table 2. By Race/Ethnicity: Most Common Reasons for Technical Violations

**NOTE:** The base sample and denominator for this analysis is all filed violations where the most serious violation was a technical violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_clean_demo %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### overall
df_technical_violations_overall <- df_technical_violations_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br>

## Table 3. By Gender: Most Common Reasons for Technical Violations

**NOTE:** The base sample and denominator for this analysis is all filed violations where the most serious violation was a technical violation.

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_clean_demo %>% 
  dplyr::group_by(gender_clean) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean) 

### overall
df_technical_violations_overall <- df_technical_violations_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Gender` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

```{r }

### unique complaints split out
df_technical_violations_clean_demo_age_to_join_counts <- df_technical_violations_clean_demo %>% 
  dplyr::summarise(`Male` = n_distinct(youth_violation_id[gender_clean=="Male"]),
                   `Female` = n_distinct(youth_violation_id[gender_clean=="Female"])) |> 
  mutate(group = "counts") |> 
  pivot_longer(!group, names_to = "gender_clean", values_to = "count") |> 
  dplyr::select(-group)

### unique violation grouped
df_technical_violations_per_year_viz <- df_technical_violations_clean_demo %>% 
  dplyr::group_by(gender_clean) %>% 
   dplyr::summarise(`Runaway Violation` = n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/n_distinct(youth_violation_id),
                   `All Other Violations` = n_distinct(youth_violation_id[violation_type_cleaned!="Runaway"])/n_distinct(youth_violation_id),) |>  
  ungroup() %>% 
  pivot_longer(!gender_clean, names_to = "complaint_type", values_to = "percent") |> 
  arrange(desc(percent)) |> 
  left_join(df_technical_violations_clean_demo_age_to_join_counts,
            by = "gender_clean") %>% 
  mutate(
    gender_clean_n = paste0(
      "<span style = 'font-size:14pt'>", gender_clean, "</span><br>",
      "<span style = 'font-size:10pt'><em>", "N = ", scales::comma(count, 1), "</em></span>")) |> 
  mutate(offense_type = factor(complaint_type,
                                levels = c("Runaway Violation",
                                           "All Other Violations"))) |> 
  arrange(offense_type)

### plot
ggplot(data = df_technical_violations_per_year_viz, aes(y = percent, x = gender_clean_n, fill = forcats::fct_rev(offense_type))) + 
  geom_bar(stat = "identity", color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent) +
   geom_label(
    aes(
      y = percent,
      label = scales::percent(percent,
                              accuracy = 1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 5,
    fill = "white",
    colour = "gray40",
    show.legend = FALSE
  ) +
  scale_fill_manual(values = c("gray","#2F7084")) +
  guides(fill = guide_legend(reverse = TRUE,
                             title.position = "top",
                             label.position = "bottom",
                             keywidth = 3,
                             nrow = 1)) +
  labs(x = NULL, y = NULL,
       fill = "Technical Violation Reason",
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme(legend.position = "top",
        legend.title = element_text(hjust = 0.5,size = 13),
        legend.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        # axis.text.x = element_markdown(),
        axis.text.y = element_markdown(size=14),
        axis.text.x = element_text(face = "bold", hjust = 1, size = 14),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_32_technical_violation_reasons_gender_runaway.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )

```

<br>

## Table 4. By Age (at start of supervision): Most Common Reasons for Technical Violations

```{r echo=FALSE,message=FALSE,warning=FALSE}
### turn age into a factor
df_technical_violations_clean_demo %<>%
 mutate(age_at_start_of_supervision_clean = factor(age_at_start_of_supervision_clean,
         levels = c("Less than 12", 
                    "12 to 13",
                    "14 to 16",
                    "17+")))
 
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_clean_demo %>% 
  dplyr::group_by(age_at_start_of_supervision_clean) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age` = age_at_start_of_supervision_clean) 

### overall
df_technical_violations_overall <- df_technical_violations_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Age` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

```{r }

### unique complaints split out
df_technical_violations_clean_demo_age_to_join_counts <- df_technical_violations_clean_demo %>% 
  dplyr::summarise(`Less than 12` = n_distinct(youth_violation_id[age_at_start_of_supervision_clean=="Less than 12"]),
                   `12 to 13` = n_distinct(youth_violation_id[age_at_start_of_supervision_clean=="12 to 13"]),
                   `14 to 16` = n_distinct(youth_violation_id[age_at_start_of_supervision_clean=="14 to 16"]),
                   `17+` = n_distinct(youth_violation_id[age_at_start_of_supervision_clean=="17+"])) |> 
  mutate(group = "counts") |> 
  pivot_longer(!group, names_to = "age_at_start_of_supervision_clean", values_to = "count") |> 
  dplyr::select(-group)

### unique violation grouped
df_technical_violations_per_year_viz <- df_technical_violations_clean_demo %>% 
  dplyr::group_by(age_at_start_of_supervision_clean) %>% 
   dplyr::summarise(`Failure to Participate\nin Program` = n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/n_distinct(youth_violation_id),
                   `All Other Violations` = n_distinct(youth_violation_id[violation_type_cleaned!="Failure to Participate in Program"])/n_distinct(youth_violation_id),) |>  
  ungroup() %>% 
  pivot_longer(!age_at_start_of_supervision_clean, names_to = "complaint_type", values_to = "percent") |> 
  arrange(desc(percent)) |> 
  left_join(df_technical_violations_clean_demo_age_to_join_counts,
            by = "age_at_start_of_supervision_clean") %>% 
  mutate(
    age_at_start_of_supervision_clean_n = paste0(
      "<span style = 'font-size:14pt'>", age_at_start_of_supervision_clean, "</span><br>",
      "<span style = 'font-size:10pt'><em>", "N = ", scales::comma(count, 1), "</em></span>")) |> 
  mutate(offense_type = factor(complaint_type,
                                levels = c("Failure to Participate\nin Program",
                                           "All Other Violations"))) |> 
  mutate(age_at_start_of_supervision_clean = factor(age_at_start_of_supervision_clean,
         levels = c("Less than 12", 
                    "12 to 13",
                    "14 to 16",
                    "17+"))) |> 
  arrange(age_at_start_of_supervision_clean,offense_type) |> 
  filter(age_at_start_of_supervision_clean!="Less than 12")

### plot
ggplot(data = df_technical_violations_per_year_viz, aes(y = percent, x = age_at_start_of_supervision_clean_n, fill = forcats::fct_rev(offense_type))) + 
  geom_bar(stat = "identity", color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent) +
   geom_label(
    aes(
      y = percent,
      label = scales::percent(percent,
                              accuracy = 1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 5,
    fill = "white",
    colour = "gray40",
    show.legend = FALSE
  ) +
  scale_fill_manual(values = c("gray","#2F7084")) +
  guides(fill = guide_legend(reverse = TRUE,
                             title.position = "top",
                             label.position = "bottom",
                             keywidth = 3,
                             nrow = 1)) +
  labs(x = NULL, y = NULL,
       fill = "Technical Violation Reason",
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme(legend.position = "top",
        legend.title = element_text(hjust = 0.5,size = 13),
        legend.text = element_text(size = 12),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        # axis.text.x = element_markdown(),
        axis.text.y = element_markdown(size=14),
        axis.text.x = element_text(face = "bold", hjust = 1, size = 14),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_32_technical_violation_reasons_age_program.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br>

## Table 5. By Risk Level: Most Common Reasons for Technical Violations

**Note:** This is the "listed risk level at the time of referral disposition"

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_clean_demo %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level) 

### overall
df_technical_violations_overall <- df_technical_violations_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br>

## Table 6. By Needs Level: Most Common Reasons for Technical Violations

**Note:** This is the "listed needs level at the time of referral disposition"

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique violation grouped
df_technical_violations_per_year <- df_technical_violations_clean_demo %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level) 

### overall
df_technical_violations_overall <- df_technical_violations_clean_demo %>% 
  dplyr::summarise(`All Technical Violations (N)` = n_distinct(youth_violation_id),
                   `General Violation (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="General Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Curfew Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Curfew Violation"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Participate in Program (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Participate in Program"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Failure to Report to PO (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Failure to Report to PO"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation Related to Placement (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation Related to Placement"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Runaway (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Runaway"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Violation of School Rules (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Violation of School Rules"])/`All Technical Violations (N)`,
                                                                       accuracy = .1),
                   `Other Violations (row %)` = scales::percent(n_distinct(youth_violation_id[violation_type_cleaned=="Other"])/`All Technical Violations (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_technical_violations_per_year_table <- rbind(df_technical_violations_per_year,df_technical_violations_overall)

### print table via kableextra
kable(df_technical_violations_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br><br>

# 2. Most Common Offenses when Technical Violation isn't Primary Offense

**UPDATE:** We noticed that about 20% of new offense violations were coded as new offenses in the violations file, but coded as VOP in the offenses file. In conversation with the Dallas team, we learned that this most often occurs because the DA wants to keep a given youth on the original and more severe charge. As a result, we won't have a representative sample of offenses if lower-level ones are more likely to be downgraded to VOPs, etc. so we are excluding all analysis in this section. 


<br><br>
