---
title: "How are modifications used?"
format: html
---


**How are modifications used?**

* What is the average number of modifications per supervision episode? How does this vary across race/ethnicity, sex, and risk level? 

* What is the average number of modifications for youth who receive a technical violation? How does this vary across race/ethnicity, sex, and risk level? 


```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog","ggpattern","ggtext")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### set project path with csg_get_project_path (just once)
# csg_set_project_path(project = "jj-av-dallas",
# sp_folder = "C:/Users/abyrum/The Council of State Governments/JC Research - JJ_AV - JJ_AV/Dallas", force = TRUE)

### data path
sp_data_path <- csg_get_project_path("jj-av-dallas")

## viz output path
sp_viz_output_path <- paste0(sp_data_path,"/output/r_output_presentation")

```

```{r include=FALSE,message=FALSE,warning=FALSE}
###############################
### import dallas analytic file
###############################

### set sharepoint path using sp_data_path and file.path function 
sharepoint_jj_av_dallas_analytic_data <- file.path(sp_data_path,"Data/analysis")

df_dallas_county_av_supervision_analytic_file <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "df_dallas_county_av_supervision_analytic_file.txt"),
                      delim = "|") %>% 
  mutate(offense_referral_risk_level = 
           case_when(
             offense_referral_risk_level=="Low Risk" ~ 1,
             offense_referral_risk_level%in%c("Medium-Low Risk",
                             "Medium-High Risk",
                             "Moderate Risk") ~ 2,
             offense_referral_risk_level=="High Risk" ~ 3,             
             offense_referral_risk_level%in%c("Unknown/Not Administered") ~ 4,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_risk_level = factor(offense_referral_risk_level,
         levels = c(1,2,3,4),
         labels =  c("Low Risk", 
                     "Moderate Risk", 
                     "High Risk",
                     "Unknown/Not Administered")),
         offense_referral_needs_level = 
           case_when(
             offense_referral_needs_level=="Low Needs" ~ 1,
             offense_referral_needs_level=="Moderate Needs" ~ 2,
             offense_referral_needs_level=="High Needs" ~ 3,             
             offense_referral_needs_level%in%c("Unknown/Not Administered") ~ 4,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_needs_level = factor(offense_referral_needs_level,
         levels = c(1,2,3,4),
         labels = c("Low Needs", 
                    "Moderate Needs", 
                    "High Needs",
                    "Unknown/Not Administered"))) |> 
  ### remove FY 2023 Completion (year is incomplete based on timing of data pull) 
  filter(supervision_end_fy!=2023)

```

# Modifications Overview

**NOTE:** All analysis of supervision level modifications (e.g., supervision episodes with at least one supervision level modification) refer to instances where a supervision phase/level is modified to a more intensive level of supervision. 

<br>


```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
### explore LOS over time to see what switch to grouping by FY of completion looks like

### total supervision los per FY of exit
df_los_per_year <- df_dallas_county_av_supervision_analytic_file %>% 
  distinct(unique_supervision_id,
           .keep_all = TRUE) |> 
  dplyr::group_by(supervision_end_fy) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Mean LOS` = mean(overall_supervision_los_days.x,
                              na.rm = TRUE),
            `Median LOS` = median(overall_supervision_los_days.x,
                              na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Completion` = supervision_end_fy) %>% 
  mutate(`FY of Completion` = as.character(`FY of Completion`))

### overall
df_los_overall <- df_dallas_county_av_supervision_analytic_file %>% 
    distinct(unique_supervision_id,
           .keep_all = TRUE) |> 
   dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Mean LOS` = mean(overall_supervision_los_days.x,
                              na.rm = TRUE),
            `Median LOS` = median(overall_supervision_los_days.x,
                              na.rm = TRUE)) %>% 
  mutate(`FY of Completion` = "Overall")

### combine tables for kable
df_los_per_year_table <- rbind(df_los_per_year,
                               df_los_overall)

### print table via kableextra
kable(df_los_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7, bold = TRUE) |> 
### save out
save_kable("C:\\Users\\abyrum\\Documents\\table_los_per_year_table.png")
```

 
## Table 1. By FY: Percentage of Supervision Episodes/Referrals with a Supervision Modification and Extension

```{r echo=FALSE,message=FALSE,warning=FALSE}
### create denominator -- unique referrals for entire sample
unique_referrals_sample_denom <- n_distinct(df_dallas_county_av_supervision_analytic_file$unique_id,
                                            df_dallas_county_av_supervision_analytic_file$referral_number)

### create denominator -- unique supervision episodes
unique_supervision_episode_denom <- n_distinct(df_dallas_county_av_supervision_analytic_file$unique_referral_id)

### create denominator -- unique youth for entire sample
unique_youth_sample_denom <- n_distinct(df_dallas_county_av_supervision_analytic_file$unique_id)

### unique youth and referrals per FY of exit
df_modifications_extensions_per_year <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(supervision_end_fy) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (row %)` = scales::percent(n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (row %)` = scales::percent(n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Completion` = supervision_end_fy) %>% 
  mutate(`FY of Completion` = as.character(`FY of Completion`))

### overall
df_modifications_extensions_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (row %)` = scales::percent(n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (row %)` = scales::percent(n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`FY of Completion` = "Overall")

### combine tables for kable
df_modifications_extensions_per_year_table <- rbind(df_modifications_extensions_per_year,df_modifications_extensions_overall)

### print table via kableextra
kable(df_modifications_extensions_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

## slide 23a
```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and referrals per FY of exit
df_modifications_extensions_per_year_viz <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(supervision_end_fy) %>% 
  dplyr::summarise(percent = n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/n_distinct(unique_referral_id)) %>% 
  ungroup() |> 
  mutate(group = "dallas")

###geom_line 
ggplot(data = df_modifications_extensions_per_year_viz, aes(x = supervision_end_fy, y = percent
                                                            ,
                                                            color = group,
                                                            group = group
                                                            )) +
  geom_line(color = "black", size = 2.75) +
  geom_line(size = 2.2) +
  geom_point(color = "black", size = 4) +
  geom_point(size = 3.5) +
  labs(x = "Fiscal Year", y = "Supervision Episodes with\nProbation Modification (%)", color=NULL, title = NULL, caption = NULL) +
  scale_y_continuous(label=scales::percent_format(accuracy=1),
                     limits = c(min(0), 
                                max(.4))) +
  theme(legend.position = "none",
        legend.title = element_text(hjust = 0.5,size = 13),
        legend.text = element_text(size = 13),
        panel.grid.major.x = element_blank(),      
        plot.title = element_text( hjust = 0.5),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.title.x = element_text(size = 16,margin = margin(t = 15)),
        axis.title.y = element_text(size = 16,margin = margin(r = 15)),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5)) +  
  scale_color_manual(values = c("#1F4A58")) +
  scale_fill_manual(values = c("#1F4A58")) +
  geom_label_repel(aes(label = scales::percent(as.numeric(percent),
                                               accuracy = 0.1),
                    fill = group
                    ),
                   hjust = .1,
                   label.padding = 0.2,
                   box.padding = 0.2,
                   color = "white",
                   size = 5,
                   segment.color = NA,
                   fontface = "bold",
                   na.rm = TRUE,
                   show.legend = FALSE)

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_23_modification_rate_overall.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br><br>

## Table 2. By Race/Ethnicity: Percentage of Supervision Episodes/Referrals with a Supervision Modification and Extension

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_modifications_extensions_race <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (row %)` = scales::percent(n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (row %)` = scales::percent(n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean)

### overall
df_modifications_extensions_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (row %)` = scales::percent(n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (row %)` = scales::percent(n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_modifications_extensions_race_table <- rbind(df_modifications_extensions_race,df_modifications_extensions_overall)

### print table via kableextra
kable(df_modifications_extensions_race_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

```{r }
### unique youth, referrals, and supervision episodes
df_modifications_extensions_race_rri <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification` = n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
             `Supervision Episodes, with at least one level modification (RRI to White youth)` = round((n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`)/0.16666667, digits = 1),
            `Supervision Episodes, with at least one supervision extension` = n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
            `Supervision Episodes, with at least one supervision extension (RRI to White youth)` = round((n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`)/0.09779614, digits = 1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean)

### remove groups analysis with small sample size
### pull out RRIs for plot
### use gather to shift data from wide to long
df_modifications_extensions_race_rri_viz <- df_modifications_extensions_race_rri %>% 
  filter(`Race/Ethnicity`%in%c("Black",
                               "Hispanic",
                               "White")) %>% 
  dplyr::select(`Race/Ethnicity`,rri=`Supervision Episodes, with at least one level modification (RRI to White youth)`) %>% 
  dplyr::filter(`Race/Ethnicity`!="White") %>% 
  mutate(reference = 1)

### plot
ggplot(data = df_modifications_extensions_race_rri_viz, 
       aes(y = rri, 
           x = `Race/Ethnicity`, 
           fill = forcats::fct_rev(`Race/Ethnicity`))) + 
  geom_bar(stat = "identity", 
           position = "dodge"
           # ,color = "gray80"
             ) +
    # geom_bar(aes(y=reference),
    #          stat = "identity", 
    #        position = "dodge", 
    #        fill = "gray80") +
    geom_col_pattern(aes(y=reference),
                   pattern_color = NA,
                   pattern_fill = "gray80",
                   pattern = "stripe"
                   # ,color = "gray80"
                     ) +
  geom_abline(slope=0, 
              intercept=1,  
              col = "#000000", 
              size = 1.5, 
              linetype="dashed") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(limits=c(min(0), 
                                           max(2.05))) +
  scale_fill_manual(values = c("#1F4A58","#87C2D4")) +
  scale_color_manual(values = rev(c("#1F4A58","#87C2D4"))) +
  theme(legend.position = "top",
        legend.title.align=0.5,
        # axis.text.y = element_text(face = "bold", hjust = 1, size = 14),
        # strip.text.x = element_text(face = "bold", vjust = 1.5, size = 14, 
        #                             hjust = 0.5),
          axis.text.y = element_text(face = "bold",size = 14),
        axis.text.x = element_text(face = "bold", hjust = 1, size = 14),
        plot.caption = element_text(hjust = 0.5),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        axis.title.x = element_text(size = 15, margin = margin(t = 15)),
        axis.title.y = element_text(size =15, margin = margin(r = 15))) +
    labs(y = "Relative Rate Index (RRI)", 
         x = NULL,
      caption = NULL,
      title = NULL,
      subtitle = NULL,
      fill = NULL) +
    coord_flip() +
  # facet_grid(~ rri_measure) +
 # guides(fill = guide_legend(reverse = TRUE,
 #                             title.position = "top",
 #                             label.position = "bottom",
 #                             keywidth = 3,
 #                             nrow = 1)) +
   guides(fill = FALSE) +
  # geom_label_repel(aes(label = format(round(as.numeric(rri), 
  #                                           digits = 1), 
  #                                     nsmall=1), 
  #                      group = forcats::fct_rev(`Race/Ethnicity`),
  #                      color = `Race/Ethnicity`),
  #                 position = position_dodge(.9),
  #                 direction = 'x',
  #                 hjust = 0.75,
  #                 label.padding = 0.3,
  #                 box.padding = 0.15,
  #                 size = 5,
  #                 fill = "white",
  #                 fontface = "bold",
  #                 na.rm = TRUE,
  #                 show.legend = FALSE) +
  annotate("text", 
           x = 2.53, 
           y = 1.47, 
           label = "This line represents White youth (reference group)", 
           colour = "#000000", 
           size = 3.75, 
           fontface = 2)


### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_24_modification_rate_race_eth_rri.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )

```


```{r echo=FALSE,message=FALSE,warning=FALSE}
# ### remove groups analysis with small sample size
# ### pull out RRIs for plot
# ### use gather to shift data from wide to long
# df_rri_overall_jj_final_to_viz <- df_rri_overall_jj_final %>% 
#   filter(`Race/Ethnicity`%in%c("Black",
#                                "Hispanic",
#                                "White")) %>% 
#   dplyr::select(`Race/Ethnicity`,rri=`JJ-involved RRI (to white youth)`) %>% 
#   dplyr::filter(`Race/Ethnicity`!="White") %>% 
#   mutate(reference = 1)
# 
# ### plot
# ggplot(data = df_rri_overall_jj_final_to_viz, 
#        aes(y = rri, 
#            x = `Race/Ethnicity`, 
#            fill = forcats::fct_rev(`Race/Ethnicity`))) + 
#   geom_bar(stat = "identity", 
#            position = "dodge"
#            # ,color = "gray80"
#              ) +
#     # geom_bar(aes(y=reference),
#     #          stat = "identity", 
#     #        position = "dodge", 
#     #        fill = "gray80") +
#     geom_col_pattern(aes(y=reference),
#                    pattern_color = NA,
#                    pattern_fill = "gray80",
#                    pattern = "stripe"
#                    # ,color = "gray80"
#                      ) +
#   geom_abline(slope=0, 
#               intercept=1,  
#               col = "#000000", 
#               size = 1.5, 
#               linetype="dashed") +
#   scale_x_discrete(limits = rev) +
#   scale_y_continuous(limits=c(min(0), 
#                                            max(2.5))) +
#   scale_fill_manual(values = c("#1F4A58","#87C2D4")) +
#   scale_color_manual(values = rev(c("#1F4A58","#87C2D4"))) +
#   theme(legend.position = "top",
#         legend.title.align=0.5,
#         # axis.text.y = element_text(face = "bold", hjust = 1, size = 14),
#         # strip.text.x = element_text(face = "bold", vjust = 1.5, size = 14, 
#         #                             hjust = 0.5),
#           axis.text.y = element_text(face = "bold",size = 14),
#         axis.text.x = element_text(face = "bold", hjust = 1, size = 14),
#         plot.caption = element_text(hjust = 0.5),
#         axis.ticks.length = unit(0, "cm"),
#         panel.grid.major.y = element_blank(),
#         # panel.grid.major.x = element_blank(),
#         panel.grid.minor = element_blank(),
#         axis.title.x = element_text(size = 15, margin = margin(t = 15)),
#         axis.title.y = element_text(size =15, margin = margin(r = 15))) +
#     labs(y = "Relative Rate Index (RRI)", 
#          x = NULL,
#       caption = NULL,
#       title = NULL,
#       subtitle = NULL,
#       fill = NULL) +
#     coord_flip() +
#   # facet_grid(~ rri_measure) +
#  # guides(fill = guide_legend(reverse = TRUE,
#  #                             title.position = "top",
#  #                             label.position = "bottom",
#  #                             keywidth = 3,
#  #                             nrow = 1)) +
#    guides(fill = FALSE) +
#   # geom_label_repel(aes(label = format(round(as.numeric(rri), 
#   #                                           digits = 1), 
#   #                                     nsmall=1), 
#   #                      group = forcats::fct_rev(`Race/Ethnicity`),
#   #                      color = `Race/Ethnicity`),
#   #                 position = position_dodge(.9),
#   #                 direction = 'x',
#   #                 hjust = 0.75,
#   #                 label.padding = 0.3,
#   #                 box.padding = 0.15,
#   #                 size = 5,
#   #                 fill = "white",
#   #                 fontface = "bold",
#   #                 na.rm = TRUE,
#   #                 show.legend = FALSE) +
#   annotate("text", 
#            x = 2.53, 
#            y = 1.57, 
#            label = "This line represents White youth (reference group)", 
#            colour = "#000000", 
#            size = 3.75, 
#            fontface = 2)

### unique youth, referrals, and supervision episodes
df_technical_violations_risk_viz <- df_dallas_county_av_supervision_analytic_file |> 
  filter(race_clean%in%c("Black","White","Hispanic")) |> 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(percent = n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/n_distinct(unique_referral_id)) %>% 
  ungroup() |> 
  pivot_longer(!race_clean, names_to = "complaint_type", values_to = "percent") 

### plot
### bar plot
ggplot(data = df_technical_violations_risk_viz,
       aes(x = race_clean,
           y = percent,
           fill = race_clean)) + 
  geom_bar(stat = "identity",  
           color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(min(0), 
                                max(.4))) +
  geom_label(
    aes(
      y = percent,
      label = scales::percent(percent,
                              accuracy = 1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 6,
    colour = "white",
    show.legend = FALSE
  ) +
  scale_fill_manual(values = c("#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084")) +
  guides(fill = FALSE) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme_minimal() +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        # axis.text.x = element_markdown(),
        axis.text.y = element_markdown(size = 16),
        axis.text.x = element_text(face = "bold", hjust = 1, size = 16),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_24_modifications_race_eth.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br><br>

## Table 3. By Gender: Percentage of Supervision Episodes/Referrals with a Supervision Modification and Extension

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_modifications_extensions_gender <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(gender_clean) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (row %)` = scales::percent(n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (row %)` = scales::percent(n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean)

### overall
df_modifications_extensions_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (row %)` = scales::percent(n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (row %)` = scales::percent(n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Gender` = "Overall")

### combine tables for kable
df_modifications_extensions_gender_table <- rbind(df_modifications_extensions_gender,df_modifications_extensions_overall)

### print table via kableextra
kable(df_modifications_extensions_gender_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_technical_violations_risk_viz <- df_dallas_county_av_supervision_analytic_file |> 
  dplyr::group_by(gender_clean) %>% 
  dplyr::summarise(percent = n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/n_distinct(unique_referral_id)) %>% 
  ungroup() |> 
  pivot_longer(!gender_clean, names_to = "complaint_type", values_to = "percent") 

### plot
### bar plot
ggplot(data = df_technical_violations_risk_viz,
       aes(x = gender_clean,
           y = percent,
           fill = gender_clean)) + 
  geom_bar(stat = "identity",  
           color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(min(0), 
                                max(.4))) +
  geom_label(
    aes(
      y = percent,
      label = scales::percent(percent,
                              accuracy = 1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 6,
    colour = "white",
    show.legend = FALSE
  ) +
  scale_fill_manual(values = c("#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084")) +
  guides(fill = FALSE) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme_minimal() +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        # axis.text.x = element_markdown(),
        axis.text.y = element_markdown(size = 16),
        axis.text.x = element_text(face = "bold", hjust = 1, size = 16),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_24_modifications_gender.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br><br>

## Table 4. By Age: Percentage of Supervision Episodes/Referrals with a Supervision Modification and Extension

```{r echo=FALSE,message=FALSE,warning=FALSE}
### turn age into a factor
df_dallas_county_av_supervision_analytic_file %<>%
 mutate(age_at_referral_clean = factor(age_at_referral_clean,
         levels = c("Less than 12", 
                    "12 to 13",
                    "14 to 16",
                    "17+")))

### unique youth, referrals, and supervision episodes
df_modifications_extensions_age <- df_dallas_county_av_supervision_analytic_file %>% 
  filter(!is.na(age_at_referral_clean)) |> 
  dplyr::group_by(age_at_referral_clean) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (row %)` = scales::percent(n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (row %)` = scales::percent(n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age` = age_at_referral_clean)

### overall
df_modifications_extensions_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  filter(!is.na(age_at_referral_clean)) |> 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (row %)` = scales::percent(n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (row %)` = scales::percent(n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Age` = "Overall")

### combine tables for kable
df_modifications_extensions_age_table <- rbind(df_modifications_extensions_age,df_modifications_extensions_overall)

### print table via kableextra
kable(df_modifications_extensions_age_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_technical_violations_risk_viz <- df_dallas_county_av_supervision_analytic_file |> 
  filter(!is.na(age_at_referral_clean)) |> 
  dplyr::group_by(age_at_referral_clean) |> 
  dplyr::summarise(percent = n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/n_distinct(unique_referral_id)) %>% 
  ungroup() |> 
  pivot_longer(!age_at_referral_clean, names_to = "complaint_type", values_to = "percent") 

### plot
### bar plot
ggplot(data = df_technical_violations_risk_viz,
       aes(x = age_at_referral_clean,
           y = percent,
           fill = age_at_referral_clean)) + 
  geom_bar(stat = "identity",  
           color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(min(0), 
                                max(.4))) +
  geom_label(
    aes(
      y = percent,
      label = scales::percent(percent,
                              accuracy = 1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 6,
    colour = "white",
    show.legend = FALSE
  ) +
  scale_fill_manual(values = c("#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084")) +
  guides(fill = FALSE) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme_minimal() +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        # axis.text.x = element_markdown(),
        axis.text.y = element_markdown(size = 16),
        axis.text.x = element_text(face = "bold", hjust = 1, size = 16),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_24_modifications_age.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br><br>

## Table 5. By Risk Level: Percentage of Supervision Episodes/Referrals with a Supervision Modification and Extension

Note: This is the "listed risk level at the time of referral disposition"

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_modifications_extensions_risk <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (row %)` = scales::percent(n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (row %)` = scales::percent(n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level)

### overall
df_modifications_extensions_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (row %)` = scales::percent(n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (row %)` = scales::percent(n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_modifications_extensions_risk_table <- rbind(df_modifications_extensions_risk,df_modifications_extensions_overall)

### print table via kableextra
kable(df_modifications_extensions_risk_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

## slide 25
```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_technical_violations_risk_viz <- df_dallas_county_av_supervision_analytic_file |> 
  filter(offense_referral_risk_level!="Unknown/Not Administered") |> 
  dplyr::group_by(offense_referral_risk_level) |> 
  dplyr::summarise(percent = n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/n_distinct(unique_referral_id)) %>% 
  ungroup() |> 
  pivot_longer(!offense_referral_risk_level, names_to = "complaint_type", values_to = "percent") 

### plot
### bar plot
ggplot(data = df_technical_violations_risk_viz,
       aes(x = offense_referral_risk_level,
           y = percent,
           fill = offense_referral_risk_level)) + 
  geom_bar(stat = "identity",  
           color = "gray80") +
  scale_x_discrete(limits = rev) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(min(0), 
                                max(.4))) +
  geom_label(
    aes(
      y = percent,
      label = scales::percent(percent,
                              accuracy = 1),
      fontface = "bold"
    ),
    position = position_stack(vjust = .5),
    size = 6,
    colour = "white",
    show.legend = FALSE
  ) +
  scale_fill_manual(values = c("#2F7084","#2F7084","#2F7084","#2F7084","#2F7084","#2F7084")) +
  guides(fill = FALSE) +
  labs(x = NULL, y = NULL,
       fill = NULL,
       caption = NULL,
       title = NULL,
       subtitle = NULL) +
  theme_minimal() +
  theme(legend.position = "top",
        legend.title.align=0.5,
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5),
        # axis.text.x = element_markdown(),
        axis.text.y = element_markdown(size = 16),
        axis.text.x = element_text(face = "bold", hjust = 1, size = 16),
        axis.ticks.length = unit(0, "cm"),
        panel.grid.major.y = element_blank(),
        # panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank()) +
  coord_flip()

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_25_extension_by_risk.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

## slide 23a
```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and referrals per FY of exit
df_modifications_extensions_per_year_viz <- df_dallas_county_av_supervision_analytic_file |> 
  dplyr::group_by(supervision_end_fy) |> 
  dplyr::summarise(percent = n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/n_distinct(unique_referral_id)) %>% 
  ungroup() |> 
  mutate(group = "dallas")

###geom_line 
ggplot(data = df_modifications_extensions_per_year_viz, aes(x = supervision_end_fy, y = percent
                                                            ,
                                                            color = group,
                                                            group = group
                                                            )) +
  geom_line(color = "black", size = 2.75) +
  geom_line(size = 2.2) +
  geom_point(color = "black", size = 4) +
  geom_point(size = 3.5) +
  labs(x = "Fiscal Year", y = "Supervision Episodes with\nProbation Extension (%)", color=NULL, title = NULL, caption = NULL) +
  scale_y_continuous(label=scales::percent_format(accuracy=1),
                     limits = c(min(0), 
                                max(.2))) +
  theme(legend.position = "none",
        legend.title = element_text(hjust = 0.5,size = 13),
        legend.text = element_text(size = 13),
        panel.grid.major.x = element_blank(),      
        plot.title = element_text( hjust = 0.5),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.title.x = element_text(size = 16,margin = margin(t = 15)),
        axis.title.y = element_text(size = 16,margin = margin(r = 15)),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5)) +  
  scale_color_manual(values = c("#1F4A58")) +
  scale_fill_manual(values = c("#1F4A58")) +
  geom_label_repel(aes(label = scales::percent(as.numeric(percent),
                                               accuracy = 0.1),
                    fill = group
                    ),
                   hjust = .1,
                   label.padding = 0.2,
                   box.padding = 0.2,
                   color = "white",
                   size = 5,
                   segment.color = NA,
                   fontface = "bold",
                   na.rm = TRUE,
                   show.legend = FALSE)

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_25_extension_by_year.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

## slide 23b
```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and referrals per FY of exit
df_modifications_extensions_per_year_risk_viz <- df_dallas_county_av_supervision_analytic_file %>% 
  filter(offense_referral_risk_level!="Unknown/Not Administered") |> 
  dplyr::group_by(supervision_end_fy,offense_referral_risk_level) %>% 
  dplyr::summarise(percent = n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/n_distinct(unique_referral_id)) %>% 
  ungroup() |> 
  pivot_longer(!c(supervision_end_fy,offense_referral_risk_level), names_to = "referral_source", values_to = "percent")

###geom_line 
ggplot(data = df_modifications_extensions_per_year_risk_viz, aes(x = supervision_end_fy, y = percent
                                                            ,
                                                            color = offense_referral_risk_level,
                                                            group = offense_referral_risk_level
                                                            )) +
  geom_line(color = "black", size = 2.75) +
  geom_line(size = 2.2) +
  geom_point(color = "black", size = 4) +
  geom_point(size = 3.5) +
  labs(x = "Fiscal Year", y = "Supervision Episodes with\nProbation Modification (%)", color=NULL, title = NULL, caption = NULL) +
  scale_y_continuous(label=scales::percent_format(accuracy=1),
                     limits = c(min(0), 
                                max(.75))) +
  theme(legend.position = "top",
        legend.title = element_text(hjust = 0.5,size = 13),
        legend.text = element_text(size = 13),
        panel.grid.major.x = element_blank(),      
        plot.title = element_text( hjust = 0.5),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.title.x = element_text(size = 16,margin = margin(t = 15)),
        axis.title.y = element_text(size = 16,margin = margin(r = 15)),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5)) +  
  scale_color_manual(values = c("#87C2D4","#2F7084","#1F4A58")) +
  scale_fill_manual(values = c("#87C2D4","#2F7084","#1F4A58")) +
  geom_label_repel(aes(label = scales::percent(as.numeric(percent),
                                               accuracy = 0.1),
                    fill = offense_referral_risk_level
                    ),
                   hjust = .1,
                   label.padding = 0.2,
                   box.padding = 0.2,
                   color = "white",
                   size = 5,
                   segment.color = NA,
                   fontface = "bold",
                   na.rm = TRUE,
                   show.legend = FALSE)

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_23_modification_rate_by_risk.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```

<br><br>

## Table 6. By Needs Level: Percentage of Supervision Episodes/Referrals with a Supervision Modification and Extension

Note: This is the "listed needs level at the time of referral disposition"

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_modifications_extensions_needs <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (row %)` = scales::percent(n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (row %)` = scales::percent(n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level)

### overall
df_modifications_extensions_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
            `Supervision Episodes, Percent of Sample (column %)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (row %)` = scales::percent(n_distinct(unique_referral_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (row %)` = scales::percent(n_distinct(unique_referral_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_modifications_extensions_needs_table <- rbind(df_modifications_extensions_needs,df_modifications_extensions_overall)

### print table via kableextra
kable(df_modifications_extensions_needs_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br><br>

# Average Number of Modifications

**Note:** This current analysis does not account for the timing of modifications or extensions relative to technical violations

<br>

## Table 7. By FY: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### de-dup analytic file by supervision episode since we are calculating mean and medians
### recode extension count vars for mean/median; extension == NA needs to be 0 
df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup <- df_dallas_county_av_supervision_analytic_file %>% 
  distinct(unique_referral_id,
           .keep_all = TRUE) %>% 
  mutate(unique_supervision_extensions_per_supervision_count_average = ifelse(is.na(unique_supervision_extensions_per_supervision_count)==TRUE,
                                                                              0,unique_supervision_extensions_per_supervision_count)) |> 
  filter(supervision_end_fy!=2023)
  
### mean and median modifications and extensions
df_modifications_mean_median_year <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::group_by(supervision_end_fy) %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Min Number of Supervision Level Modifications` = min(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Level Modifications` = max(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                    `Min Number of Supervision Extensions` = min(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Extensions` = max(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Completion` = supervision_end_fy) %>% 
  mutate(`FY of Completion` = as.character(`FY of Completion`))

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
   dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Min Number of Supervision Level Modifications` = min(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Level Modifications` = max(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                    `Min Number of Supervision Extensions` = min(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Extensions` = max(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`FY of Completion` = "Overall")

### combine tables for kable
df_modifications_mean_median_year_table <- rbind(df_modifications_mean_median_year,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

## Table 8. By Race/Ethnicity: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_race <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Min Number of Supervision Level Modifications` = min(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Level Modifications` = max(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                    `Min Number of Supervision Extensions` = min(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Extensions` = max(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Min Number of Supervision Level Modifications` = min(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Level Modifications` = max(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                    `Min Number of Supervision Extensions` = min(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Extensions` = max(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_modifications_mean_median_race_table <- rbind(df_modifications_mean_median_race,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_race_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

## Table 9. By Gender: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_gender <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::group_by(gender_clean) %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Min Number of Supervision Level Modifications` = min(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Level Modifications` = max(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                    `Min Number of Supervision Extensions` = min(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Extensions` = max(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Min Number of Supervision Level Modifications` = min(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Level Modifications` = max(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                    `Min Number of Supervision Extensions` = min(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Extensions` = max(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`Gender` = "Overall")

### combine tables for kable
df_modifications_mean_median_gender_table <- rbind(df_modifications_mean_median_gender,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_gender_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br><br>

## Table 10. By Age: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %<>%
 mutate(age_at_referral_clean = factor(age_at_referral_clean,
         levels = c("Less than 12", 
                    "12 to 13",
                    "14 to 16",
                    "17+")))

### mean and median modifications and extensions
df_modifications_mean_median_age <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  filter(!is.na(age_at_referral_clean)) |> 
  dplyr::group_by(age_at_referral_clean) %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Min Number of Supervision Level Modifications` = min(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Level Modifications` = max(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                    `Min Number of Supervision Extensions` = min(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Extensions` = max(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age` = age_at_referral_clean) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  filter(!is.na(age_at_referral_clean)) |> 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Min Number of Supervision Level Modifications` = min(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Level Modifications` = max(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                    `Min Number of Supervision Extensions` = min(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Extensions` = max(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`Age` = "Overall")

### combine tables for kable
df_modifications_mean_median_age_table <- rbind(df_modifications_mean_median_age,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_age_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br><br>

## Table 11. By Risk Level: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_risk <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Min Number of Supervision Level Modifications` = min(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Level Modifications` = max(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                    `Min Number of Supervision Extensions` = min(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Extensions` = max(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>%  
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Min Number of Supervision Level Modifications` = min(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Level Modifications` = max(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                    `Min Number of Supervision Extensions` = min(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Extensions` = max(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_modifications_mean_median_risk_table <- rbind(df_modifications_mean_median_risk,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_risk_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br><br>

## Table 11b. By Risk Level: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_risk <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
                   `Mean Overall LOS` = mean(overall_supervision_los_days_min_max,
                                                                 na.rm = TRUE),
                   `Median Overall LOS` = median(overall_supervision_los_days_min_max,
                                                                 na.rm = TRUE),
                   `min Overall LOS` = min(overall_supervision_los_days_min_max,
                                                                 na.rm = TRUE),
                   `max Overall LOS` = max(overall_supervision_los_days_min_max,
                                                                 na.rm = TRUE)) %>%  
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level) 


### print table via kableextra
kable(df_modifications_mean_median_risk, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") 
```

<br><br>

## Table 12. By Needs Level: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_needs <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Min Number of Supervision Level Modifications` = min(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Level Modifications` = max(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                    `Min Number of Supervision Extensions` = min(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Extensions` = max(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_referral_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Min Number of Supervision Level Modifications` = min(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Level Modifications` = max(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                    `Min Number of Supervision Extensions` = min(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Max Number of Supervision Extensions` = max(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_modifications_mean_median_needs_table <- rbind(df_modifications_mean_median_needs,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_needs_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br><br>

# % of Episodes with Supervision Modifications Prior to First Technical Violation

**NOTE:** The following tables are limited to youth with a technical violation. The current analysis includes any upward modification of supervision level intensiveness (moving to a more intensive supervision level) that occurs prior to the first date of violation *AND* that is not linked to a new offense violation (definition of linked is that the modification occurs between 1 day prior to violation disposition or up to 3 days following violation disposition). Further, I only considered modifications that occurred two or more days prior to the filing date of the first technical violation for a given supervision episode as having occurred before a violation (and as likely unrelated to the violation).

<br>

## Table 13. By FY: % of Episodes with Supervision Modifications Prior to First Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
### using modification_increase_prior_to_technical_count in this section

### de-dup analytic file by supervision episode since we are calculating mean and medians
### filter on those with at least one technical violation as this will be the base sample
### of the youth with a technical violation, how many experienced increases in supervision level 
### intensiveness prior to the violation?

### recode modification var for mean/median; NA needs to be 0 
df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup <- df_dallas_county_av_supervision_analytic_file %>% 
  distinct(unique_referral_id,
           .keep_all = TRUE) %>% 
  filter(technical_violation_count>0) %>% 
  mutate(unique_supervision_extensions_per_supervision_count_average = ifelse(is.na(unique_supervision_extensions_per_supervision_count)==TRUE,
                                                                              0,unique_supervision_extensions_per_supervision_count),
         modification_increase_prior_to_technical_count_average = ifelse(is.na(modification_increase_prior_to_technical_count)==TRUE,
                                                                              0,modification_increase_prior_to_technical_count)) |> 
  filter(supervision_end_fy!=2023)

### mean and median modifications and extensions
df_modifications_mean_median_year <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::group_by(supervision_end_fy) %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_referral_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (row %)` = scales::percent(n_distinct(unique_referral_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Completion` = supervision_end_fy) %>% 
  mutate(`FY of Completion` = as.character(`FY of Completion`))

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_referral_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (row %)` = scales::percent(n_distinct(unique_referral_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1)) %>%  
  mutate(`FY of Completion` = "Overall")

### combine tables for kable
df_modifications_mean_median_year_table <- rbind(df_modifications_mean_median_year,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

## slide 23a
```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth and referrals per FY of exit
df_modifications_extensions_per_year_viz <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::group_by(supervision_end_fy) %>% 
  dplyr::summarise(percent = n_distinct(unique_referral_id[modification_increase_prior_to_technical_count_average>0])/n_distinct(unique_referral_id)) %>% 
  ungroup() |> 
  mutate(group = "dallas")

###geom_line 
ggplot(data = df_modifications_extensions_per_year_viz, aes(x = supervision_end_fy, y = percent
                                                            ,
                                                            color = group,
                                                            group = group
                                                            )) +
  geom_line(color = "black", size = 2.75) +
  geom_line(size = 2.2) +
  geom_point(color = "black", size = 4) +
  geom_point(size = 3.5) +
  labs(x = "Fiscal Year", y = "Supervision Episodes with Modification\n Prior to First Technical Violation (%)", color=NULL, title = NULL, caption = NULL) +
  scale_y_continuous(label=scales::percent_format(accuracy=1),
                     limits = c(min(0), 
                                max(.52))) +
  theme(legend.position = "none",
        legend.title = element_text(hjust = 0.5,size = 13),
        legend.text = element_text(size = 13),
        panel.grid.major.x = element_blank(),      
        plot.title = element_text( hjust = 0.5),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.title.x = element_text(size = 16,margin = margin(t = 15)),
        axis.title.y = element_text(size = 16,margin = margin(r = 15)),
        plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 0.5)) +  
  scale_color_manual(values = c("#1F4A58")) +
  scale_fill_manual(values = c("#1F4A58")) +
  geom_label_repel(aes(label = scales::percent(as.numeric(percent),
                                               accuracy = 0.1),
                    fill = group
                    ),
                   hjust = .1,
                   label.padding = 0.2,
                   box.padding = 0.2,
                   color = "white",
                   size = 5,
                   segment.color = NA,
                   fontface = "bold",
                   na.rm = TRUE,
                   show.legend = FALSE)

### write out
ggsave(
    filename = file.path(sp_viz_output_path, "slide_26_modification_prior_to_first_technical.png"),
    plot = last_plot(),
    device = ragg::agg_png,
    dpi = 300,
    height = 5.25,
    width = 10,
    units = "in",
    bg = "transparent"
  )
```


<br><br>

## Table 14. By Race/Ethnicity: % of Episodes with Supervision Modifications Prior to First Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_race <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_referral_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (row %)` = scales::percent(n_distinct(unique_referral_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_referral_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (row %)` = scales::percent(n_distinct(unique_referral_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1)) %>%  
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_modifications_mean_median_race_table <- rbind(df_modifications_mean_median_race,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_race_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

## Table 15. By Gender: % of Episodes with Supervision Modifications Prior to First Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_gender <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::group_by(gender_clean) %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_referral_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (row %)` = scales::percent(n_distinct(unique_referral_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Gender` = gender_clean) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_referral_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (row %)` = scales::percent(n_distinct(unique_referral_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Gender` = "Overall")

### combine tables for kable
df_modifications_mean_median_gender_table <- rbind(df_modifications_mean_median_gender,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_gender_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(3, bold = TRUE)
```

<br><br>

## Table 16. By Age: % of Episodes with Supervision Modifications Prior to First Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %<>%
 mutate(age_at_referral_clean = factor(age_at_referral_clean,
         levels = c("Less than 12", 
                    "12 to 13",
                    "14 to 16",
                    "17+")))

### mean and median modifications and extensions
df_modifications_mean_median_age <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  filter(!is.na(age_at_referral_clean)) |> 
  dplyr::group_by(age_at_referral_clean) %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_referral_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (row %)` = scales::percent(n_distinct(unique_referral_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Age` = age_at_referral_clean) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  filter(!is.na(age_at_referral_clean)) |> 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_referral_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (row %)` = scales::percent(n_distinct(unique_referral_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1)) %>%  
  mutate(`Age` = "Overall")

### combine tables for kable
df_modifications_mean_median_age_table <- rbind(df_modifications_mean_median_age,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_age_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br><br>

## Table 17. By Risk Level: % of Episodes with Supervision Modifications Prior to First Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_risk <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_referral_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (row %)` = scales::percent(n_distinct(unique_referral_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_referral_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (row %)` = scales::percent(n_distinct(unique_referral_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_modifications_mean_median_risk_table <- rbind(df_modifications_mean_median_risk,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_risk_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br><br>

## Table 18. By Needs Level: % of Episodes with Supervision Modifications Prior to First Technical Violation

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_needs <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_referral_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (row %)` = scales::percent(n_distinct(unique_referral_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_referral_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (row %)` = scales::percent(n_distinct(unique_referral_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_modifications_mean_median_needs_table <- rbind(df_modifications_mean_median_needs,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_needs_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(5, bold = TRUE)
```

<br><br>
