---
title: "How are modifications used?"
format: html
---


**How are modifications used?**

* What is the average number of modifications per supervision episode? How does this vary across race/ethnicity, sex, and risk level? 

* What is the average number of modifications for youth who receive a technical violation? How does this vary across race/ethnicity, sex, and risk level? 


```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### set project path with csg_get_project_path (just once)
# csg_set_project_path(project = "jj-av-dallas",
# sp_folder = "C:/Users/abyrum/The Council of State Governments/JC Research - JJ_AV - JJ_AV/Dallas", force = TRUE)

### data path
sp_data_path <- csg_get_project_path("jj-av-dallas")

### viz output path
# sp_viz_output_path <- paste(sp_data_path, "/Output/r_output_presentation")

```

```{r include=FALSE,message=FALSE,warning=FALSE}
###############################
### import dallas analytic file
###############################

### set sharepoint path using sp_data_path and file.path function 
sharepoint_jj_av_dallas_analytic_data <- file.path(sp_data_path,"Data/analysis")

df_dallas_county_av_supervision_analytic_file <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "df_dallas_county_av_supervision_analytic_file.txt"),
                      delim = "|") %>% 
  mutate(offense_referral_risk_level = 
           case_when(
             offense_referral_risk_level=="Low Risk" ~ 1,
             offense_referral_risk_level%in%c("Medium-Low Risk",
                             "Medium-High Risk",
                             "Moderate Risk") ~ 2,
             offense_referral_risk_level=="High Risk" ~ 3,             
             offense_referral_risk_level=="Unknown" ~ 4,
             offense_referral_risk_level=="Not Administered" ~ 5,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_risk_level = factor(offense_referral_risk_level,
         levels = c(1,2,3,4,5),
         labels =  c("Low Risk", 
                     "Moderate Risk", 
                     "High Risk",
                     "Unknown",
                     "Not Administered")),
         offense_referral_needs_level = 
           case_when(
             offense_referral_needs_level=="Low Needs" ~ 1,
             offense_referral_needs_level=="Moderate Needs" ~ 2,
             offense_referral_needs_level=="High Needs" ~ 3,             
             offense_referral_needs_level=="Unknown" ~ 4,
             offense_referral_needs_level=="Not Administered" ~ 5,
             TRUE ~ as.numeric(NA)),
         ### use factor function to assign labels to values
         offense_referral_needs_level = factor(offense_referral_needs_level,
         levels = c(1,2,3,4,5),
         labels = c("Low Needs", 
                    "Moderate Needs", 
                    "High Needs",
                    "Unknown",
                    "Not Administered")))

```

# Modifications Overview

**NOTE:** All analysis of supervision level modifications (e.g., supervision episodes with at least one supervision level modification) refer to instances where a supervision phase/level is modified to a more intensive level of supervision. 

<br>


```{r eval=FALSE,include=FALSE,message=FALSE,warning=FALSE}
### explore LOS over time to see what switch to grouping by FY of completion looks like

### total supervision los per FY of exit
df_los_per_year <- df_dallas_county_av_supervision_analytic_file %>% 
  distinct(unique_supervision_id,
           .keep_all = TRUE) |> 
  dplyr::group_by(supervision_end_fy) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Mean LOS` = mean(overall_supervision_los_days.x,
                              na.rm = TRUE),
            `Median LOS` = median(overall_supervision_los_days.x,
                              na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Completion` = supervision_end_fy) %>% 
  mutate(`FY of Completion` = as.character(`FY of Completion`))

### overall
df_los_overall <- df_dallas_county_av_supervision_analytic_file %>% 
    distinct(unique_supervision_id,
           .keep_all = TRUE) |> 
   dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Mean LOS` = mean(overall_supervision_los_days.x,
                              na.rm = TRUE),
            `Median LOS` = median(overall_supervision_los_days.x,
                              na.rm = TRUE)) %>% 
  mutate(`FY of Completion` = "Overall")

### combine tables for kable
df_los_per_year_table <- rbind(df_los_per_year,
                               df_los_overall)

### print table via kableextra
kable(df_los_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7, bold = TRUE) |> 
### save out
save_kable("C:\\Users\\abyrum\\Documents\\table_los_per_year_table.png")
```


## Table 1. By FY: Percentage of Supervision Episodes/Referrals with a Supervision Modification and Extension

```{r echo=FALSE,message=FALSE,warning=FALSE}
### create denominator -- unique referrals for entire sample
unique_referrals_sample_denom <- n_distinct(df_dallas_county_av_supervision_analytic_file$unique_id,
                                            df_dallas_county_av_supervision_analytic_file$referral_number)

### create denominator -- unique supervision episodes
unique_supervision_episode_denom <- n_distinct(df_dallas_county_av_supervision_analytic_file$unique_supervision_id)

### create denominator -- unique youth for entire sample
unique_youth_sample_denom <- n_distinct(df_dallas_county_av_supervision_analytic_file$unique_id)

### unique youth and referrals per FY of exit
df_modifications_extensions_per_year <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(supervision_end_fy) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Completion` = supervision_end_fy) %>% 
  mutate(`FY of Completion` = as.character(`FY of Completion`))

### overall
df_modifications_extensions_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`FY of Completion` = "Overall")

### combine tables for kable
df_modifications_extensions_per_year_table <- rbind(df_modifications_extensions_per_year,df_modifications_extensions_overall)

### print table via kableextra
kable(df_modifications_extensions_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7, bold = TRUE)
```

<br><br>

## Table 2. By Race/Ethnicity: Percentage of Supervision Episodes/Referrals with a Supervision Modification and Extension

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_modifications_extensions_race <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean)

### overall
df_modifications_extensions_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_modifications_extensions_race_table <- rbind(df_modifications_extensions_race,df_modifications_extensions_overall)

### print table via kableextra
kable(df_modifications_extensions_race_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```


<br><br>

## Table 3. By Risk Level: Percentage of Supervision Episodes/Referrals with a Supervision Modification and Extension

Note: This is the "listed risk level at the time of referral disposition"

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_modifications_extensions_risk <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level)

### overall
df_modifications_extensions_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_modifications_extensions_risk_table <- rbind(df_modifications_extensions_risk,df_modifications_extensions_overall)

### print table via kableextra
kable(df_modifications_extensions_risk_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

## Table 4. By Needs Level: Percentage of Supervision Episodes/Referrals with a Supervision Modification and Extension

Note: This is the "listed needs level at the time of referral disposition"

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_modifications_extensions_needs <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level)

### overall
df_modifications_extensions_overall <- df_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_modifications_extensions_needs_table <- rbind(df_modifications_extensions_needs,df_modifications_extensions_overall)

### print table via kableextra
kable(df_modifications_extensions_needs_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

# Average Number of Modifications

**Note:** This current analysis does not account for the timing of modifications or extensions relative to technical violations

<br>

## Table 5. By FY: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### de-dup analytic file by supervision episode since we are calculating mean and medians
### recode extension count vars for mean/median; extension == NA needs to be 0 
df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup <- df_dallas_county_av_supervision_analytic_file %>% 
  distinct(unique_supervision_id,
           .keep_all = TRUE) %>% 
  mutate(unique_supervision_extensions_per_supervision_count_average = ifelse(is.na(unique_supervision_extensions_per_supervision_count)==TRUE,
                                                                              0,unique_supervision_extensions_per_supervision_count))
  

### mean and median modifications and extensions
df_modifications_mean_median_year <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::group_by(supervision_end_fy) %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Completion` = supervision_end_fy) %>% 
  mutate(`FY of Completion` = as.character(`FY of Completion`))

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`FY of Completion` = "Overall")

### combine tables for kable
df_modifications_mean_median_year_table <- rbind(df_modifications_mean_median_year,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7, bold = TRUE)
```

<br><br>

## Table 6. By Race/Ethnicity: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_race <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_modifications_mean_median_race_table <- rbind(df_modifications_mean_median_race,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_race_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

## Table 7. By Risk Level: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_risk <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_modifications_mean_median_risk_table <- rbind(df_modifications_mean_median_risk,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_risk_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

## Table 8. By Needs Level: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_needs <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_modifications_mean_median_needs_table <- rbind(df_modifications_mean_median_needs,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_needs_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

# Average Number of Modifications Prior to First Technical Violation

**NOTE:** The following tables are limited to youth with a technical violation. The current analysis includes any upward modification of supervision level intensiveness (moving to a more intensive supervision level) that occurs prior to the date of violation. In some instances, we may counting modifications linked to the violation (e.g., when the modification occurred one day before the violation, it's very possible they are linked to the same event).

<br>

## Table 9. By FY: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### using modification_increase_prior_to_technical_count in this section

### de-dup analytic file by supervision episode since we are calculating mean and medians
### filter on those with at least one technical violation as this will be the base sample
### of the youth with a technical violation, how many experienced increases in supervision level 
### intensiveness prior to the violation?

### recode modification var for mean/median; NA needs to be 0 
df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup <- df_dallas_county_av_supervision_analytic_file %>% 
  distinct(unique_supervision_id,
           .keep_all = TRUE) %>% 
  filter(technical_violation_count>0) %>% 
  mutate(unique_supervision_extensions_per_supervision_count_average = ifelse(is.na(unique_supervision_extensions_per_supervision_count)==TRUE,
                                                                              0,unique_supervision_extensions_per_supervision_count),
         modification_increase_prior_to_technical_count_average = ifelse(is.na(modification_increase_prior_to_technical_count)==TRUE,
                                                                              0,modification_increase_prior_to_technical_count))

### mean and median modifications and extensions
df_modifications_mean_median_year <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::group_by(supervision_end_fy) %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_supervision_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (%)` = scales::percent(n_distinct(unique_supervision_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1),
                   `Mean Number of Prior Supervision Level Modifications` = mean(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Prior Supervision Level Modifications` = median(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`FY of Completion` = supervision_end_fy) %>% 
  mutate(`FY of Completion` = as.character(`FY of Completion`))

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_supervision_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (%)` = scales::percent(n_distinct(unique_supervision_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1),
                   `Mean Number of Prior Supervision Level Modifications` = mean(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Prior Supervision Level Modifications` = median(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`FY of Completion` = "Overall")

### combine tables for kable
df_modifications_mean_median_year_table <- rbind(df_modifications_mean_median_year,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(7, bold = TRUE)
```

<br><br>

## Table 10. By Race/Ethnicity: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_race <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_supervision_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (%)` = scales::percent(n_distinct(unique_supervision_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1),
                   `Mean Number of Prior Supervision Level Modifications` = mean(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Prior Supervision Level Modifications` = median(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_supervision_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (%)` = scales::percent(n_distinct(unique_supervision_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1),
                   `Mean Number of Prior Supervision Level Modifications` = mean(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Prior Supervision Level Modifications` = median(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_modifications_mean_median_race_table <- rbind(df_modifications_mean_median_race,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_race_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

## Table 11. By Risk Level: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_risk <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_supervision_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (%)` = scales::percent(n_distinct(unique_supervision_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1),
                   `Mean Number of Prior Supervision Level Modifications` = mean(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Prior Supervision Level Modifications` = median(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_supervision_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (%)` = scales::percent(n_distinct(unique_supervision_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1),
                   `Mean Number of Prior Supervision Level Modifications` = mean(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Prior Supervision Level Modifications` = median(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_modifications_mean_median_risk_table <- rbind(df_modifications_mean_median_risk,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_risk_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

## Table 12. By Needs Level: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_needs <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_supervision_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (%)` = scales::percent(n_distinct(unique_supervision_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1),
                   `Mean Number of Prior Supervision Level Modifications` = mean(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Prior Supervision Level Modifications` = median(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level) 

### overall
df_modifications_mean_median_overall <- df_dallas_county_av_supervision_analytic_file_supervision_episode_technical_de_dup %>% 
  dplyr::summarise(`Supervision Episodes w/ Technical Violation (N)` = n_distinct(unique_supervision_id),
                   `Supervision Episodes, with at least one level modification prior to Technical (%)` = scales::percent(n_distinct(unique_supervision_id[modification_increase_prior_to_technical_count_average>0])/`Supervision Episodes w/ Technical Violation (N)`,
                                                                       accuracy = .1),
                   `Mean Number of Prior Supervision Level Modifications` = mean(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Prior Supervision Level Modifications` = median(modification_increase_prior_to_technical_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_modifications_mean_median_needs_table <- rbind(df_modifications_mean_median_needs,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_needs_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>
