---
title: "How are modifications used?"
format: html
---


**How are modifications used?**

* What is the average number of modifications per supervision episode? How does this vary across race/ethnicity, sex, and risk level? 

* What is the average number of modifications for youth who receive a technical violation? How does this vary across race/ethnicity, sex, and risk level? 

* What are the most common reasons for modifications? 

* What are the most common results of modifications? 

```{r include=FALSE}
### call libraries
library(easypackages)
libraries("tidyverse","foreign","lubridate","reshape2", "ggplot2","RColorBrewer","knitr","forcats","openxlsx","statar","svDialogs","xlsx", "magrittr","stringr", "data.table","janitor","kableExtra","leaflet", "readr", "rmarkdown","rowr", "gganimate", "gifski","tidycensus","sf","htmltools","acs","tigris","mapview","rgeos", "ggrepel", "censusxy","gdata","lavaan","mclust","tmap", "raster","rgeos","gmapsdistance","viridis","cowplot","lintr","leaflet.extras","censusapi","data.table","gridGraphics","readxl","haven","ggridges","extrafont","extrafontdb","datamodelr","Lahman","DiagrammeR","fs","readxl","rsvg","V8","csgjcr","DataExplorer","tidylog")
```

```{r include=FALSE,message=FALSE,warning=FALSE}
### set chunk output specifications
knitr::opts_chunk$set(
  echo = TRUE,
  dev = "ragg_png",
  cache = FALSE)

### set theme
theme_set(theme_minimal())

### set project path with csg_get_project_path (just once)
# csg_set_project_path(project = "jj-av-dallas",
# sp_folder = "C:/Users/abyrum/The Council of State Governments/JC Research - JJ_AV - JJ_AV/Dallas", force = TRUE)

### data path
sp_data_path <- csg_get_project_path("jj-av-dallas")

### viz output path
# sp_viz_output_path <- paste(sp_data_path, "/Output/r_output_presentation")

```

```{r include=FALSE,message=FALSE,warning=FALSE}
###############################
### import dallas analytic file
###############################

### set sharepoint path using sp_data_path and file.path function 
sharepoint_jj_av_dallas_analytic_data <- file.path(sp_data_path,"Data/analysis")

prelim_dallas_county_av_supervision_analytic_file <- read_delim(file.path(sharepoint_jj_av_dallas_analytic_data,
                      "prelim_dallas_county_av_supervision_analytic_file.txt"),
                      delim = "|")

```

# Modifications Overview

**NOTE:** All analysis of supervision level modifications (e.g., supervision episodes with at least one supervision level modification) refer to instances where a supervision phase/level is modified to a more intensive level of supervision. 

<br>

## Table 1. By year: Percentage of Supervision Episodes/Referrals with a Supervision Modification and Extension

```{r echo=FALSE,message=FALSE,warning=FALSE}
### create denominator -- unique referrals for entire sample
unique_referrals_sample_denom <- n_distinct(prelim_dallas_county_av_supervision_analytic_file$unique_id,
                                            prelim_dallas_county_av_supervision_analytic_file$referral_number)

### create denominator -- unique supervision episodes
unique_supervision_episode_denom <- n_distinct(prelim_dallas_county_av_supervision_analytic_file$unique_supervision_id)

### create denominator -- unique youth for entire sample
unique_youth_sample_denom <- n_distinct(prelim_dallas_county_av_supervision_analytic_file$unique_id)

### unique youth and referrals per year
df_modifications_extensions_per_year <- prelim_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(referral_year) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Year of Referral` = referral_year) %>% 
  mutate(`Year of Referral` = as.character(`Year of Referral`))

### overall
df_modifications_extensions_overall <- prelim_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Year of Referral` = "Overall")

### combine tables for kable
df_modifications_extensions_per_year_table <- rbind(df_modifications_extensions_per_year,df_modifications_extensions_overall)

### print table via kableextra
kable(df_modifications_extensions_per_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(11, bold = TRUE)
```

<br><br>

## Table 2. By Race/Ethnicity: Percentage of Supervision Episodes/Referrals with a Supervision Modification and Extension

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_modifications_extensions_race <- prelim_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean)

### overall
df_modifications_extensions_overall <- prelim_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_modifications_extensions_race_table <- rbind(df_modifications_extensions_race,df_modifications_extensions_overall)

### print table via kableextra
kable(df_modifications_extensions_race_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```


<br><br>

## Table 3. By Risk Level: Percentage of Supervision Episodes/Referrals with a Supervision Modification and Extension

Note: This is the "listed risk level at the time of referral disposition"

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_modifications_extensions_risk <- prelim_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level)

### overall
df_modifications_extensions_overall <- prelim_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_modifications_extensions_risk_table <- rbind(df_modifications_extensions_risk,df_modifications_extensions_overall)

### print table via kableextra
kable(df_modifications_extensions_risk_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br><br>

## Table 4. By Needs Level: Percentage of Supervision Episodes/Referrals with a Supervision Modification and Extension

Note: This is the "listed needs level at the time of referral disposition"

```{r echo=FALSE,message=FALSE,warning=FALSE}
### unique youth, referrals, and supervision episodes
df_modifications_extensions_needs <- prelim_dallas_county_av_supervision_analytic_file %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level)

### overall
df_modifications_extensions_overall <- prelim_dallas_county_av_supervision_analytic_file %>% 
  dplyr::summarise(`Unique Youth (N)` = n_distinct(unique_id),
            `Unique Referrals (N)` = n_distinct(unique_referral_id),
            `Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
            `Supervision Episodes, Percent of Sample (%)` = scales::percent(`Unique Supervision Episodes (N)`/unique_supervision_episode_denom,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one level modification (%)` = scales::percent(n_distinct(unique_supervision_id[supervision_level_increases_per_supervision_episode_count>1])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1),
            `Supervision Episodes, with at least one supervision extension (%)` = scales::percent(n_distinct(unique_supervision_id[unique_supervision_extensions_per_supervision_count>0])/`Unique Supervision Episodes (N)`,
                                                                       accuracy = .1)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_modifications_extensions_needs_table <- rbind(df_modifications_extensions_needs,df_modifications_extensions_overall)

### print table via kableextra
kable(df_modifications_extensions_needs_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

# Average Number of Modifications

Note: This current analysis does not account for the timing of modifications or extensions relative to technical violations

<br>

## Table 5. By year: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### de-dup analytic file by supervision episode since we are calculating mean and medians
### recode modification and extension count vars for mean/median; extension == NA needs to be 0 and modification count should subtract one as as supervision episodes have at least one phase/level
prelim_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup <- prelim_dallas_county_av_supervision_analytic_file %>% 
  distinct(unique_supervision_id,
           .keep_all = TRUE) %>% 
  mutate(supervision_level_increases_per_supervision_episode_count_average = supervision_level_increases_per_supervision_episode_count-1,
         unique_supervision_extensions_per_supervision_count_average = ifelse(is.na(unique_supervision_extensions_per_supervision_count)==TRUE,
                                                                              0,unique_supervision_extensions_per_supervision_count))
  

### mean and median modifications and extensions
df_modifications_mean_median_year <- prelim_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::group_by(referral_year) %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Year of Referral` = referral_year) %>% 
  mutate(`Year of Referral` = as.character(`Year of Referral`))

### overall
df_modifications_mean_median_overall <- prelim_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`Year of Referral` = "Overall")

### combine tables for kable
df_modifications_mean_median_year_table <- rbind(df_modifications_mean_median_year,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_year_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(11, bold = TRUE)
```

<br><br>

## Table 6. By Race/Ethnicity: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_race <- prelim_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::group_by(race_clean) %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Race/Ethnicity` = race_clean) 

### overall
df_modifications_mean_median_overall <- prelim_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`Race/Ethnicity` = "Overall")

### combine tables for kable
df_modifications_mean_median_race_table <- rbind(df_modifications_mean_median_race,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_race_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

## Table 7. By Risk Level: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_risk <- prelim_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::group_by(offense_referral_risk_level) %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Risk Level` = offense_referral_risk_level) 

### overall
df_modifications_mean_median_overall <- prelim_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`Risk Level` = "Overall")

### combine tables for kable
df_modifications_mean_median_risk_table <- rbind(df_modifications_mean_median_risk,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_risk_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(8, bold = TRUE)
```

<br><br>

## Table 8. By Needs Level: Average Number of Supervision Modifications and Extensions per Supervision Episode

```{r echo=FALSE,message=FALSE,warning=FALSE}
### mean and median modifications and extensions
df_modifications_mean_median_needs <- prelim_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::group_by(offense_referral_needs_level) %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::rename(`Needs Level` = offense_referral_needs_level) 

### overall
df_modifications_mean_median_overall <- prelim_dallas_county_av_supervision_analytic_file_supervision_episode_de_dup %>% 
  dplyr::summarise(`Unique Supervision Episodes (N)` = n_distinct(unique_supervision_id),
                   `Mean Number of Supervision Level Modifications` = mean(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Level Modifications` = median(supervision_level_increases_per_supervision_episode_count_average,
                                                                 na.rm = TRUE),
                   `Mean Number of Supervision Extensions` = mean(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE),
                   `Median Number of Supervision Extensions` = median(unique_supervision_extensions_per_supervision_count_average,
                                                                 na.rm = TRUE)) %>% 
  mutate(`Needs Level` = "Overall")

### combine tables for kable
df_modifications_mean_median_needs_table <- rbind(df_modifications_mean_median_needs,df_modifications_mean_median_overall)

### print table via kableextra
kable(df_modifications_mean_median_needs_table, 
      format.args = list(big.mark = ","), 
      align=rep('c')) %>%
  kable_styling(bootstrap_options = c("striped", 
                                       "hover", 
                                       "condensed", 
                                       "responsive"), 
                 row_label_position = "l") %>% 
  row_spec(6, bold = TRUE)
```

<br><br>

# Reasons and Outcomes of Modifications

TBD 
